---
title: "Maternal Rat Anthropometry at Collection Data AIN-76A diet with MD or Alcohol and Iron Supplement or Water- GD20.5, Removing 2 DataPoints"
author: "Kaylee Helfrich"
date: "10/26/20"
output: 
  pdf_document: default
  html_document: default
data: "Maternal_Rat_Anthropometry_Nov-Dec2019_RmData2.csv"
---

Built with R `r getRversion()`

```{r RMarkdown setup, include = FALSE, message = FALSE}
require(knitr)
knitr::opts_chunk$set(echo = TRUE, tidy.opts=list(width.cutoff=60), tidy=TRUE)
knitr::opts_knit$set(root.dir = "~/KayleeStuff/Smith_Lab/Data/Rat_Iron/Maternal_Anthro/Collection")
options(tinytex.verbose = TRUE)
```

# Graphing Maternal Rat Anthropometry
This document details my graphing of the anthropometry data from maternal rats, including maternal weight at GD0.5 and GD20.5, gestational weight gain, dosing weight gain, litter size, percent survival, percent male, non-pregnancy weight, total uterine weight, uterine weight per fetus, maternal spleen weight, and maternal kidney weight. This analysis uses only data that was collected from rat dams with litter sizes that were more than 2 SD from the average litter size of 10 (excluding the nonpregnant dams). Dams R029 and R031 were excluded. Another set of analyses will exclude samples from all dams, regardless of litter size. All samples were collected between 11/2019-12/2019 by Kaylee Helfrich, Olivia Rivera, Nipun Saini, and Cecilia Kwan. Long-Evans rats arrived at 7 weeks old and were mated at 9-11 weeks of age. The rats were dosed with 5g/kg ethanol or isocaloric maltodextrin from GD13.5-19.5. The dams also received either an iron supplement (6g/kg, Fer-In-Sol) or the same volume of water as a gavage from GD12.5-GD19.5. All dams consumed AIN-76G diet modified to contain 100ppm of iron from arrival through pregnancy. Tissues were harvested on GD20.5. All graphs are mean with standard deviation, since there are not multiple measures per sample. This analysis will allow us to compare the 4 groups. Statistical analysis in JMP will use ANOVA, following checks for normality and variance, to assign significance to the measures. 

```{r include = FALSE}
rm(list=ls())
setwd("~/KayleeStuff/Smith_Lab/Data/Rat_Iron/Maternal_Anthro/Collection")
library(ggplot2)
library(plotrix)
```

```{r Import file and rearrange by treatment to be alphabetical}
File <- "Maternal_Rat_Anthropometry_Nov-Dec2019_RmData2.csv"
data <- read.csv(File, header=TRUE) 
data_frame <- data.frame(data)
data_frame <- data_frame[order(data_frame$Treatment), ]
```
```{r echo = FALSE}
print(data_frame)
```
```{r Prepare data for graphing}
ActualGroupOrder <- c("PAE-Iron", "PAE","MD-Iron", "MD")
NumPoints <- 9 #Make sure to set the integer to the number of dots/values you have for each treatment
```

# Maternal Weight at GD0.5

## All code is included for this first example, but thereafter, only the heading and graphs are shown. For all graphs, all data is graphed unless mentioned otherwise. Messages and warnings are excluded, since NA's were included to make all groups even, and I didn't want the code to print out these errors when they weren't necessary.
```{r, warning = FALSE, message = FALSE}
#Mean- calculate mean for column, repeat it to number of points, and create dataframe
Mean <- tapply(data_frame$Maternal.Wt.GD0.5, as.character(data_frame$Treatment), mean, na.rm=TRUE) #make sure to change selected column to change data for graph
Mean <- as.data.frame(rep(Mean, each = NumPoints)) #repeat mean a set number of times
Mean$Treatment <- rep(ActualGroupOrder, each = NumPoints) #repeat treatment a set number of times
colnames(Mean)[1] <- "Mean" #fix column name

#Stdev- calculate standard deviation for column, repeat it to number of points, and create dataframe
Stdev <- tapply(data_frame$Maternal.Wt.GD0.5, as.character(data_frame$Treatment), sd, na.rm=TRUE) #make sure to change selected column
Stdev <- as.data.frame(rep(Stdev, each = NumPoints)) #repeat stdev a set number of times
Stdev$Treatment <- rep(ActualGroupOrder, each = NumPoints) #repeat treatment a set number of times
colnames(Stdev)[1] <- "Stdev" #fix column name

#Combine mean, standard deviation, and individual data points
dataframe_combine <- cbind(Mean, Stdev, data_frame$Maternal.Wt.GD0.5) #make sure to change selected column
colnames(dataframe_combine)[5] <- "Value" #Fix name of individual data point column
dataframe_combine <- dataframe_combine[-2] #Remove extra treatment column

#Error bars
dataframe_combine$Upper <- dataframe_combine$Mean + dataframe_combine$Stdev #upper error
dataframe_combine$Lower <- dataframe_combine$Mean - dataframe_combine$Stdev #lower error

#Make Graph#
png("Maternal_WeightatGD0.5_RmData2_PAExFe_Dotplot.png", units="in", width=7, height=7, res=600) 

sets <- c("MD", "PAE", "MD-Iron", "PAE-Iron")

p<- ggplot(dataframe_combine, aes(x=Treatment, y=Mean)) + 
  geom_bar(stat="identity", color="black", aes(fill = Treatment),
           position=position_dodge()) +
  scale_fill_manual(values=c("MD" = "#0000CC",
                             "PAE" = "#6699FF",
                             "MD-Iron" = "#660066",
                             "PAE-Iron" = "#9900CC"
                             )) +
  geom_errorbar(aes(ymin=Lower, ymax=Upper), width=.2,
                position=position_dodge(.9)) + 
  geom_point(aes(x=Treatment, y=Value),
             size = 1.25, shape = 19, position = position_jitter(width=.15)) +
  scale_y_continuous(expand = c(0,0), limits = c(0,300)) +
  ggtitle("Maternal Weight at GD0.5") +
  ylab(expression("Maternal Weight (g)")) + 
  theme(plot.title = element_text(hjust = 0.5, size=18), 
        axis.title.x = element_blank(), #gets rid of x-axis label
        axis.title.y = element_text(size = 16),
        panel.grid.major = element_blank(), #gets rid of major gridlines
        panel.grid.minor = element_blank(), #gets rid of minor gridlines
        panel.background = element_blank(), #turns background white instead of gray
        axis.line = element_line(colour = "black"), 
        legend.position="none", #gets rid of legend
        axis.text=element_text(size=18, color = "black"), #sets size of x and y axis labels
        axis.text.x=element_text(angle = 45, vjust = .95, hjust = 0.9),
        axis.title=element_text(size=20,face="bold")) + 
  scale_x_discrete (limits = sets)
print(p)
dev.off() 
```
```{r Maternal Weight at GD0.5, echo = FALSE}
print(p)
```

# Maternal Weight at GD20.5
```{r, echo = FALSE, warning = FALSE, message = FALSE}
#Mean
Mean <- tapply(data_frame$Maternal.Wt.GD20.5, as.character(data_frame$Treatment), mean, na.rm=TRUE) #make sure to change 
Mean <- as.data.frame(rep(Mean, each = NumPoints))
Mean$Treatment <- rep(ActualGroupOrder, each = NumPoints) 
colnames(Mean)[1] <- "Mean"

#Stdev
Stdev <- tapply(data_frame$Maternal.Wt.GD20.5, as.character(data_frame$Treatment), sd, na.rm=TRUE) #make sure to change 
Stdev <- as.data.frame(rep(Stdev, each = NumPoints))
Stdev$Treatment <- rep(ActualGroupOrder, each = NumPoints)
colnames(Stdev)[1] <- "Stdev"

#Combine
dataframe_combine <- cbind(Mean, Stdev, data_frame$Maternal.Wt.GD20.5) #make sure to change
colnames(dataframe_combine)[5] <- "Value"
dataframe_combine <- dataframe_combine[-2]

#Error bars
dataframe_combine$Upper <- dataframe_combine$Mean + dataframe_combine$Stdev
dataframe_combine$Lower <- dataframe_combine$Mean - dataframe_combine$Stdev

#Make Graph#
png("Maternal_WeightatGD20.5_RmData2_PAExFe_Dotplot.png", units="in", width=7, height=7, res=600) 

sets <- c("MD", "PAE", "MD-Iron", "PAE-Iron")

p<- ggplot(dataframe_combine, aes(x=Treatment, y=Mean)) + 
  geom_bar(stat="identity", color="black", aes(fill = Treatment),
           position=position_dodge()) +
  scale_fill_manual(values=c("MD" = "#0000CC",
                             "PAE" = "#6699FF",
                             "MD-Iron" = "#660066",
                             "PAE-Iron" = "#9900CC"
                             )) +
  geom_errorbar(aes(ymin=Lower, ymax=Upper), width=.2,
                position=position_dodge(.9)) + 
  geom_point(aes(x=Treatment, y=Value),
             size = 1.25, shape = 19, position = position_jitter(width=.15)) +
  scale_y_continuous(expand = c(0,0), limits = c(0,400)) +
  ggtitle("Maternal Weight at GD20.5") +
  ylab(expression("Gestational Weight at GD20.5 (g)")) + 
  theme(plot.title = element_text(hjust = 0.5, size=18), 
        axis.title.x = element_blank(), #gets rid of x-axis label
        axis.title.y = element_text(size = 16),
        panel.grid.major = element_blank(), #gets rid of major gridlines
        panel.grid.minor = element_blank(), #gets rid of minor gridlines
        panel.background = element_blank(), #turns background white instead of gray
        axis.line = element_line(colour = "black"), 
        legend.position="none", #gets rid of legend
        axis.text=element_text(size=18, color = "black"), #sets size of x and y axis labels
        axis.text.x=element_text(angle = 45, vjust = .95, hjust = 0.9),
        axis.title=element_text(size=20,face="bold")) + 
  scale_x_discrete (limits = sets)
print(p)
dev.off() 
```
```{r Maternal Weight at GD20.5, echo = FALSE, warning = FALSE, message = FALSE}
print(p)
```

# Maternal Gestational Weight Gain
```{r, echo = FALSE, warning = FALSE, message = FALSE}
#Mean
Mean <- tapply(data_frame$Gestational.Wt.Gain, as.character(data_frame$Treatment), mean, na.rm=TRUE) #make sure to change 
Mean <- as.data.frame(rep(Mean, each = NumPoints))
Mean$Treatment <- rep(ActualGroupOrder, each = NumPoints) 
colnames(Mean)[1] <- "Mean"

#Stdev
Stdev <- tapply(data_frame$Gestational.Wt.Gain, as.character(data_frame$Treatment), sd, na.rm=TRUE) #make sure to change 
Stdev <- as.data.frame(rep(Stdev, each = NumPoints))
Stdev$Treatment <- rep(ActualGroupOrder, each = NumPoints)
colnames(Stdev)[1] <- "Stdev"

#Combine
dataframe_combine <- cbind(Mean, Stdev, data_frame$Gestational.Wt.Gain) #make sure to change
colnames(dataframe_combine)[5] <- "Value"
dataframe_combine <- dataframe_combine[-2]

#Error bars
dataframe_combine$Upper <- dataframe_combine$Mean + dataframe_combine$Stdev
dataframe_combine$Lower <- dataframe_combine$Mean - dataframe_combine$Stdev

#Make Graph#
png("Maternal_GestationalWeightGain_RmData2_PAExFe_Dotplot.png", units="in", width=7, height=7, res=600) 

sets <- c("MD", "PAE", "MD-Iron", "PAE-Iron")

p<- ggplot(dataframe_combine, aes(x=Treatment, y=Mean)) + 
  geom_bar(stat="identity", color="black", aes(fill = Treatment),
           position=position_dodge()) +
  scale_fill_manual(values=c("MD" = "#0000CC",
                             "PAE" = "#6699FF",
                             "MD-Iron" = "#660066",
                             "PAE-Iron" = "#9900CC"
                             )) +
  geom_errorbar(aes(ymin=Lower, ymax=Upper), width=.2,
                position=position_dodge(.9)) + 
  geom_point(aes(x=Treatment, y=Value),
             size = 1.25, shape = 19, position = position_jitter(width=.15)) +
  scale_y_continuous(expand = c(0,0), limits = c(0,150)) +
  ggtitle("Maternal Gestational Weight Gain") +
  ylab(expression("Gestational Weight Gain (g)")) + 
  theme(plot.title = element_text(hjust = 0.5, size=18), 
        axis.title.x = element_blank(), #gets rid of x-axis label
        axis.title.y = element_text(size = 16),
        panel.grid.major = element_blank(), #gets rid of major gridlines
        panel.grid.minor = element_blank(), #gets rid of minor gridlines
        panel.background = element_blank(), #turns background white instead of gray
        axis.line = element_line(colour = "black"), 
        legend.position="none", #gets rid of legend
        axis.text=element_text(size=18, color = "black"), #sets size of x and y axis labels
        axis.text.x=element_text(angle = 45, vjust = .95, hjust = 0.9),
        axis.title=element_text(size=20,face="bold")) + 
  scale_x_discrete (limits = sets)
print(p)
dev.off() 
```
```{r Gestational Weight Gain, echo = FALSE, warning = FALSE, message = FALSE}
print(p)
```

# Dosing Weight Gain (GD12.5-20.5)
```{r, echo = FALSE, warning = FALSE, message = FALSE}
#Mean
Mean <- tapply(data_frame$Dosing.Wt.Gain, as.character(data_frame$Treatment), mean, na.rm=TRUE) #make sure to change 
Mean <- as.data.frame(rep(Mean, each = NumPoints))
Mean$Treatment <- rep(ActualGroupOrder, each = NumPoints) 
colnames(Mean)[1] <- "Mean"

#Stdev
Stdev <- tapply(data_frame$Dosing.Wt.Gain, as.character(data_frame$Treatment), sd, na.rm=TRUE) #make sure to change 
Stdev <- as.data.frame(rep(Stdev, each = NumPoints))
Stdev$Treatment <- rep(ActualGroupOrder, each = NumPoints)
colnames(Stdev)[1] <- "Stdev"

#Combine
dataframe_combine <- cbind(Mean, Stdev, data_frame$Dosing.Wt.Gain) #make sure to change
colnames(dataframe_combine)[5] <- "Value"
dataframe_combine <- dataframe_combine[-2]

#Error bars
dataframe_combine$Upper <- dataframe_combine$Mean + dataframe_combine$Stdev
dataframe_combine$Lower <- dataframe_combine$Mean - dataframe_combine$Stdev

#Make Graph#
png("Maternal_DosingWeightGain_RmData2_PAExFe_Dotplot.png", units="in", width=7, height=7, res=600) 

sets <- c("MD", "PAE", "MD-Iron", "PAE-Iron")

p<- ggplot(dataframe_combine, aes(x=Treatment, y=Mean)) + 
  geom_bar(stat="identity", color="black", aes(fill = Treatment),
           position=position_dodge()) +
  scale_fill_manual(values=c("MD" = "#0000CC",
                             "PAE" = "#6699FF",
                             "MD-Iron" = "#660066",
                             "PAE-Iron" = "#9900CC"
                             )) +
  geom_errorbar(aes(ymin=Lower, ymax=Upper), width=.2,
                position=position_dodge(.9)) + 
  geom_point(aes(x=Treatment, y=Value),
             size = 1.25, shape = 19, position = position_jitter(width=.15)) +
  scale_y_continuous(expand = c(0,0), limits = c(-25,100)) +
  ggtitle("Maternal Dosing Weight Gain (GD12.5-20.5)") +
  ylab(expression("Maternal Dosing Weight Gain (g)")) + 
  theme(plot.title = element_text(hjust = 0.5, size=18), 
        axis.title.x = element_blank(), #gets rid of x-axis label
        axis.title.y = element_text(size = 16),
        panel.grid.major = element_blank(), #gets rid of major gridlines
        panel.grid.minor = element_blank(), #gets rid of minor gridlines
        panel.background = element_blank(), #turns background white instead of gray
        axis.line = element_line(colour = "black"), 
        legend.position="none", #gets rid of legend
        axis.text=element_text(size=18, color = "black"), #sets size of x and y axis labels
        axis.text.x=element_text(angle = 45, vjust = .95, hjust = 0.9),
        axis.title=element_text(size=20,face="bold")) + 
  scale_x_discrete (limits = sets)
print(p)
dev.off() 
```
```{r Maternal Dosing Weight Gain, echo = FALSE, warning = FALSE, message = FALSE}
print(p)
```

# Litter Size
```{r, echo = FALSE, warning = FALSE, message = FALSE}
#Mean
Mean <- tapply(data_frame$Litter.Size, as.character(data_frame$Treatment), mean, na.rm=TRUE) #make sure to change 
Mean <- as.data.frame(rep(Mean, each = NumPoints))
Mean$Treatment <- rep(ActualGroupOrder, each = NumPoints) 
colnames(Mean)[1] <- "Mean"

#Stdev
Stdev <- tapply(data_frame$Litter.Size, as.character(data_frame$Treatment), sd, na.rm=TRUE) #make sure to change 
Stdev <- as.data.frame(rep(Stdev, each = NumPoints))
Stdev$Treatment <- rep(ActualGroupOrder, each = NumPoints)
colnames(Stdev)[1] <- "Stdev"

#Combine
dataframe_combine <- cbind(Mean, Stdev, data_frame$Litter.Size) #make sure to change
colnames(dataframe_combine)[5] <- "Value"
dataframe_combine <- dataframe_combine[-2]

#Error bars
dataframe_combine$Upper <- dataframe_combine$Mean + dataframe_combine$Stdev
dataframe_combine$Lower <- dataframe_combine$Mean - dataframe_combine$Stdev

#Make Graph#
png("LitterSize_RmData2_PAExFe_Dotplot.png", units="in", width=7, height=7, res=600) 

sets <- c("MD", "PAE", "MD-Iron", "PAE-Iron")

p<- ggplot(dataframe_combine, aes(x=Treatment, y=Mean)) + 
  geom_bar(stat="identity", color="black", aes(fill = Treatment),
           position=position_dodge()) +
  scale_fill_manual(values=c("MD" = "#0000CC",
                             "PAE" = "#6699FF",
                             "MD-Iron" = "#660066",
                             "PAE-Iron" = "#9900CC"
                             )) +
  geom_errorbar(aes(ymin=Lower, ymax=Upper), width=.2,
                position=position_dodge(.9)) + 
  geom_point(aes(x=Treatment, y=Value),
             size = 1.25, shape = 19, position = position_jitter(width=.15)) +
  scale_y_continuous(expand = c(0,0), limits = c(0,15)) +
  ggtitle("Litter Size") +
  ylab(expression("Litter Size (n)")) + 
  theme(plot.title = element_text(hjust = 0.5, size=18), 
        axis.title.x = element_blank(), #gets rid of x-axis label
        axis.title.y = element_text(size = 16),
        panel.grid.major = element_blank(), #gets rid of major gridlines
        panel.grid.minor = element_blank(), #gets rid of minor gridlines
        panel.background = element_blank(), #turns background white instead of gray
        axis.line = element_line(colour = "black"), 
        legend.position="none", #gets rid of legend
        axis.text=element_text(size=18, color = "black"), #sets size of x and y axis labels
        axis.text.x=element_text(angle = 45, vjust = .95, hjust = 0.9),
        axis.title=element_text(size=20,face="bold")) + 
  scale_x_discrete (limits = sets)
print(p)
dev.off() 
```
```{r Litter Size, echo = FALSE, warning = FALSE, message = FALSE}
print(p)
```

# Percent Survival
```{r, echo = FALSE, warning = FALSE, message = FALSE}
#Mean
Mean <- tapply(data_frame$Percent.survival, as.character(data_frame$Treatment), mean, na.rm=TRUE) #make sure to change 
Mean <- as.data.frame(rep(Mean, each = NumPoints))
Mean$Treatment <- rep(ActualGroupOrder, each = NumPoints) 
colnames(Mean)[1] <- "Mean"

#Stdev
Stdev <- tapply(data_frame$Percent.survival, as.character(data_frame$Treatment), sd, na.rm=TRUE) #make sure to change 
Stdev <- as.data.frame(rep(Stdev, each = NumPoints))
Stdev$Treatment <- rep(ActualGroupOrder, each = NumPoints)
colnames(Stdev)[1] <- "Stdev"

#Combine
dataframe_combine <- cbind(Mean, Stdev, data_frame$Percent.survival) #make sure to change
colnames(dataframe_combine)[5] <- "Value"
dataframe_combine <- dataframe_combine[-2]

#Error bars
dataframe_combine$Upper <- dataframe_combine$Mean + dataframe_combine$Stdev
dataframe_combine$Lower <- dataframe_combine$Mean - dataframe_combine$Stdev

#Change to percent
dataframe_combine$Mean <- dataframe_combine$Mean * 100
dataframe_combine$Stdev <- dataframe_combine$Stdev * 100
dataframe_combine$Value <- dataframe_combine$Value * 100
dataframe_combine$Upper <- dataframe_combine$Upper * 100
dataframe_combine$Lower <- dataframe_combine$Lower * 100

#Make Graph#
png("PercentSurvival_RmData2_PAExFe_Dotplot.png", units="in", width=7, height=7, res=600) 

sets <- c("MD", "PAE", "MD-Iron", "PAE-Iron")

p<- ggplot(dataframe_combine, aes(x=Treatment, y=Mean)) + 
  geom_bar(stat="identity", color="black", aes(fill = Treatment),
           position=position_dodge()) +
  scale_fill_manual(values=c("MD" = "#0000CC",
                             "PAE" = "#6699FF",
                             "MD-Iron" = "#660066",
                             "PAE-Iron" = "#9900CC"
                             )) +
  geom_errorbar(aes(ymin=Lower, ymax=Upper), width=.2,
                position=position_dodge(.9)) + 
  geom_point(aes(x=Treatment, y=Value),
             size = 1.25, shape = 19, position = position_jitter(width=.15)) +
  scale_y_continuous(expand = c(0,0), limits = c(0,125)) +
  ggtitle("Percent Litter Survival") +
  ylab(expression("Percent Survival (%)")) + 
  theme(plot.title = element_text(hjust = 0.5, size=18), 
        axis.title.x = element_blank(), #gets rid of x-axis label
        axis.title.y = element_text(size = 16),
        panel.grid.major = element_blank(), #gets rid of major gridlines
        panel.grid.minor = element_blank(), #gets rid of minor gridlines
        panel.background = element_blank(), #turns background white instead of gray
        axis.line = element_line(colour = "black"), 
        legend.position="none", #gets rid of legend
        axis.text=element_text(size=18, color = "black"), #sets size of x and y axis labels
        axis.text.x=element_text(angle = 45, vjust = .95, hjust = 0.9),
        axis.title=element_text(size=20,face="bold")) + 
  scale_x_discrete (limits = sets)
print(p)
dev.off() 
```
```{r Percent Litter Survival, echo = FALSE, warning = FALSE, message = FALSE}
print(p)
```

# Percent Male 
```{r, echo = FALSE, warning = FALSE, message = FALSE}
#Mean
Mean <- tapply(data_frame$Percent.Male, as.character(data_frame$Treatment), mean, na.rm=TRUE) #make sure to change 
Mean <- as.data.frame(rep(Mean, each = NumPoints))
Mean$Treatment <- rep(ActualGroupOrder, each = NumPoints) 
colnames(Mean)[1] <- "Mean"

#Stdev
Stdev <- tapply(data_frame$Percent.Male, as.character(data_frame$Treatment), sd, na.rm=TRUE) #make sure to change 
Stdev <- as.data.frame(rep(Stdev, each = NumPoints))
Stdev$Treatment <- rep(ActualGroupOrder, each = NumPoints)
colnames(Stdev)[1] <- "Stdev"

#Combine
dataframe_combine <- cbind(Mean, Stdev, data_frame$Percent.Male) #make sure to change
colnames(dataframe_combine)[5] <- "Value"
dataframe_combine <- dataframe_combine[-2]

#Error bars
dataframe_combine$Upper <- dataframe_combine$Mean + dataframe_combine$Stdev
dataframe_combine$Lower <- dataframe_combine$Mean - dataframe_combine$Stdev

#Change to percent
dataframe_combine$Mean <- dataframe_combine$Mean * 100
dataframe_combine$Stdev <- dataframe_combine$Stdev * 100
dataframe_combine$Value <- dataframe_combine$Value * 100
dataframe_combine$Upper <- dataframe_combine$Upper * 100
dataframe_combine$Lower <- dataframe_combine$Lower * 100

#Make Graph#
png("PercentMale_RmData2_PAExFe_Dotplot.png", units="in", width=7, height=7, res=600) 

sets <- c("MD", "PAE", "MD-Iron", "PAE-Iron")

p<- ggplot(dataframe_combine, aes(x=Treatment, y=Mean)) + 
  geom_bar(stat="identity", color="black", aes(fill = Treatment),
           position=position_dodge()) +
  scale_fill_manual(values=c("MD" = "#0000CC",
                             "PAE" = "#6699FF",
                             "MD-Iron" = "#660066",
                             "PAE-Iron" = "#9900CC"
                             )) +
  geom_errorbar(aes(ymin=Lower, ymax=Upper), width=.2,
                position=position_dodge(.9)) + 
  geom_point(aes(x=Treatment, y=Value),
             size = 1.25, shape = 19, position = position_jitter(width=.15)) +
  scale_y_continuous(expand = c(0,0), limits = c(0,100)) +
  ggtitle("Percent of Litter That Is Male") +
  ylab(expression("Percent Male (%)")) + 
  theme(plot.title = element_text(hjust = 0.5, size=18), 
        axis.title.x = element_blank(), #gets rid of x-axis label
        axis.title.y = element_text(size = 16),
        panel.grid.major = element_blank(), #gets rid of major gridlines
        panel.grid.minor = element_blank(), #gets rid of minor gridlines
        panel.background = element_blank(), #turns background white instead of gray
        axis.line = element_line(colour = "black"), 
        legend.position="none", #gets rid of legend
        axis.text=element_text(size=18, color = "black"), #sets size of x and y axis labels
        axis.text.x=element_text(angle = 45, vjust = .95, hjust = 0.9),
        axis.title=element_text(size=20,face="bold")) + 
  scale_x_discrete (limits = sets)
print(p)
dev.off() 
```
```{r Percent Male, echo = FALSE, warning = FALSE, message = FALSE}
print(p)
```

# Non-pregnancy weight
```{r, echo = FALSE, warning = FALSE, message = FALSE}
#Mean
Mean <- tapply(data_frame$Non.pregnancy.weight, as.character(data_frame$Treatment), mean, na.rm=TRUE) #make sure to change 
Mean <- as.data.frame(rep(Mean, each = NumPoints))
Mean$Treatment <- rep(ActualGroupOrder, each = NumPoints) 
colnames(Mean)[1] <- "Mean"

#Stdev
Stdev <- tapply(data_frame$Non.pregnancy.weight, as.character(data_frame$Treatment), sd, na.rm=TRUE) #make sure to change 
Stdev <- as.data.frame(rep(Stdev, each = NumPoints))
Stdev$Treatment <- rep(ActualGroupOrder, each = NumPoints)
colnames(Stdev)[1] <- "Stdev"

#Combine
dataframe_combine <- cbind(Mean, Stdev, data_frame$Non.pregnancy.weight) #make sure to change
colnames(dataframe_combine)[5] <- "Value"
dataframe_combine <- dataframe_combine[-2]

#Error bars
dataframe_combine$Upper <- dataframe_combine$Mean + dataframe_combine$Stdev
dataframe_combine$Lower <- dataframe_combine$Mean - dataframe_combine$Stdev

#Make Graph#
png("Maternal_NonpregnancyWeight_RmData2_PAExFe_Dotplot.png", units="in", width=7, height=7, res=600) 

sets <- c("MD", "PAE", "MD-Iron", "PAE-Iron")

p<- ggplot(dataframe_combine, aes(x=Treatment, y=Mean)) + 
  geom_bar(stat="identity", color="black", aes(fill = Treatment),
           position=position_dodge()) +
  scale_fill_manual(values=c("MD" = "#0000CC",
                             "PAE" = "#6699FF",
                             "MD-Iron" = "#660066",
                             "PAE-Iron" = "#9900CC"
                             )) +
  geom_errorbar(aes(ymin=Lower, ymax=Upper), width=.2,
                position=position_dodge(.9)) + 
  geom_point(aes(x=Treatment, y=Value),
             size = 1.25, shape = 19, position = position_jitter(width=.15)) +
  scale_y_continuous(expand = c(0,0), limits = c(0,350)) +
  ggtitle("Maternal Non-pregnancy Weight") +
  ylab(expression("Maternal Nonpregnancy Weight (g)")) + 
  theme(plot.title = element_text(hjust = 0.5, size=18), 
        axis.title.x = element_blank(), #gets rid of x-axis label
        axis.title.y = element_text(size = 16),
        panel.grid.major = element_blank(), #gets rid of major gridlines
        panel.grid.minor = element_blank(), #gets rid of minor gridlines
        panel.background = element_blank(), #turns background white instead of gray
        axis.line = element_line(colour = "black"), 
        legend.position="none", #gets rid of legend
        axis.text=element_text(size=18, color = "black"), #sets size of x and y axis labels
        axis.text.x=element_text(angle = 45, vjust = .95, hjust = 0.9),
        axis.title=element_text(size=20,face="bold")) + 
  scale_x_discrete (limits = sets)
print(p)
dev.off() 
```
```{r Maternal Non-pregnancy Weight, echo = FALSE, warning = FALSE, message = FALSE}
print(p)
```

# Uterine Horn Weight
```{r, echo = FALSE, warning = FALSE, message = FALSE}
#Mean
Mean <- tapply(data_frame$Uterine.Horn.Weight, as.character(data_frame$Treatment), mean, na.rm=TRUE) #make sure to change 
Mean <- as.data.frame(rep(Mean, each = NumPoints))
Mean$Treatment <- rep(ActualGroupOrder, each = NumPoints) 
colnames(Mean)[1] <- "Mean"

#Stdev
Stdev <- tapply(data_frame$Uterine.Horn.Weight, as.character(data_frame$Treatment), sd, na.rm=TRUE) #make sure to change 
Stdev <- as.data.frame(rep(Stdev, each = NumPoints))
Stdev$Treatment <- rep(ActualGroupOrder, each = NumPoints)
colnames(Stdev)[1] <- "Stdev"

#Combine
dataframe_combine <- cbind(Mean, Stdev, data_frame$Uterine.Horn.Weight) #make sure to change
colnames(dataframe_combine)[5] <- "Value"
dataframe_combine <- dataframe_combine[-2]

#Error bars
dataframe_combine$Upper <- dataframe_combine$Mean + dataframe_combine$Stdev
dataframe_combine$Lower <- dataframe_combine$Mean - dataframe_combine$Stdev

#Make Graph#
png("UterineHornWeight_RmData2_PAExFe_Dotplot.png", units="in", width=7, height=7, res=600) 

sets <- c("MD", "PAE", "MD-Iron", "PAE-Iron")

p<- ggplot(dataframe_combine, aes(x=Treatment, y=Mean)) + 
  geom_bar(stat="identity", color="black", aes(fill = Treatment),
           position=position_dodge()) +
  scale_fill_manual(values=c("MD" = "#0000CC",
                             "PAE" = "#6699FF",
                             "MD-Iron" = "#660066",
                             "PAE-Iron" = "#9900CC"
                             )) +
  geom_errorbar(aes(ymin=Lower, ymax=Upper), width=.2,
                position=position_dodge(.9)) + 
  geom_point(aes(x=Treatment, y=Value),
             size = 1.25, shape = 19, position = position_jitter(width=.15)) +
  scale_y_continuous(expand = c(0,0), limits = c(0,80)) +
  ggtitle("Uterine Horn Weight") +
  ylab(expression("Uterine Horn Weight (g)")) + 
  theme(plot.title = element_text(hjust = 0.5, size=18), 
        axis.title.x = element_blank(), #gets rid of x-axis label
        axis.title.y = element_text(size = 16),
        panel.grid.major = element_blank(), #gets rid of major gridlines
        panel.grid.minor = element_blank(), #gets rid of minor gridlines
        panel.background = element_blank(), #turns background white instead of gray
        axis.line = element_line(colour = "black"), 
        legend.position="none", #gets rid of legend
        axis.text=element_text(size=18, color = "black"), #sets size of x and y axis labels
        axis.text.x=element_text(angle = 45, vjust = .95, hjust = 0.9),
        axis.title=element_text(size=20,face="bold")) + 
  scale_x_discrete (limits = sets)
print(p)
dev.off() 
```
```{r Uterine Horn Weight, echo = FALSE, warning = FALSE, message = FALSE}
print(p)
```

# Uterine Weight Per Fetus
```{r, echo = FALSE, warning = FALSE, message = FALSE}
#Mean
Mean <- tapply(data_frame$Uterine.Weight.per.Fetus, as.character(data_frame$Treatment), mean, na.rm=TRUE) #make sure to change 
Mean <- as.data.frame(rep(Mean, each = NumPoints))
Mean$Treatment <- rep(ActualGroupOrder, each = NumPoints) 
colnames(Mean)[1] <- "Mean"

#Stdev
Stdev <- tapply(data_frame$Uterine.Weight.per.Fetus, as.character(data_frame$Treatment), sd, na.rm=TRUE) #make sure to change 
Stdev <- as.data.frame(rep(Stdev, each = NumPoints))
Stdev$Treatment <- rep(ActualGroupOrder, each = NumPoints)
colnames(Stdev)[1] <- "Stdev"

#Combine
dataframe_combine <- cbind(Mean, Stdev, data_frame$Uterine.Weight.per.Fetus) #make sure to change
colnames(dataframe_combine)[5] <- "Value"
dataframe_combine <- dataframe_combine[-2]

#Error bars
dataframe_combine$Upper <- dataframe_combine$Mean + dataframe_combine$Stdev
dataframe_combine$Lower <- dataframe_combine$Mean - dataframe_combine$Stdev

#Make Graph#
png("UterineWeightPerFetus_RmData2_PAExFe_Dotplot.png", units="in", width=7, height=7, res=600) 

sets <- c("MD", "PAE", "MD-Iron", "PAE-Iron")

p<- ggplot(dataframe_combine, aes(x=Treatment, y=Mean)) + 
  geom_bar(stat="identity", color="black", aes(fill = Treatment),
           position=position_dodge()) +
  scale_fill_manual(values=c("MD" = "#0000CC",
                             "PAE" = "#6699FF",
                             "MD-Iron" = "#660066",
                             "PAE-Iron" = "#9900CC"
                             )) +
  geom_errorbar(aes(ymin=Lower, ymax=Upper), width=.2,
                position=position_dodge(.9)) + 
  geom_point(aes(x=Treatment, y=Value),
             size = 1.25, shape = 19, position = position_jitter(width=.15)) +
  scale_y_continuous(expand = c(0,0), limits = c(0,8)) +
  ggtitle("Uterine Weight Per Fetus") +
  ylab(expression("Uterine Weight Per Fetus (g)")) + 
  theme(plot.title = element_text(hjust = 0.5, size=18), 
        axis.title.x = element_blank(), #gets rid of x-axis label
        axis.title.y = element_text(size = 16),
        panel.grid.major = element_blank(), #gets rid of major gridlines
        panel.grid.minor = element_blank(), #gets rid of minor gridlines
        panel.background = element_blank(), #turns background white instead of gray
        axis.line = element_line(colour = "black"), 
        legend.position="none", #gets rid of legend
        axis.text=element_text(size=18, color = "black"), #sets size of x and y axis labels
        axis.text.x=element_text(angle = 45, vjust = .95, hjust = 0.9),
        axis.title=element_text(size=20,face="bold")) + 
  scale_x_discrete (limits = sets)
print(p)
dev.off() 
```
```{r Uterine Weight Per Fetus, echo = FALSE, warning = FALSE, message = FALSE}
print(p)
```

# Maternal Spleen Weight
```{r, echo = FALSE, warning = FALSE, message = FALSE}
#Mean
Mean <- tapply(data_frame$Maternal.Spleen..g., as.character(data_frame$Treatment), mean, na.rm=TRUE) #make sure to change 
Mean <- as.data.frame(rep(Mean, each = NumPoints))
Mean$Treatment <- rep(ActualGroupOrder, each = NumPoints) 
colnames(Mean)[1] <- "Mean"

#Stdev
Stdev <- tapply(data_frame$Maternal.Spleen..g., as.character(data_frame$Treatment), sd, na.rm=TRUE) #make sure to change 
Stdev <- as.data.frame(rep(Stdev, each = NumPoints))
Stdev$Treatment <- rep(ActualGroupOrder, each = NumPoints)
colnames(Stdev)[1] <- "Stdev"

#Combine
dataframe_combine <- cbind(Mean, Stdev, data_frame$Maternal.Spleen..g.) #make sure to change
colnames(dataframe_combine)[5] <- "Value"
dataframe_combine <- dataframe_combine[-2]

#Error bars
dataframe_combine$Upper <- dataframe_combine$Mean + dataframe_combine$Stdev
dataframe_combine$Lower <- dataframe_combine$Mean - dataframe_combine$Stdev

#Make Graph#
png("Maternal_SpleenWeight_RmData2_PAExFe_Dotplot.png", units="in", width=7, height=7, res=600) 

sets <- c("MD", "PAE", "MD-Iron", "PAE-Iron")

p<- ggplot(dataframe_combine, aes(x=Treatment, y=Mean)) + 
  geom_bar(stat="identity", color="black", aes(fill = Treatment),
           position=position_dodge()) +
  scale_fill_manual(values=c("MD" = "#0000CC",
                             "PAE" = "#6699FF",
                             "MD-Iron" = "#660066",
                             "PAE-Iron" = "#9900CC"
                             )) +
  geom_errorbar(aes(ymin=Lower, ymax=Upper), width=.2,
                position=position_dodge(.9)) + 
  geom_point(aes(x=Treatment, y=Value),
             size = 1.25, shape = 19, position = position_jitter(width=.15)) +
  scale_y_continuous(expand = c(0,0), limits = c(0,1)) +
  ggtitle("Maternal Spleen Weight") +
  ylab(expression("Maternal Spleen Weight (g)")) + 
  theme(plot.title = element_text(hjust = 0.5, size=18), 
        axis.title.x = element_blank(), #gets rid of x-axis label
        axis.title.y = element_text(size = 16),
        panel.grid.major = element_blank(), #gets rid of major gridlines
        panel.grid.minor = element_blank(), #gets rid of minor gridlines
        panel.background = element_blank(), #turns background white instead of gray
        axis.line = element_line(colour = "black"), 
        legend.position="none", #gets rid of legend
        axis.text=element_text(size=18, color = "black"), #sets size of x and y axis labels
        axis.text.x=element_text(angle = 45, vjust = .95, hjust = 0.9),
        axis.title=element_text(size=20,face="bold")) + 
  scale_x_discrete (limits = sets)
print(p)
dev.off() 
```
```{r Maternal Spleen Weight, echo = FALSE, warning = FALSE, message = FALSE}
print(p)
```

# Maternal Kidney Weight
```{r, echo = FALSE, warning = FALSE, message = FALSE}
#Mean
Mean <- tapply(data_frame$Maternal.Kidney..g., as.character(data_frame$Treatment), mean, na.rm=TRUE) #make sure to change 
Mean <- as.data.frame(rep(Mean, each = NumPoints))
Mean$Treatment <- rep(ActualGroupOrder, each = NumPoints) 
colnames(Mean)[1] <- "Mean"

#Stdev
Stdev <- tapply(data_frame$Maternal.Kidney..g., as.character(data_frame$Treatment), sd, na.rm=TRUE) #make sure to change 
Stdev <- as.data.frame(rep(Stdev, each = NumPoints))
Stdev$Treatment <- rep(ActualGroupOrder, each = NumPoints)
colnames(Stdev)[1] <- "Stdev"

#Combine
dataframe_combine <- cbind(Mean, Stdev, data_frame$Maternal.Kidney..g.) #make sure to change
colnames(dataframe_combine)[5] <- "Value"
dataframe_combine <- dataframe_combine[-2]

#Error bars
dataframe_combine$Upper <- dataframe_combine$Mean + dataframe_combine$Stdev
dataframe_combine$Lower <- dataframe_combine$Mean - dataframe_combine$Stdev

#Make Graph#
png("Maternal_KidneyWeight_RmData2_PAExFe_Dotplot.png", units="in", width=7, height=7, res=600) 

sets <- c("MD", "PAE", "MD-Iron", "PAE-Iron")

p<- ggplot(dataframe_combine, aes(x=Treatment, y=Mean)) + 
  geom_bar(stat="identity", color="black", aes(fill = Treatment),
           position=position_dodge()) +
  scale_fill_manual(values=c("MD" = "#0000CC",
                             "PAE" = "#6699FF",
                             "MD-Iron" = "#660066",
                             "PAE-Iron" = "#9900CC"
                             )) +
  geom_errorbar(aes(ymin=Lower, ymax=Upper), width=.2,
                position=position_dodge(.9)) + 
  geom_point(aes(x=Treatment, y=Value),
             size = 1.25, shape = 19, position = position_jitter(width=.15)) +
  scale_y_continuous(expand = c(0,0), limits = c(0,3)) +
  ggtitle("Maternal Kidney Weight") +
  ylab(expression("Maternal Kidney Weight (g)")) + 
  theme(plot.title = element_text(hjust = 0.5, size=18), 
        axis.title.x = element_blank(), #gets rid of x-axis label
        axis.title.y = element_text(size = 16),
        panel.grid.major = element_blank(), #gets rid of major gridlines
        panel.grid.minor = element_blank(), #gets rid of minor gridlines
        panel.background = element_blank(), #turns background white instead of gray
        axis.line = element_line(colour = "black"), 
        legend.position="none", #gets rid of legend
        axis.text=element_text(size=18, color = "black"), #sets size of x and y axis labels
        axis.text.x=element_text(angle = 45, vjust = .95, hjust = 0.9),
        axis.title=element_text(size=20,face="bold")) + 
  scale_x_discrete (limits = sets)
print(p)
dev.off() 
```
```{r Maternal Kidney Weight, echo = FALSE, warning = FALSE, message = FALSE}
print(p)
```

# Session Information
```{r, echo = FALSE}
session_info <- devtools::session_info()
print(session_info)
```