---
title: "Fetal Rat Anthropometry at Collection GD20.5, AIN-76A diet with MD or Alcohol and Iron Supplement or Water- 2 Small Litters Removed"
author: "Kaylee Helfrich"
date: "9/16/20"
output: 
  pdf_document: default
  html_document: default
data: "Fetal_Rat_Anthropometry_Nov-Dec2019_withSex_RmData2.csv"
---

Built with R `r getRversion()`

```{r RMarkdown setup, include = FALSE, message = FALSE}
require(knitr)
knitr::opts_chunk$set(echo = TRUE, tidy.opts=list(width.cutoff=60), tidy=TRUE)
knitr::opts_knit$set(root.dir = "~/KayleeStuff/Smith_Lab/Data/Rat_Iron/Fetal_Anthro/RmData2")
options(tinytex.verbose = TRUE)
```

# Graphing Fetal Rat Anthropometry- Data from two small litters and individual data outliers removed
This document details my graphing of the anthropometry data from fetal rats at tissue collection on GD20.5, including fetal weight, placental weight, placental efficiency, brain weight, brain to body weight ratio, liver weight, liver to body weight ratio, ratio of brain to liver weight, heart weight, and ratio of heart to body weight. This analysis uses the data that was collected on the fetuses in this study, excluding samples from fetuses from litters that were more than 2 standard deviations (SD = 3) from the mean (Mean = 10), including 2 litters with only 2 fetuses each (R029-MD+H2O and R031-MD+Fe). Also, data from 4 underdeveloped fetuses from MD+H2O litter R054 (4,6,8,9) were removed. Finally, the following individual data points were removed as the data were statistical outliers via Grubb's test- placental weight (R015-2), placental efficiency (R015-2), brain weight (R043-13), ratio brain to body weight (R043-13), liver weight (R042-11, R011-6), ratio liver to body weight (R010-4, R042-11, R011-6), ratio brain to liver weight (R010-4, R043-13, R042-11, R032-4, R011-6, R026-10), and ratio of heart to body weight (R010-5, R030-6, R027-1). All samples were collected between 11/2019-12/2019 by Kaylee Helfrich, Olivia Rivera, Nipun Saini, and Cecilia Kwan. Female Long-Evans rats arrived at 7 weeks old and were mated at 9-11 weeks of age. The dams were dosed with 5g/kg ethanol or isocaloric maltodextrin from GD13.5-19.5. The dams also received either an iron supplement (6g/kg, Fer-In-Sol) or the same volume of water as a gavage from GD12.5-GD19.5. All dams consumed AIN-76G diet modified to contain 100ppm of iron from arrival through pregnancy. Tissues were harvested on GD20.5. All graphs are mean with standard deviation, since there are not multiple measures per sample. This analysis will allow us to compare the 4 groups. Statistical analysis in JMP will use ANOVA, following checks for normality and variance, to assign significance to the measures. 

```{r include = FALSE}
rm(list=ls())
setwd("~/KayleeStuff/Smith_Lab/Data/Rat_Iron/Fetal_Anthro/RmData2")
library(ggplot2)
library(plotrix)
library(dplyr)
```

```{r Import file and rearrange by treatment to be alphabetical}
File <- "Fetal_Rat_Anthropometry_Nov-Dec2019_withSex_RmData2.csv"
data <- read.csv(File, header=TRUE) 
data_frame <- data.frame(data)
data_frame <- data_frame[order(data_frame$Treatment), ]
```
```{r echo = FALSE}
print(data_frame)
```
```{r Prepare data for graphing}
ActualGroupOrder <- c("PAE-Iron", "PAE","MD-Iron", "MD")
```

# Equalize Row Number by Treatment
```{r}
#Figure out how many rows of empty NA's are needed to equalize the treatment groups
Groupcount <- data_frame %>% count(Treatment) #Calculate how many individuals there are per treatment group
NumPoints <- max(Groupcount$n) #Create the variable "NumPoints" to count the # of points in the final graphs
DiffFunc <- function(x) NumPoints - x #Create the function "DiffFunc" to calculate the number of NA rows to be added
DiffPoints <- as.data.frame(tapply(Groupcount$n, as.character(Groupcount$Treatment), DiffFunc)) #Calculate number of NA rows to be added to each treatment group
DiffPoints$Treatment <- ActualGroupOrder #add new column so that the # of points to be added is assigned to the treatment
colnames(DiffPoints)[1] <- "NumberN" #rename column
Nrow <- sum(DiffPoints$NumberN) #figure out how many total rows will be added to the DF_extra dataframe
AlcFe <- DiffPoints[1,1] #for each of these, it is creating a variable for the "vector" below
AlcH2O <- DiffPoints[2,1]
MDFe <- DiffPoints[3,1]
MDH2O <- DiffPoints[4,1]

#Add extra rows of NAs to equalize groups
DF_extra <- data.frame(matrix(NA, nrow = Nrow, ncol = 16)) #create an empty dataframe filled with NA's
vector <- rep(c("Alc+Fe", "Alc+H2O", "MD+Fe", "MD+H2O"), times = c(AlcFe, AlcH2O, MDFe, MDH2O)) #create the vector to add the treatment groups to the NA matrix
DF_extra$Treatment <- vector #add in the Treatment column to the DF_extra dataframe
DF_extra <- DF_extra[,c(1:2,17,3:16)] #rearrange the columns so that they are in the same order as the original DF
DF_extra <- setNames(DF_extra, names(data_frame)) #set the names of the new df to match the original df
DF_new <- rbind(data_frame, DF_extra) #Rbind the 2 dataframes so that we now have equal treatment group sizes
print(DF_new %>% count(Treatment)) #check that the groups are now equal
#rearrange to be in order of Treatment, otherwise the dots get accidentally reassigned to the wrong group
DF_new <- DF_new[order(DF_new$Treatment), ]
```

# Fetal Weight

## All code is included for this first example, but thereafter, only the heading and graphs are shown. For all graphs, all data is graphed unless mentioned otherwise. Messages and warnings are excluded, since NA's were included to make all groups even, and I didn't want the code to print out these errors when they weren't necessary.
```{r, warning = FALSE, message = FALSE}
#Mean- calculate mean for column, repeat it to number of points, and create dataframe
Mean <- tapply(DF_new$Fetal.Wt, as.character(DF_new$Treatment), mean, na.rm=TRUE) #make sure to change selected column to change data for graph
Mean <- as.data.frame(rep(Mean, each = NumPoints)) #repeat mean a set number of times
Mean$Treatment <- rep(ActualGroupOrder, each = NumPoints) #repeat treatment a set number of times
colnames(Mean)[1] <- "Mean" #fix column name

#Stdev- calculate standard deviation for column, repeat it to number of points, and create dataframe
Stdev <- tapply(DF_new$Fetal.Wt, as.character(DF_new$Treatment), sd, na.rm=TRUE) #make sure to change selected column
Stdev <- as.data.frame(rep(Stdev, each = NumPoints)) #repeat stdev a set number of times
Stdev$Treatment <- rep(ActualGroupOrder, each = NumPoints) #repeat treatment a set number of times
colnames(Stdev)[1] <- "Stdev" #fix column name

#Combine mean, standard deviation, and individual data points
dataframe_combine <- cbind(Mean, Stdev, DF_new$Fetal.Wt) #make sure to change selected column
colnames(dataframe_combine)[5] <- "Value" #Fix name of individual data point column
dataframe_combine <- dataframe_combine[-2] #Remove extra treatment column

#Error bars
dataframe_combine$Upper <- dataframe_combine$Mean + dataframe_combine$Stdev #upper error
dataframe_combine$Lower <- dataframe_combine$Mean - dataframe_combine$Stdev #lower error

#Make Graph#
png("FetalWeight_RmData2_PAExFe_Dotplot.png", units="in", width=7, height=7, res=600) 

sets <- c("MD", "PAE", "MD-Iron", "PAE-Iron")

p<- ggplot(dataframe_combine, aes(x=Treatment, y=Mean)) + 
  geom_bar(stat="identity", color="black", aes(fill = Treatment),
           position=position_dodge()) +
  scale_fill_manual(values=c("MD" = "#0000CC",
                             "PAE" = "#6699FF",
                             "MD-Iron" = "#660066",
                             "PAE-Iron" = "#9900CC"
                             )) +
  geom_errorbar(aes(ymin=Lower, ymax=Upper), width=.2,
                position=position_dodge(.9)) + 
  geom_point(aes(x=Treatment, y=Value),
             size = 1.25, shape = 19, alpha = 0.3, position = position_jitter(width=.15)) +
  scale_y_continuous(expand = c(0,0), limits = c(0,5)) +
  ggtitle("Fetal Weight- Males and Females") +
  ylab(expression("Fetal Weight (g)")) + 
  theme(plot.title = element_text(hjust = 0.5, size=18), 
        axis.title.x = element_blank(), #gets rid of x-axis label
        axis.title.y = element_text(size = 16),
        panel.grid.major = element_blank(), #gets rid of major gridlines
        panel.grid.minor = element_blank(), #gets rid of minor gridlines
        panel.background = element_blank(), #turns background white instead of gray
        axis.line = element_line(colour = "black"), 
        legend.position="none", #gets rid of legend
        axis.text=element_text(size=18, color = "black"), #sets size of x and y axis labels
        axis.text.x=element_text(),
        axis.title=element_text(size=20,face="bold")) + 
  scale_x_discrete (limits = sets)
print(p)
dev.off() 
```
```{r Fetal Weight, echo = FALSE}
print(p)
```

# Placental Weight
```{r, echo = FALSE, warning = FALSE, message = FALSE}
#Mean
Mean <- tapply(DF_new$Placental.Wt, as.character(DF_new$Treatment), mean, na.rm=TRUE) #make sure to change 
Mean <- as.data.frame(rep(Mean, each = NumPoints))
Mean$Treatment <- rep(ActualGroupOrder, each = NumPoints) 
colnames(Mean)[1] <- "Mean"

#Stdev
Stdev <- tapply(DF_new$Placental.Wt, as.character(DF_new$Treatment), sd, na.rm=TRUE) #make sure to change 
Stdev <- as.data.frame(rep(Stdev, each = NumPoints))
Stdev$Treatment <- rep(ActualGroupOrder, each = NumPoints)
colnames(Stdev)[1] <- "Stdev"

#Combine
dataframe_combine <- cbind(Mean, Stdev, DF_new$Placental.Wt) #make sure to change
colnames(dataframe_combine)[5] <- "Value"
dataframe_combine <- dataframe_combine[-2]

#Error bars
dataframe_combine$Upper <- dataframe_combine$Mean + dataframe_combine$Stdev
dataframe_combine$Lower <- dataframe_combine$Mean - dataframe_combine$Stdev

#Make Graph#
png("PlacentalWeight_RmData2_PAExFe_Dotplot.png", units="in", width=7, height=7, res=600) 

sets <- c("MD", "PAE", "MD-Iron", "PAE-Iron")

p<- ggplot(dataframe_combine, aes(x=Treatment, y=Mean)) + 
  geom_bar(stat="identity", color="black", aes(fill = Treatment),
           position=position_dodge()) +
  scale_fill_manual(values=c("MD" = "#0000CC",
                             "PAE" = "#6699FF",
                             "MD-Iron" = "#660066",
                             "PAE-Iron" = "#9900CC"
                             )) +
  geom_errorbar(aes(ymin=Lower, ymax=Upper), width=.2,
                position=position_dodge(.9)) + 
  geom_point(aes(x=Treatment, y=Value),
             size = 1.25, shape = 19, alpha = 0.3, position = position_jitter(width=.15)) +
  scale_y_continuous(expand = c(0,0), limits = c(0,0.62)) +
  ggtitle("Placental Weight- Males and Females") +
  ylab(expression("Placental Weight (g)")) + 
  theme(plot.title = element_text(hjust = 0.5, size=18), 
        axis.title.x = element_blank(), #gets rid of x-axis label
        axis.title.y = element_text(size = 16),
        panel.grid.major = element_blank(), #gets rid of major gridlines
        panel.grid.minor = element_blank(), #gets rid of minor gridlines
        panel.background = element_blank(), #turns background white instead of gray
        axis.line = element_line(colour = "black"), 
        legend.position="none", #gets rid of legend
        axis.text=element_text(size=18, color = "black"), #sets size of x and y axis labels
        axis.text.x=element_text(),
        axis.title=element_text(size=20,face="bold")) + 
  scale_x_discrete (limits = sets)
print(p)
dev.off() 
```
```{r Placental Weight, echo = FALSE, warning = FALSE, message = FALSE}
print(p)
```

# Placental Efficiency
```{r, echo = FALSE, warning = FALSE, message = FALSE}
#Mean
Mean <- tapply(DF_new$Placental.Efficiency, as.character(DF_new$Treatment), mean, na.rm=TRUE) #change 
Mean <- as.data.frame(rep(Mean, each = NumPoints))
Mean$Treatment <- rep(ActualGroupOrder, each = NumPoints) 
colnames(Mean)[1] <- "Mean"

#Stdev
Stdev <- tapply(DF_new$Placental.Efficiency, as.character(DF_new$Treatment), sd, na.rm=TRUE) #change 
Stdev <- as.data.frame(rep(Stdev, each = NumPoints))
Stdev$Treatment <- rep(ActualGroupOrder, each = NumPoints)
colnames(Stdev)[1] <- "Stdev"

#Combine
dataframe_combine <- cbind(Mean, Stdev, DF_new$Placental.Efficiency) #make sure to change
colnames(dataframe_combine)[5] <- "Value"
dataframe_combine <- dataframe_combine[-2]

#Error bars
dataframe_combine$Upper <- dataframe_combine$Mean + dataframe_combine$Stdev
dataframe_combine$Lower <- dataframe_combine$Mean - dataframe_combine$Stdev

#Make Graph#
png("PlacentalEfficiency_RmData2_PAExFe_Dotplot.png", units="in", width=7, height=7, res=600) 

sets <- c("MD", "PAE", "MD-Iron", "PAE-Iron")

p<- ggplot(dataframe_combine, aes(x=Treatment, y=Mean)) + 
  geom_bar(stat="identity", color="black", aes(fill = Treatment),
           position=position_dodge()) +
  scale_fill_manual(values=c("MD" = "#0000CC",
                             "PAE" = "#6699FF",
                             "MD-Iron" = "#660066",
                             "PAE-Iron" = "#9900CC"
                             )) +
  geom_errorbar(aes(ymin=Lower, ymax=Upper), width=.2,
                position=position_dodge(.9)) + 
  geom_point(aes(x=Treatment, y=Value),
             size = 1.25, shape = 19, alpha = 0.3, position = position_jitter(width=.15)) +
  scale_y_continuous(expand = c(0,0), limits = c(0,15)) +
  ggtitle("Placental Efficiency- Males and Females") +
  ylab(expression("Placental Efficiency (Fetal Weight/Placental Weight) ")) + 
  theme(plot.title = element_text(hjust = 0.5, size=18), 
        axis.title.x = element_blank(), #gets rid of x-axis label
        axis.title.y = element_text(size = 16),
        panel.grid.major = element_blank(), #gets rid of major gridlines
        panel.grid.minor = element_blank(), #gets rid of minor gridlines
        panel.background = element_blank(), #turns background white instead of gray
        axis.line = element_line(colour = "black"), 
        legend.position="none", #gets rid of legend
        axis.text=element_text(size=18, color = "black"), #sets size of x and y axis labels
        axis.text.x=element_text(),
        axis.title=element_text(size=20,face="bold")) + 
  scale_x_discrete (limits = sets)
print(p)
dev.off() 
```
```{r Placental Efficiency, echo = FALSE, warning = FALSE, message = FALSE}
print(p)
```

# Fetal Brain Weight

## One fetal brain weight (along with ratio of brain to body, and brain to liver) was removed from the analysis because it was a significant outlier by Grubb's Test (p<0.05). It is likely that there was residual water or a piece of skull left when the sample was weighed. 
```{r, echo = FALSE, warning = FALSE, message = FALSE}
#Mean
Mean <- tapply(DF_new$Brain.Wt, as.character(DF_new$Treatment), mean, na.rm=TRUE) #change 
Mean <- as.data.frame(rep(Mean, each = NumPoints))
Mean$Treatment <- rep(ActualGroupOrder, each = NumPoints) 
colnames(Mean)[1] <- "Mean"

#Stdev
Stdev <- tapply(DF_new$Brain.Wt, as.character(DF_new$Treatment), sd, na.rm=TRUE) #change 
Stdev <- as.data.frame(rep(Stdev, each = NumPoints))
Stdev$Treatment <- rep(ActualGroupOrder, each = NumPoints)
colnames(Stdev)[1] <- "Stdev"

#Combine
dataframe_combine <- cbind(Mean, Stdev, DF_new$Brain.Wt) #make sure to change
colnames(dataframe_combine)[5] <- "Value"
dataframe_combine <- dataframe_combine[-2]

#Error bars
dataframe_combine$Upper <- dataframe_combine$Mean + dataframe_combine$Stdev
dataframe_combine$Lower <- dataframe_combine$Mean - dataframe_combine$Stdev

#Make Graph#
png("FetalBrainWeight_RmData2_PAExFe_Dotplot.png", units="in", width=7, height=7, res=600) 

sets <- c("MD", "PAE", "MD-Iron", "PAE-Iron")

p<- ggplot(dataframe_combine, aes(x=Treatment, y=Mean)) + 
  geom_bar(stat="identity", color="black", aes(fill = Treatment),
           position=position_dodge()) +
  scale_fill_manual(values=c("MD" = "#0000CC",
                             "PAE" = "#6699FF",
                             "MD-Iron" = "#660066",
                             "PAE-Iron" = "#9900CC"
                             )) +
  geom_errorbar(aes(ymin=Lower, ymax=Upper), width=.2,
                position=position_dodge(.9)) + 
  geom_point(aes(x=Treatment, y=Value),
             size = 1.25, shape = 19, alpha = 0.3, position = position_jitter(width=.15)) +
  scale_y_continuous(expand = c(0,0), limits = c(0,0.2)) +
  ggtitle("Fetal Brain Weight- Males and Females") +
  ylab(expression("Fetal Brain Weight (g)) ")) + 
  theme(plot.title = element_text(hjust = 0.5, size=18), 
        axis.title.x = element_blank(), #gets rid of x-axis label
        axis.title.y = element_text(size = 16),
        panel.grid.major = element_blank(), #gets rid of major gridlines
        panel.grid.minor = element_blank(), #gets rid of minor gridlines
        panel.background = element_blank(), #turns background white instead of gray
        axis.line = element_line(colour = "black"), 
        legend.position="none", #gets rid of legend
        axis.text=element_text(size=18, color = "black"), #sets size of x and y axis labels
        axis.text.x=element_text(),
        axis.title=element_text(size=20,face="bold")) + 
  scale_x_discrete (limits = sets)
print(p)
dev.off() 
```
```{r Fetal Brain Weight, echo = FALSE, warning = FALSE, message = FALSE}
print(p)
```

# Fetal Brain to Body Weight Ratio

## One fetal brain weight (along with ratio of brain to body, and brain to liver) was removed from the analysis because it was a significant outlier by Grubb's Test (p<0.05). It is likely that there was residual water or a piece of skull left when the sample was weighed. 
```{r, echo = FALSE, warning = FALSE, message = FALSE}
#Mean
Mean <- tapply(DF_new$Ratio.Brain.Body, as.character(DF_new$Treatment), mean, na.rm=TRUE) #change 
Mean <- as.data.frame(rep(Mean, each = NumPoints))
Mean$Treatment <- rep(ActualGroupOrder, each = NumPoints) 
colnames(Mean)[1] <- "Mean"

#Stdev
Stdev <- tapply(DF_new$Ratio.Brain.Body, as.character(DF_new$Treatment), sd, na.rm=TRUE) #change 
Stdev <- as.data.frame(rep(Stdev, each = NumPoints))
Stdev$Treatment <- rep(ActualGroupOrder, each = NumPoints)
colnames(Stdev)[1] <- "Stdev"

#Combine
dataframe_combine <- cbind(Mean, Stdev, DF_new$Ratio.Brain.Body) #make sure to change
colnames(dataframe_combine)[5] <- "Value"
dataframe_combine <- dataframe_combine[-2]

#Error bars
dataframe_combine$Upper <- dataframe_combine$Mean + dataframe_combine$Stdev
dataframe_combine$Lower <- dataframe_combine$Mean - dataframe_combine$Stdev

#Make Graph#
png("FetalBraintoBodyWeightRatio_RmData2_PAExFe_Dotplot.png", units="in", width=7, height=7, res=600) 

sets <- c("MD", "PAE", "MD-Iron", "PAE-Iron")

p<- ggplot(dataframe_combine, aes(x=Treatment, y=Mean)) + 
  geom_bar(stat="identity", color="black", aes(fill = Treatment),
           position=position_dodge()) +
  scale_fill_manual(values=c("MD" = "#0000CC",
                             "PAE" = "#6699FF",
                             "MD-Iron" = "#660066",
                             "PAE-Iron" = "#9900CC"
                             )) +
  geom_errorbar(aes(ymin=Lower, ymax=Upper), width=.2,
                position=position_dodge(.9)) + 
  geom_point(aes(x=Treatment, y=Value),
             size = 1.25, shape = 19, alpha = 0.3, position = position_jitter(width=.15)) +
  scale_y_continuous(expand = c(0,0), limits = c(0,0.08)) +
  ggtitle("Fetal Brain to Body Weight Ratio- Males and Females") +
  ylab(expression("Fetal Brain to Body Weight Ratio")) + 
  theme(plot.title = element_text(hjust = 0.5, size=18), 
        axis.title.x = element_blank(), #gets rid of x-axis label
        axis.title.y = element_text(size = 16),
        panel.grid.major = element_blank(), #gets rid of major gridlines
        panel.grid.minor = element_blank(), #gets rid of minor gridlines
        panel.background = element_blank(), #turns background white instead of gray
        axis.line = element_line(colour = "black"), 
        legend.position="none", #gets rid of legend
        axis.text=element_text(size=18, color = "black"), #sets size of x and y axis labels
        axis.text.x=element_text(),
        axis.title=element_text(size=20,face="bold")) + 
  scale_x_discrete (limits = sets)
print(p)
dev.off() 
```
```{r Fetal Brain to Body Weight Ratio, echo = FALSE, warning = FALSE, message = FALSE}
print(p)
```

# Fetal Liver Weight
```{r, echo = FALSE, warning = FALSE, message = FALSE}
#Mean
Mean <- tapply(DF_new$Liver.Wt, as.character(DF_new$Treatment), mean, na.rm=TRUE) #change 
Mean <- as.data.frame(rep(Mean, each = NumPoints))
Mean$Treatment <- rep(ActualGroupOrder, each = NumPoints) 
colnames(Mean)[1] <- "Mean"

#Stdev
Stdev <- tapply(DF_new$Liver.Wt, as.character(DF_new$Treatment), sd, na.rm=TRUE) #change 
Stdev <- as.data.frame(rep(Stdev, each = NumPoints))
Stdev$Treatment <- rep(ActualGroupOrder, each = NumPoints)
colnames(Stdev)[1] <- "Stdev"

#Combine
dataframe_combine <- cbind(Mean, Stdev, DF_new$Liver.Wt) #make sure to change
colnames(dataframe_combine)[5] <- "Value"
dataframe_combine <- dataframe_combine[-2]

#Error bars
dataframe_combine$Upper <- dataframe_combine$Mean + dataframe_combine$Stdev
dataframe_combine$Lower <- dataframe_combine$Mean - dataframe_combine$Stdev

#Make Graph#
png("FetalLiverWeight_RmData2_PAExFe_Dotplot.png", units="in", width=7, height=7, res=600) 

sets <- c("MD", "PAE", "MD-Iron", "PAE-Iron")

p<- ggplot(dataframe_combine, aes(x=Treatment, y=Mean)) + 
  geom_bar(stat="identity", color="black", aes(fill = Treatment),
           position=position_dodge()) +
  scale_fill_manual(values=c("MD" = "#0000CC",
                             "PAE" = "#6699FF",
                             "MD-Iron" = "#660066",
                             "PAE-Iron" = "#9900CC"
                             )) +
  geom_errorbar(aes(ymin=Lower, ymax=Upper), width=.2,
                position=position_dodge(.9)) + 
  geom_point(aes(x=Treatment, y=Value),
             size = 1.25, shape = 19, alpha = 0.3, position = position_jitter(width=.15)) +
  scale_y_continuous(expand = c(0,0), limits = c(0,0.41)) +
  ggtitle("Fetal Liver Weight- Males and Females") +
  ylab(expression("Fetal Liver Weight (g)")) + 
  theme(plot.title = element_text(hjust = 0.5, size=18), 
        axis.title.x = element_blank(), #gets rid of x-axis label
        axis.title.y = element_text(size = 16),
        panel.grid.major = element_blank(), #gets rid of major gridlines
        panel.grid.minor = element_blank(), #gets rid of minor gridlines
        panel.background = element_blank(), #turns background white instead of gray
        axis.line = element_line(colour = "black"), 
        legend.position="none", #gets rid of legend
        axis.text=element_text(size=18, color = "black"), #sets size of x and y axis labels
        axis.text.x=element_text(),
        axis.title=element_text(size=20,face="bold")) + 
  scale_x_discrete (limits = sets)
print(p)
dev.off() 
```
```{r Fetal Liver Weight, echo = FALSE, warning = FALSE, message = FALSE}
print(p)
```

# Fetal Liver to Body Weight Ratio
```{r, echo = FALSE, warning = FALSE, message = FALSE}
#Mean
Mean <- tapply(DF_new$Ratio.Liver.Body, as.character(DF_new$Treatment), mean, na.rm=TRUE) #change 
Mean <- as.data.frame(rep(Mean, each = NumPoints))
Mean$Treatment <- rep(ActualGroupOrder, each = NumPoints) 
colnames(Mean)[1] <- "Mean"

#Stdev
Stdev <- tapply(DF_new$Ratio.Liver.Body, as.character(DF_new$Treatment), sd, na.rm=TRUE) #change 
Stdev <- as.data.frame(rep(Stdev, each = NumPoints))
Stdev$Treatment <- rep(ActualGroupOrder, each = NumPoints)
colnames(Stdev)[1] <- "Stdev"

#Combine
dataframe_combine <- cbind(Mean, Stdev, DF_new$Ratio.Liver.Body) #make sure to change
colnames(dataframe_combine)[5] <- "Value"
dataframe_combine <- dataframe_combine[-2]

#Error bars
dataframe_combine$Upper <- dataframe_combine$Mean + dataframe_combine$Stdev
dataframe_combine$Lower <- dataframe_combine$Mean - dataframe_combine$Stdev

#Make Graph#
png("FetalLiverBodyWeightRatio_RmData2_PAExFe_Dotplot.png", units="in", width=7, height=7, res=600) 

sets <- c("MD", "PAE", "MD-Iron", "PAE-Iron")

p<- ggplot(dataframe_combine, aes(x=Treatment, y=Mean)) + 
  geom_bar(stat="identity", color="black", aes(fill = Treatment),
           position=position_dodge()) +
  scale_fill_manual(values=c("MD" = "#0000CC",
                             "PAE" = "#6699FF",
                             "MD-Iron" = "#660066",
                             "PAE-Iron" = "#9900CC"
                             )) +
  geom_errorbar(aes(ymin=Lower, ymax=Upper), width=.2,
                position=position_dodge(.9)) + 
  geom_point(aes(x=Treatment, y=Value),
             size = 1.25, shape = 19, alpha = 0.3, position = position_jitter(width=.15)) +
  scale_y_continuous(expand = c(0,0), limits = c(0,0.11)) +
  ggtitle("Fetal Liver to Body Weight Ratio- Males and Females") +
  ylab(expression("Fetal Liver to Body Weight Ratio")) + 
  theme(plot.title = element_text(hjust = 0.5, size=18), 
        axis.title.x = element_blank(), #gets rid of x-axis label
        axis.title.y = element_text(size = 16),
        panel.grid.major = element_blank(), #gets rid of major gridlines
        panel.grid.minor = element_blank(), #gets rid of minor gridlines
        panel.background = element_blank(), #turns background white instead of gray
        axis.line = element_line(colour = "black"), 
        legend.position="none", #gets rid of legend
        axis.text=element_text(size=18, color = "black"), #sets size of x and y axis labels
        axis.text.x=element_text(),
        axis.title=element_text(size=20,face="bold")) + 
  scale_x_discrete (limits = sets)
print(p)
dev.off() 
```
```{r Fetal Liver to Body Weight Ratio, echo = FALSE, warning = FALSE, message = FALSE}
print(p)
```

# Fetal Brain to Liver Weight Ratio

## One fetal brain weight (along with ratio of brain to body, and brain to liver) was removed from the analysis because it was a significant outlier by Grubb's Test (p<0.05). It is likely that there was residual water or a piece of skull left when the sample was weighed. 
```{r, echo = FALSE, warning = FALSE, message = FALSE}
#Mean
Mean <- tapply(DF_new$Ratio.Brain.Liver, as.character(DF_new$Treatment), mean, na.rm=TRUE) #change 
Mean <- as.data.frame(rep(Mean, each = NumPoints))
Mean$Treatment <- rep(ActualGroupOrder, each = NumPoints) 
colnames(Mean)[1] <- "Mean"

#Stdev
Stdev <- tapply(DF_new$Ratio.Brain.Liver, as.character(DF_new$Treatment), sd, na.rm=TRUE) #change 
Stdev <- as.data.frame(rep(Stdev, each = NumPoints))
Stdev$Treatment <- rep(ActualGroupOrder, each = NumPoints)
colnames(Stdev)[1] <- "Stdev"

#Combine
dataframe_combine <- cbind(Mean, Stdev, DF_new$Ratio.Brain.Liver) #make sure to change
colnames(dataframe_combine)[5] <- "Value"
dataframe_combine <- dataframe_combine[-2]

#Error bars
dataframe_combine$Upper <- dataframe_combine$Mean + dataframe_combine$Stdev
dataframe_combine$Lower <- dataframe_combine$Mean - dataframe_combine$Stdev

#Make Graph#
png("FetalBraintoLiverWeightRatio_RmData2_PAExFe_Dotplot.png", units="in", width=7, height=7, res=600) 

sets <- c("MD", "PAE", "MD-Iron", "PAE-Iron")

p<- ggplot(dataframe_combine, aes(x=Treatment, y=Mean)) + 
  geom_bar(stat="identity", color="black", aes(fill = Treatment),
           position=position_dodge()) +
  scale_fill_manual(values=c("MD" = "#0000CC",
                             "PAE" = "#6699FF",
                             "MD-Iron" = "#660066",
                             "PAE-Iron" = "#9900CC"
                             )) +
  geom_errorbar(aes(ymin=Lower, ymax=Upper), width=.2,
                position=position_dodge(.9)) + 
  geom_point(aes(x=Treatment, y=Value),
             size = 1.25, shape = 19, alpha = 0.3, position = position_jitter(width=.15)) +
  scale_y_continuous(expand = c(0,0), limits = c(0,1.5)) +
  ggtitle("Fetal Brain to Liver Weight Ratio- Males and Females") +
  ylab(expression("Fetal Brain to Liver Weight Ratio")) + 
  theme(plot.title = element_text(hjust = 0.5, size=18), 
        axis.title.x = element_blank(), #gets rid of x-axis label
        axis.title.y = element_text(size = 16),
        panel.grid.major = element_blank(), #gets rid of major gridlines
        panel.grid.minor = element_blank(), #gets rid of minor gridlines
        panel.background = element_blank(), #turns background white instead of gray
        axis.line = element_line(colour = "black"), 
        legend.position="none", #gets rid of legend
        axis.text=element_text(size=18, color = "black"), #sets size of x and y axis labels
        axis.text.x=element_text(),
        axis.title=element_text(size=20,face="bold")) + 
  scale_x_discrete (limits = sets)
print(p)
dev.off() 
```
```{r Fetal Brain to Liver Weight Ratio, echo = FALSE, warning = FALSE, message = FALSE}
print(p)
```

# Fetal Heart Weight
```{r, echo = FALSE, warning = FALSE, message = FALSE}
#Mean
Mean <- tapply(DF_new$Heart.Wt, as.character(DF_new$Treatment), mean, na.rm=TRUE) #change 
Mean <- as.data.frame(rep(Mean, each = NumPoints))
Mean$Treatment <- rep(ActualGroupOrder, each = NumPoints) 
colnames(Mean)[1] <- "Mean"

#Stdev
Stdev <- tapply(DF_new$Heart.Wt, as.character(DF_new$Treatment), sd, na.rm=TRUE) #change 
Stdev <- as.data.frame(rep(Stdev, each = NumPoints))
Stdev$Treatment <- rep(ActualGroupOrder, each = NumPoints)
colnames(Stdev)[1] <- "Stdev"

#Combine
dataframe_combine <- cbind(Mean, Stdev, DF_new$Heart.Wt) #make sure to change
colnames(dataframe_combine)[5] <- "Value"
dataframe_combine <- dataframe_combine[-2]

#Error bars
dataframe_combine$Upper <- dataframe_combine$Mean + dataframe_combine$Stdev
dataframe_combine$Lower <- dataframe_combine$Mean - dataframe_combine$Stdev

#Make Graph#
png("FetalHeartWeight_RmData2_PAExFe_Dotplot.png", units="in", width=7, height=7, res=600) 

sets <- c("MD", "PAE", "MD-Iron", "PAE-Iron")

p<- ggplot(dataframe_combine, aes(x=Treatment, y=Mean)) + 
  geom_bar(stat="identity", color="black", aes(fill = Treatment),
           position=position_dodge()) +
  scale_fill_manual(values=c("MD" = "#0000CC",
                             "PAE" = "#6699FF",
                             "MD-Iron" = "#660066",
                             "PAE-Iron" = "#9900CC"
                             )) +
  geom_errorbar(aes(ymin=Lower, ymax=Upper), width=.2,
                position=position_dodge(.9)) + 
  geom_point(aes(x=Treatment, y=Value),
             size = 1.25, shape = 19, alpha = 0.3, position = position_jitter(width=.15)) +
  scale_y_continuous(expand = c(0,0), limits = c(0,0.03)) +
  ggtitle("Fetal Heart Weight- Males and Females") +
  ylab(expression("Fetal Heart Weight (g)")) + 
  theme(plot.title = element_text(hjust = 0.5, size=18), 
        axis.title.x = element_blank(), #gets rid of x-axis label
        axis.title.y = element_text(size = 16),
        panel.grid.major = element_blank(), #gets rid of major gridlines
        panel.grid.minor = element_blank(), #gets rid of minor gridlines
        panel.background = element_blank(), #turns background white instead of gray
        axis.line = element_line(colour = "black"), 
        legend.position="none", #gets rid of legend
        axis.text=element_text(size=18, color = "black"), #sets size of x and y axis labels
        axis.text.x=element_text(),
        axis.title=element_text(size=20,face="bold")) + 
  scale_x_discrete (limits = sets)
print(p)
dev.off() 
```
```{r Fetal Heart Weight, echo = FALSE, warning = FALSE, message = FALSE}
print(p)
```

# Fetal Heart to Body Weight Ratio
```{r, echo = FALSE, warning = FALSE, message = FALSE}
#Mean
Mean <- tapply(DF_new$Ratio.Heart.Body, as.character(DF_new$Treatment), mean, na.rm=TRUE) #change 
Mean <- as.data.frame(rep(Mean, each = NumPoints))
Mean$Treatment <- rep(ActualGroupOrder, each = NumPoints) 
colnames(Mean)[1] <- "Mean"

#Stdev
Stdev <- tapply(DF_new$Ratio.Heart.Body, as.character(DF_new$Treatment), sd, na.rm=TRUE) #change 
Stdev <- as.data.frame(rep(Stdev, each = NumPoints))
Stdev$Treatment <- rep(ActualGroupOrder, each = NumPoints)
colnames(Stdev)[1] <- "Stdev"

#Combine
dataframe_combine <- cbind(Mean, Stdev, DF_new$Ratio.Heart.Body) #make sure to change
colnames(dataframe_combine)[5] <- "Value"
dataframe_combine <- dataframe_combine[-2]

#Error bars
dataframe_combine$Upper <- dataframe_combine$Mean + dataframe_combine$Stdev
dataframe_combine$Lower <- dataframe_combine$Mean - dataframe_combine$Stdev

#Make Graph#
png("FetalHeartBodyWeightRatio_RmData2_PAExFe_Dotplot.png", units="in", width=7, height=7, res=600) 

sets <- c("MD", "PAE", "MD-Iron", "PAE-Iron")

p<- ggplot(dataframe_combine, aes(x=Treatment, y=Mean)) + 
  geom_bar(stat="identity", color="black", aes(fill = Treatment),
           position=position_dodge()) +
  scale_fill_manual(values=c("MD" = "#0000CC",
                             "PAE" = "#6699FF",
                             "MD-Iron" = "#660066",
                             "PAE-Iron" = "#9900CC"
                             )) +
  geom_errorbar(aes(ymin=Lower, ymax=Upper), width=.2,
                position=position_dodge(.9)) + 
  geom_point(aes(x=Treatment, y=Value),
             size = 1.25, shape = 19, alpha = 0.3, position = position_jitter(width=.15)) +
  scale_y_continuous(expand = c(0,0), limits = c(0,0.008)) +
  ggtitle("Fetal Heart to Body Weight Ratio- Males and Females") +
  ylab(expression("Fetal Heart to Body Weight Ratio")) + 
  theme(plot.title = element_text(hjust = 0.5, size=18), 
        axis.title.x = element_blank(), #gets rid of x-axis label
        axis.title.y = element_text(size = 16),
        panel.grid.major = element_blank(), #gets rid of major gridlines
        panel.grid.minor = element_blank(), #gets rid of minor gridlines
        panel.background = element_blank(), #turns background white instead of gray
        axis.line = element_line(colour = "black"), 
        legend.position="none", #gets rid of legend
        axis.text=element_text(size=18, color = "black"), #sets size of x and y axis labels
        axis.text.x=element_text(),
        axis.title=element_text(size=20,face="bold")) + 
  scale_x_discrete (limits = sets)
print(p)
dev.off() 
```
```{r Fetal Heart to Body Weight Ratio, echo = FALSE, warning = FALSE, message = FALSE}
print(p)
```

# Session Information
```{r, echo = FALSE}
session_info <- devtools::session_info()
print(session_info)
```