---
title: "Fetal Rat Anthropometry at Collection GD20.5, AIN-76A diet with MD or Alcohol and Iron Supplement or Water- 2 Small Litters Removed- Males Only"
author: "Kaylee Helfrich"
date: "9/16/20"
output: 
  pdf_document: default
  html_document: default
data: "Fetal_Rat_Anthropometry_Nov-Dec2019_withSex_RmData2.csv"
---

Built with R `r getRversion()`

```{r RMarkdown setup, include = FALSE, message = FALSE}
require(knitr)
knitr::opts_chunk$set(echo = TRUE, tidy.opts=list(width.cutoff=60), tidy=TRUE)
knitr::opts_knit$set(root.dir = "~/KayleeStuff/Smith_Lab/Data/Rat_Iron/Fetal_Anthro/RmData2")
options(tinytex.verbose = TRUE)
```

# Graphing Fetal Rat Anthropometry- Data from two small litters and individual data outliers removed- Males Only
This document details my graphing of the anthropometry data from fetal rats at tissue collection on GD20.5, including fetal weight, placental weight, placental efficiency, brain weight, brain to body weight ratio, liver weight, liver to body weight ratio, ratio of brain to liver weight, heart weight, and ratio of heart to body weight. This analysis uses the data that was collected on the male fetuses in this study, excluding samples from fetuses from litters that were more than 2 standard deviations (SD = 3) from the mean (Mean = 10), including 2 litters with only 2 fetuses each (R029-MD+H2O and R031-MD+Fe). The following removed data is from the dataset as a whole, and may include both male and female inviduals. Also, data from 4 underdeveloped fetuses from MD+H2O litter R054 (4,6,8,9) were removed. Finally, the following individual data points were removed as the data were statistical outliers via Grubb's test- placental weight (R015-2), placental efficiency (R015-2), brain weight (R043-13), ratio brain to body weight (R043-13), liver weight (R042-11, R011-6), ratio liver to body weight (R010-4, R042-11, R011-6), ratio brain to liver weight (R010-4, R043-13, R042-11, R032-4, R011-6, R026-10), and ratio of heart to body weight (R010-5, R030-6, R027-1). All samples were collected between 11/2019-12/2019 by Kaylee Helfrich, Olivia Rivera, Nipun Saini, and Cecilia Kwan. Female Long-Evans rats arrived at 7 weeks old and were mated at 9-11 weeks of age. The dams were dosed with 5g/kg ethanol or isocaloric maltodextrin from GD13.5-19.5. The dams also received either an iron supplement (6g/kg, Fer-In-Sol) or the same volume of water as a gavage from GD12.5-GD19.5. All dams consumed AIN-76G diet modified to contain 100ppm of iron from arrival through pregnancy. Tissues were harvested on GD20.5. All graphs are mean with standard deviation, since there are not multiple measures per sample. This analysis will allow us to compare the 4 groups. Statistical analysis in JMP will use ANOVA, following checks for normality and variance, to assign significance to the measures. 

```{r include = FALSE}
rm(list=ls())
setwd("~/KayleeStuff/Smith_Lab/Data/Rat_Iron/Fetal_Anthro/RmData2")
library(ggplot2)
library(plotrix)
library(dplyr)
library(extrafont)
loadfonts(device = "win")
```

```{r Import file and rearrange by treatment to be alphabetical}
File <- "Fetal_Rat_Anthropometry_Nov-Dec2019_withSex_RmData2.csv"
data <- read.csv(File, header=TRUE) 
data_frame <- data.frame(data)
data_frame <- data_frame[order(data_frame$Treatment), ]
```
```{r Prepare data for graphing}
ActualGroupOrder <- c("PAE+Iron", "PAE","MD+Iron", "MD")
```

# Select out only male data and equalize the number of rows for each treatment group
```{r}
Males <- data_frame[ which(data_frame$Sex=='M'), ] #Create new dataframe of only males
```
```{r echo = FALSE}
print(Males)
```
```{r}
#Figure out how many rows of empty NA's are needed to equalize the treatment groups
Groupcount <- Males %>% count(Treatment) #Calculate how many individual males there are per treatment group
NumPoints <- max(Groupcount$n) #Create the variable "NumPoints" to count the # of points in the final graphs
DiffFunc <- function(x) NumPoints - x #Create the function "DiffFunc" to calculate the number of NA rows to be added
DiffPoints <- as.data.frame(tapply(Groupcount$n, as.character(Groupcount$Treatment), DiffFunc)) #Calculate number of NA rows to be added to each treatment group
DiffPoints$Treatment <- ActualGroupOrder #add new column so that the # of points to be added is assigned to the treatment
colnames(DiffPoints)[1] <- "NumberN" #rename column
Nrow <- sum(DiffPoints$NumberN) #figure out how many total rows will be added to the DF_extra dataframe
AlcFe <- DiffPoints[1,1] #for each of these, it is creating a variable for the "vector" below
AlcH2O <- DiffPoints[2,1]
MDFe <- DiffPoints[3,1]
MDH2O <- DiffPoints[4,1]

#Add extra rows of NAs to equalize groups
DF_extra <- data.frame(matrix(NA, nrow = Nrow, ncol = 16)) #create an empty dataframe filled with NA's
vector <- rep(c("Alc+Fe", "Alc+H2O", "MD+Fe", "MD+H2O"), times = c(AlcFe, AlcH2O, MDFe, MDH2O)) #create the vector to add the treatment groups to the NA matrix
DF_extra$Treatment <- vector #add in the Treatment column to the DF_extra dataframe
DF_extra <- DF_extra[,c(1:2,17,3:16)] #rearrange the columns so that they are in the same order as the original DF
DF_extra <- setNames(DF_extra, names(Males)) #set the names of the new df to match the original df
Males_new <- rbind(Males, DF_extra) #Rbind the 2 dataframes so that we now have equal treatment group sizes
print(Males_new %>% count(Treatment)) #check that the groups are now equal
#rearrange to be in order of Treatment, otherwise the dots get accidentally reassigned to the wrong group
Males_new <- Males_new[order(Males_new$Treatment), ]
```

# Fetal Brain Weight

## One fetal brain weight (along with ratio of brain to body, and brain to liver) was removed from the analysis because it was a significant outlier by Grubb's Test (p<0.05). It is likely that there was residual water or a piece of skull left when the sample was weighed. 
```{r, echo = FALSE, warning = FALSE, message = FALSE}
#Mean
Mean <- tapply(Males_new$Brain.Wt, as.character(Males_new$Treatment), mean, na.rm=TRUE) #change 
Mean <- as.data.frame(rep(Mean, each = NumPoints))
Mean$Treatment <- rep(ActualGroupOrder, each = NumPoints) 
colnames(Mean)[1] <- "Mean"

#Stdev
Stdev <- tapply(Males_new$Brain.Wt, as.character(Males_new$Treatment), sd, na.rm=TRUE) #change 
Stdev <- as.data.frame(rep(Stdev, each = NumPoints))
Stdev$Treatment <- rep(ActualGroupOrder, each = NumPoints)
colnames(Stdev)[1] <- "Stdev"

#Combine
dataframe_combine <- cbind(Mean, Stdev, Males_new$Brain.Wt) #make sure to change
colnames(dataframe_combine)[5] <- "Value"
dataframe_combine <- dataframe_combine[-2]

#Error bars
dataframe_combine$Upper <- dataframe_combine$Mean + dataframe_combine$Stdev
dataframe_combine$Lower <- dataframe_combine$Mean - dataframe_combine$Stdev

#Make Graph#
png("FetalBrainWeight_MalesOnly_RmData2_PAExFe_Dotplot_B&W.png", units="in", width=7, height=4, res=600) 

sets <- c("MD", "PAE", "MD+Iron", "PAE+Iron")

p<- ggplot(dataframe_combine, aes(x=Treatment, y=Mean)) + 
  geom_bar(stat="identity", color="black", aes(fill = Treatment),
           position=position_dodge()) +
  scale_fill_manual(values=c("MD" = "grey100",
                             "PAE" = "grey51",
                             "MD+Iron" = "grey75",
                             "PAE+Iron" = "grey30"
                             )) +
  geom_errorbar(aes(ymin=Lower, ymax=Upper), width=.2,
                position=position_dodge(.9)) + 
  geom_point(aes(x=Treatment, y=Value),
             size = 1.25, shape = 19, alpha = 0.3, position = position_jitter(width=.15, height = 0)) +
  scale_y_continuous(expand = c(0,0), limits = c(0,0.31)) +
  ggtitle("Fetal Brain Weight- Males") +
  ylab(expression("Fetal Brain Weight (g)")) + 
  theme(plot.title = element_text(hjust = 0.5, size=18, family = "Times New Roman"), 
        axis.title.x = element_blank(), #gets rid of x-axis label
        axis.title.y = element_text(size = 20, family = "Times New Roman"),
        panel.grid.major = element_blank(), #gets rid of major gridlines
        panel.grid.minor = element_blank(), #gets rid of minor gridlines
        panel.background = element_blank(), #turns background white instead of gray
        axis.line = element_line(colour = "black"), 
        legend.position="none", #gets rid of legend
        axis.text=element_text(size=18, color = "black", family = "Times New Roman"), #sets size of x and y axis labels
        axis.text.x=element_text(family = "Times New Roman"),
        axis.title=element_text(size=22,face="bold", family = "Times New Roman")) + 
  scale_x_discrete (limits = sets)
print(p)
dev.off() 
```
```{r Fetal Brain Weight, echo = FALSE, warning = FALSE, message = FALSE}
print(p)
```

# Fetal Brain to Body Weight Ratio

## One fetal brain weight (along with ratio of brain to body, and brain to liver) was removed from the analysis because it was a significant outlier by Grubb's Test (p<0.05). It is likely that there was residual water or a piece of skull left when the sample was weighed. 
```{r, echo = FALSE, warning = FALSE, message = FALSE}
#Mean
Mean <- tapply(Males_new$Ratio.Brain.Body, as.character(Males_new$Treatment), mean, na.rm=TRUE) #change 
Mean <- as.data.frame(rep(Mean, each = NumPoints))
Mean$Treatment <- rep(ActualGroupOrder, each = NumPoints) 
colnames(Mean)[1] <- "Mean"

#Stdev
Stdev <- tapply(Males_new$Ratio.Brain.Body, as.character(Males_new$Treatment), sd, na.rm=TRUE) #change 
Stdev <- as.data.frame(rep(Stdev, each = NumPoints))
Stdev$Treatment <- rep(ActualGroupOrder, each = NumPoints)
colnames(Stdev)[1] <- "Stdev"

#Combine
dataframe_combine <- cbind(Mean, Stdev, Males_new$Ratio.Brain.Body) #make sure to change
colnames(dataframe_combine)[5] <- "Value"
dataframe_combine <- dataframe_combine[-2]

#Error bars
dataframe_combine$Upper <- dataframe_combine$Mean + dataframe_combine$Stdev
dataframe_combine$Lower <- dataframe_combine$Mean - dataframe_combine$Stdev

#Make Graph#
png("FetalBrainToBodyRatio_MalesOnly_RmData2_PAExFe_Dotplot_B&W.png", units="in", width=7, height=4, res=600) 

sets <- c("MD", "PAE", "MD+Iron", "PAE+Iron")

p<- ggplot(dataframe_combine, aes(x=Treatment, y=Mean)) + 
  geom_bar(stat="identity", color="black", aes(fill = Treatment),
           position=position_dodge()) +
  scale_fill_manual(values=c("MD" = "grey100",
                             "PAE" = "grey51",
                             "MD+Iron" = "grey75",
                             "PAE+Iron" = "grey30"
                             )) +
  geom_errorbar(aes(ymin=Lower, ymax=Upper), width=.2,
                position=position_dodge(.9)) + 
  geom_point(aes(x=Treatment, y=Value),
             size = 1.25, shape = 19, alpha = 0.3, position = position_jitter(width=.15, height = 0)) +
  scale_y_continuous(expand = c(0,0), limits = c(0,0.1)) +
  ggtitle("Fetal Brain to Body Ratio- Males") +
  ylab(expression("Brain to Body Ratio")) + 
  theme(plot.title = element_text(hjust = 0.5, size=18, family = "Times New Roman"), 
        axis.title.x = element_blank(), #gets rid of x-axis label
        axis.title.y = element_text(size = 20, family = "Times New Roman"),
        panel.grid.major = element_blank(), #gets rid of major gridlines
        panel.grid.minor = element_blank(), #gets rid of minor gridlines
        panel.background = element_blank(), #turns background white instead of gray
        axis.line = element_line(colour = "black"), 
        legend.position="none", #gets rid of legend
        axis.text=element_text(size=18, color = "black", family = "Times New Roman"), #sets size of x and y axis labels
        axis.text.x=element_text(family = "Times New Roman"),
        axis.title=element_text(size=22,face="bold", family = "Times New Roman")) + 
  scale_x_discrete (limits = sets)
print(p)
dev.off() 
```
```{r Fetal Brain to Body Weight Ratio, echo = FALSE, warning = FALSE, message = FALSE}
print(p)
```

# Session Information
```{r, echo = FALSE}
session_info <- devtools::session_info()
print(session_info)
```