---
title: "Maternal Rat Prenatal Food Intake, AIN-76A diet with MD or Alcohol and Iron Supplement or Water- Dams with litters mean+/- 2SD removed"
author: "Kaylee Helfrich"
date: "7/7/20-10/26/20"
output: 
  pdf_document: default
  html_document: default
data: "MaternalFoodIntake_RmData2.csv"
---

Built with R `r getRversion()`

```{r RMarkdown setup, include = FALSE, message = FALSE}
require(knitr)
knitr::opts_chunk$set(echo = TRUE, tidy.opts=list(width.cutoff=60), tidy=TRUE)
knitr::opts_knit$set(root.dir = "~/KayleeStuff/Smith_Lab/Data/Rat_Iron/Maternal_Anthro/FoodIntake")
options(tinytex.verbose = TRUE)
```

# Graphing Maternal Rat Food Intake
This document details my graphing of the food and energy intake data from maternal rats. This includes bar graphs for total prenatal food intake and food intake during dosing, as well as a line graph for food intake over the pregnancy. Further, this has graphs of total energy intake (including calories from gavage) and energy efficiency, where weight gain is compared to total energy intake. This analysis uses all data that was collected (excluding the nonpregnant dams) and excluding samples from dams with litters that were +/- 2 SDs from the mean of 10 (including R029 and R031). Long-Evans rats arrived at 7 weeks old and were mated at 9-11 weeks of age. The rats were dosed with 5g/kg ethanol or isocaloric maltodextrin from GD13.5-19.5. The dams also received either an iron supplement (6g/kg, Fer-In-Sol) or the same volume of water as a gavage from GD12.5-GD19.5. All dams consumed AIN-76G diet modified to contain 100ppm of iron from arrival through pregnancy. Tissues were harvested on GD20.5. All graphs are mean with standard deviation, since there are not multiple measures per sample. This analysis will allow us to compare the 4 groups. Statistical analysis in JMP will use ANOVA, following checks for normality and variance, to assign significance to the measures. 

```{r include = FALSE}
rm(list=ls())
setwd("~/KayleeStuff/Smith_Lab/Data/Rat_Iron/Maternal_Anthro/FoodIntake")
library(ggplot2)
library(plotrix)
```

```{r Import file and rearrange by treatment to be alphabetical}
File <- "MaternalFoodIntake_RmData2.csv"
data <- read.csv(File, header=TRUE) 
data_frame <- data.frame(data)
data_frame <- data_frame[order(data_frame$Treatment), ]
```
```{r echo = FALSE}
print(data_frame)
```
```{r Prepare data for graphing}
ActualGroupOrder <- c("PAE-Iron", "PAE","MD-Iron", "MD")
NumPoints <- 11 #Make sure to set the integer to the number of dots/values you have for each treatment
```

# Maternal Total Prenatal Food Intake

## All code is included for this first example, but thereafter, only the heading and graphs are shown. For all graphs, all data is graphed unless mentioned otherwise. Messages and warnings are excluded, since NA's were included to make all groups even, and I didn't want the code to print out these errors when they weren't necessary.
```{r, warning = FALSE, message = FALSE}
#Mean- calculate mean for column, repeat it to number of points, and create dataframe
Mean <- tapply(data_frame$Total.Pregnancy.Intake, as.character(data_frame$Treatment), mean, na.rm=TRUE) #make sure to change selected column to change data for graph
Mean <- as.data.frame(rep(Mean, each = NumPoints)) #repeat mean a set number of times
Mean$Treatment <- rep(ActualGroupOrder, each = NumPoints) #repeat treatment a set number of times
colnames(Mean)[1] <- "Mean" #fix column name

#Stdev- calculate standard deviation for column, repeat it to number of points, and create dataframe
Stdev <- tapply(data_frame$Total.Pregnancy.Intake, as.character(data_frame$Treatment), sd, na.rm=TRUE) #make sure to change selected column
Stdev <- as.data.frame(rep(Stdev, each = NumPoints)) #repeat stdev a set number of times
Stdev$Treatment <- rep(ActualGroupOrder, each = NumPoints) #repeat treatment a set number of times
colnames(Stdev)[1] <- "Stdev" #fix column name

#Combine mean, standard deviation, and individual data points
dataframe_combine <- cbind(Mean, Stdev, data_frame$Total.Pregnancy.Intake) #make sure to change selected column
colnames(dataframe_combine)[5] <- "Value" #Fix name of individual data point column
dataframe_combine <- dataframe_combine[-2] #Remove extra treatment column

#Error bars
dataframe_combine$Upper <- dataframe_combine$Mean + dataframe_combine$Stdev #upper error
dataframe_combine$Lower <- dataframe_combine$Mean - dataframe_combine$Stdev #lower error

#Make Graph#
png("Maternal_TotalPrenatalFoodIntake_RmData2_PAExFe_Dotplot.png", units="in", width=7, height=7, res=600) 

sets <- c("MD", "PAE", "MD-Iron", "PAE-Iron")

p<- ggplot(dataframe_combine, aes(x=Treatment, y=Mean)) + 
  geom_bar(stat="identity", color="black", aes(fill = Treatment),
           position=position_dodge()) +
  scale_fill_manual(values=c("MD" = "#0000CC",
                             "PAE" = "#6699FF",
                             "MD-Iron" = "#660066",
                             "PAE-Iron" = "#9900CC"
                             )) +
  geom_errorbar(aes(ymin=Lower, ymax=Upper), width=.2,
                position=position_dodge(.9)) + 
  geom_point(aes(x=Treatment, y=Value),
             size = 1.25, shape = 19, position = position_jitter(width=.15, height=0)) +
  scale_y_continuous(expand = c(0,0), limits = c(0,425)) +
  ggtitle("Maternal Prenatal Food Intake") +
  ylab(expression("Food Intake (g)")) + 
  theme(plot.title = element_text(hjust = 0.5, size=18), 
        axis.title.x = element_blank(), #gets rid of x-axis label
        axis.title.y = element_text(size = 16),
        panel.grid.major = element_blank(), #gets rid of major gridlines
        panel.grid.minor = element_blank(), #gets rid of minor gridlines
        panel.background = element_blank(), #turns background white instead of gray
        axis.line = element_line(colour = "black"), 
        legend.position="none", #gets rid of legend
        axis.text=element_text(size=18, color = "black"), #sets size of x and y axis labels
        axis.text.x=element_text(angle = 45, vjust = .95, hjust = 0.9),
        axis.title=element_text(size=20,face="bold")) + 
  scale_x_discrete (limits = sets)
print(p)
dev.off() 
```
```{r Maternal Prenatal Food Intake, echo = FALSE}
print(p)
```

# Maternal Food Intake During Dosing
```{r, echo = FALSE, warning = FALSE, message = FALSE}
#Mean
Mean <- tapply(data_frame$GD13.5.20.5, as.character(data_frame$Treatment), mean, na.rm=TRUE) #make sure to change 
Mean <- as.data.frame(rep(Mean, each = NumPoints))
Mean$Treatment <- rep(ActualGroupOrder, each = NumPoints) 
colnames(Mean)[1] <- "Mean"

#Stdev
Stdev <- tapply(data_frame$GD13.5.20.5, as.character(data_frame$Treatment), sd, na.rm=TRUE) #make sure to change 
Stdev <- as.data.frame(rep(Stdev, each = NumPoints))
Stdev$Treatment <- rep(ActualGroupOrder, each = NumPoints)
colnames(Stdev)[1] <- "Stdev"

#Combine
dataframe_combine <- cbind(Mean, Stdev, data_frame$GD13.5.20.5) #make sure to change
colnames(dataframe_combine)[5] <- "Value"
dataframe_combine <- dataframe_combine[-2]

#Error bars
dataframe_combine$Upper <- dataframe_combine$Mean + dataframe_combine$Stdev
dataframe_combine$Lower <- dataframe_combine$Mean - dataframe_combine$Stdev

#Make Graph#
png("Maternal_FoodIntakeDuringDosing_RmData2_PAExFe_Dotplot.png", units="in", width=7, height=7, res=600) 

sets <- c("MD", "PAE", "MD-Iron", "PAE-Iron")

p<- ggplot(dataframe_combine, aes(x=Treatment, y=Mean)) + 
  geom_bar(stat="identity", color="black", aes(fill = Treatment),
           position=position_dodge()) +
  scale_fill_manual(values=c("MD" = "#0000CC",
                             "PAE" = "#6699FF",
                             "MD-Iron" = "#660066",
                             "PAE-Iron" = "#9900CC"
                             )) +
  geom_errorbar(aes(ymin=Lower, ymax=Upper), width=.2,
                position=position_dodge(.9)) + 
  geom_point(aes(x=Treatment, y=Value),
             size = 1.25, shape = 19, position = position_jitter(width=.15, height=0)) +
  scale_y_continuous(expand = c(0,0), limits = c(0,200)) +
  ggtitle("Maternal Food Intake, GD13.5-20.5") +
  ylab(expression("Food Intake (g)")) + 
  theme(plot.title = element_text(hjust = 0.5, size=18), 
        axis.title.x = element_blank(), #gets rid of x-axis label
        axis.title.y = element_text(size = 16),
        panel.grid.major = element_blank(), #gets rid of major gridlines
        panel.grid.minor = element_blank(), #gets rid of minor gridlines
        panel.background = element_blank(), #turns background white instead of gray
        axis.line = element_line(colour = "black"), 
        legend.position="none", #gets rid of legend
        axis.text=element_text(size=18, color = "black"), #sets size of x and y axis labels
        axis.text.x=element_text(angle = 45, vjust = .95, hjust = 0.9),
        axis.title=element_text(size=20,face="bold")) + 
  scale_x_discrete (limits = sets)
print(p)
dev.off() 
```
```{r Maternal Food Intake During Dosing, echo = FALSE, warning = FALSE, message = FALSE}
print(p)
```

# Maternal Food Conversion into Weight
This number is calculated as gestational weight gain (GD0.5-GD20.5) divided by the total number of Kcal of food they consumed.
```{r, echo = FALSE, warning = FALSE, message = FALSE}
#Mean
Mean <- tapply(data_frame$WtGainOverKcalIntakeFood, as.character(data_frame$Treatment), mean, na.rm=TRUE) #make sure to change 
Mean <- as.data.frame(rep(Mean, each = NumPoints))
Mean$Treatment <- rep(ActualGroupOrder, each = NumPoints) 
colnames(Mean)[1] <- "Mean"

#Stdev
Stdev <- tapply(data_frame$WtGainOverKcalIntakeFood, as.character(data_frame$Treatment), sd, na.rm=TRUE) #make sure to change 
Stdev <- as.data.frame(rep(Stdev, each = NumPoints))
Stdev$Treatment <- rep(ActualGroupOrder, each = NumPoints)
colnames(Stdev)[1] <- "Stdev"

#Combine
dataframe_combine <- cbind(Mean, Stdev, data_frame$WtGainOverKcalIntakeFood) #make sure to change
colnames(dataframe_combine)[5] <- "Value"
dataframe_combine <- dataframe_combine[-2]

#Error bars
dataframe_combine$Upper <- dataframe_combine$Mean + dataframe_combine$Stdev
dataframe_combine$Lower <- dataframe_combine$Mean - dataframe_combine$Stdev

#Make Graph#
png("Maternal_FoodIntakeConversionIntoWeight_RmData2_PAExFe_Dotplot.png", units="in", width=7, height=7, res=600) 

sets <- c("MD", "PAE", "MD-Iron", "PAE-Iron")

p<- ggplot(dataframe_combine, aes(x=Treatment, y=Mean)) + 
  geom_bar(stat="identity", color="black", aes(fill = Treatment),
           position=position_dodge()) +
  scale_fill_manual(values=c("MD" = "#0000CC",
                             "PAE" = "#6699FF",
                             "MD-Iron" = "#660066",
                             "PAE-Iron" = "#9900CC"
                             )) +
  geom_errorbar(aes(ymin=Lower, ymax=Upper), width=.2,
                position=position_dodge(.9)) + 
  geom_point(aes(x=Treatment, y=Value),
             size = 1.25, shape = 19, position = position_jitter(width=.3, height=0)) +
  scale_y_continuous(expand = c(0,0), limits = c(0,.1)) +
  ggtitle("Maternal Food Conversion into Weight Gain") +
  ylab(expression("Prenatal Weight Gain/Total Food Intake (g Wt/Kcal Food)")) + 
  theme(plot.title = element_text(hjust = 0.5, size=18), 
        axis.title.x = element_blank(), #gets rid of x-axis label
        axis.title.y = element_text(size = 16),
        panel.grid.major = element_blank(), #gets rid of major gridlines
        panel.grid.minor = element_blank(), #gets rid of minor gridlines
        panel.background = element_blank(), #turns background white instead of gray
        axis.line = element_line(colour = "black"), 
        legend.position="none", #gets rid of legend
        axis.text=element_text(size=18, color = "black"), #sets size of x and y axis labels
        axis.text.x=element_text(angle = 45, vjust = .95, hjust = 0.9),
        axis.title=element_text(size=20,face="bold")) + 
  scale_x_discrete (limits = sets)
print(p)
dev.off() 
```
```{r Maternal Food Conversion into Weight, echo = FALSE, warning = FALSE, message = FALSE}
print(p)
```

# Maternal Conversion of all calories consumed (including alcohol or maltodextrin) into weight gain
This number is calculated as gestational weight gain (GD0.5-GD20.5) divided by the total number of Kcal of food + the number of Kcal from the alcohol or maltodextrin they consumed.
```{r, echo = FALSE, warning = FALSE, message = FALSE}
#Mean
Mean <- tapply(data_frame$WtGainOverKcalIntakeTotal, as.character(data_frame$Treatment), mean, na.rm=TRUE) #make sure to change 
Mean <- as.data.frame(rep(Mean, each = NumPoints))
Mean$Treatment <- rep(ActualGroupOrder, each = NumPoints) 
colnames(Mean)[1] <- "Mean"

#Stdev
Stdev <- tapply(data_frame$WtGainOverKcalIntakeTotal, as.character(data_frame$Treatment), sd, na.rm=TRUE) #make sure to change 
Stdev <- as.data.frame(rep(Stdev, each = NumPoints))
Stdev$Treatment <- rep(ActualGroupOrder, each = NumPoints)
colnames(Stdev)[1] <- "Stdev"

#Combine
dataframe_combine <- cbind(Mean, Stdev, data_frame$WtGainOverKcalIntakeTotal) #make sure to change
colnames(dataframe_combine)[5] <- "Value"
dataframe_combine <- dataframe_combine[-2]

#Error bars
dataframe_combine$Upper <- dataframe_combine$Mean + dataframe_combine$Stdev
dataframe_combine$Lower <- dataframe_combine$Mean - dataframe_combine$Stdev

#Make Graph#
png("Maternal_TotalCalorieIntakeConversionIntoWeight_RmData2_PAExFe_Dotplot.png", units="in", width=7, height=7, res=600) 

sets <- c("MD", "PAE", "MD-Iron", "PAE-Iron")

p<- ggplot(dataframe_combine, aes(x=Treatment, y=Mean)) + 
  geom_bar(stat="identity", color="black", aes(fill = Treatment),
           position=position_dodge()) +
  scale_fill_manual(values=c("MD" = "#0000CC",
                             "PAE" = "#6699FF",
                             "MD-Iron" = "#660066",
                             "PAE-Iron" = "#9900CC"
                             )) +
  geom_errorbar(aes(ymin=Lower, ymax=Upper), width=.2,
                position=position_dodge(.9)) + 
  geom_point(aes(x=Treatment, y=Value),
             size = 1.25, shape = 19, position = position_jitter(width=.3, height=0)) +
  scale_y_continuous(expand = c(0,0), limits = c(0,.1)) +
  ggtitle("Maternal Total Kcal Intake Conversion into Weight Gain") +
  ylab(expression("Prenatal Weight Gain/Total Calorie Intake (g Wt/Kcal Food)")) + 
  theme(plot.title = element_text(hjust = 0.5, size=18), 
        axis.title.x = element_blank(), #gets rid of x-axis label
        axis.title.y = element_text(size = 16),
        panel.grid.major = element_blank(), #gets rid of major gridlines
        panel.grid.minor = element_blank(), #gets rid of minor gridlines
        panel.background = element_blank(), #turns background white instead of gray
        axis.line = element_line(colour = "black"), 
        legend.position="none", #gets rid of legend
        axis.text=element_text(size=18, color = "black"), #sets size of x and y axis labels
        axis.text.x=element_text(angle = 45, vjust = .95, hjust = 0.9),
        axis.title=element_text(size=20,face="bold")) + 
  scale_x_discrete (limits = sets)
print(p)
dev.off() 
```
```{r Maternal Total Kcal Conversion into Weight, echo = FALSE, warning = FALSE, message = FALSE}
print(p)
```

# Maternal Prenatal Food Intake Over Total Pregnancy
```{r}
ActualGroupOrder2 <- c("4-PAE+iron", "2-PAE", "3-MD+iron", "1-MD")
```

## Create mean and standard deviation tables for each day of pregnancy
```{r}
#Food Intake at GD3.5
GD3.5 <- tapply(data_frame$GD3.5, as.character(data_frame$Treatment), mean, na.rm=TRUE)
GD3.5 <- as.data.frame(GD3.5)
GD3.5$Treatment <- ActualGroupOrder2
colnames(GD3.5)[1] <- "Mean" #fix column name
GD3.5.Stdev <- tapply(data_frame$GD3.5, as.character(data_frame$Treatment), sd, na.rm=TRUE)
GD3.5$Stdev <- GD3.5.Stdev
GD3.5$Day <- rep("03.5", 4)

#Food Intake at GD5.5
GD5.5 <- tapply(data_frame$GD5.5, as.character(data_frame$Treatment), mean, na.rm=TRUE)
GD5.5 <- as.data.frame(GD5.5)
GD5.5$Treatment <- ActualGroupOrder2
colnames(GD5.5)[1] <- "Mean" #fix column name
GD5.5.Stdev <- tapply(data_frame$GD5.5, as.character(data_frame$Treatment), sd, na.rm=TRUE)
GD5.5$Stdev <- GD5.5.Stdev
GD5.5$Day <- rep("05.5", 4)

#Food Intake at GD8.5
GD8.5 <- tapply(data_frame$GD8.5, as.character(data_frame$Treatment), mean, na.rm=TRUE)
GD8.5 <- as.data.frame(GD8.5)
GD8.5$Treatment <- ActualGroupOrder2
colnames(GD8.5)[1] <- "Mean" #fix column name
GD8.5.Stdev <- tapply(data_frame$GD8.5, as.character(data_frame$Treatment), sd, na.rm=TRUE)
GD8.5$Stdev <- GD8.5.Stdev
GD8.5$Day <- rep("08.5", 4)

#Food Intake at GD11.5
GD11.5 <- tapply(data_frame$GD11.5, as.character(data_frame$Treatment), mean, na.rm=TRUE)
GD11.5 <- as.data.frame(GD11.5)
GD11.5$Treatment <- ActualGroupOrder2
colnames(GD11.5)[1] <- "Mean" #fix column name
GD11.5.Stdev <- tapply(data_frame$GD11.5, as.character(data_frame$Treatment), sd, na.rm=TRUE)
GD11.5$Stdev <- GD11.5.Stdev
GD11.5$Day <- rep("11.5", 4)

#Food Intake at GD12.5
GD12.5 <- tapply(data_frame$GD12.5, as.character(data_frame$Treatment), mean, na.rm=TRUE)
GD12.5 <- as.data.frame(GD12.5)
GD12.5$Treatment <- ActualGroupOrder2
colnames(GD12.5)[1] <- "Mean" #fix column name
GD12.5.Stdev <- tapply(data_frame$GD12.5, as.character(data_frame$Treatment), sd, na.rm=TRUE)
GD12.5$Stdev <- GD12.5.Stdev
GD12.5$Day <- rep("12.5", 4)

#Food Intake at GD13.5
GD13.5 <- tapply(data_frame$GD13.5, as.character(data_frame$Treatment), mean, na.rm=TRUE)
GD13.5 <- as.data.frame(GD13.5)
GD13.5$Treatment <- ActualGroupOrder2
colnames(GD13.5)[1] <- "Mean" #fix column name
GD13.5.Stdev <- tapply(data_frame$GD13.5, as.character(data_frame$Treatment), sd, na.rm=TRUE)
GD13.5$Stdev <- GD13.5.Stdev
GD13.5$Day <- rep("13.5", 4)

#Food Intake at GD14.5
GD14.5 <- tapply(data_frame$GD14.5, as.character(data_frame$Treatment), mean, na.rm=TRUE)
GD14.5 <- as.data.frame(GD14.5)
GD14.5$Treatment <- ActualGroupOrder2
colnames(GD14.5)[1] <- "Mean" #fix column name
GD14.5.Stdev <- tapply(data_frame$GD14.5, as.character(data_frame$Treatment), sd, na.rm=TRUE)
GD14.5$Stdev <- GD14.5.Stdev
GD14.5$Day <- rep("14.5", 4)

#Food Intake at GD15.5
GD15.5 <- tapply(data_frame$GD15.5, as.character(data_frame$Treatment), mean, na.rm=TRUE)
GD15.5 <- as.data.frame(GD15.5)
GD15.5$Treatment <- ActualGroupOrder2
colnames(GD15.5)[1] <- "Mean" #fix column name
GD15.5.Stdev <- tapply(data_frame$GD15.5, as.character(data_frame$Treatment), sd, na.rm=TRUE)
GD15.5$Stdev <- GD15.5.Stdev
GD15.5$Day <- rep("15.5", 4)

#Food Intake at GD16.5
GD16.5 <- tapply(data_frame$GD16.5, as.character(data_frame$Treatment), mean, na.rm=TRUE)
GD16.5 <- as.data.frame(GD16.5)
GD16.5$Treatment <- ActualGroupOrder2
colnames(GD16.5)[1] <- "Mean" #fix column name
GD16.5.Stdev <- tapply(data_frame$GD16.5, as.character(data_frame$Treatment), sd, na.rm=TRUE)
GD16.5$Stdev <- GD16.5.Stdev
GD16.5$Day <- rep("16.5", 4)

#Food Intake at GD17.5
GD17.5 <- tapply(data_frame$GD17.5, as.character(data_frame$Treatment), mean, na.rm=TRUE)
GD17.5 <- as.data.frame(GD17.5)
GD17.5$Treatment <- ActualGroupOrder2
colnames(GD17.5)[1] <- "Mean" #fix column name
GD17.5.Stdev <- tapply(data_frame$GD17.5, as.character(data_frame$Treatment), sd, na.rm=TRUE)
GD17.5$Stdev <- GD17.5.Stdev
GD17.5$Day <- rep("17.5", 4)

#Food Intake at GD18.5
GD18.5 <- tapply(data_frame$GD18.5, as.character(data_frame$Treatment), mean, na.rm=TRUE)
GD18.5 <- as.data.frame(GD18.5)
GD18.5$Treatment <- ActualGroupOrder2
colnames(GD18.5)[1] <- "Mean" #fix column name
GD18.5.Stdev <- tapply(data_frame$GD18.5, as.character(data_frame$Treatment), sd, na.rm=TRUE)
GD18.5$Stdev <- GD18.5.Stdev
GD18.5$Day <- rep("18.5", 4)

#Food Intake at GD19.5
GD19.5 <- tapply(data_frame$GD19.5, as.character(data_frame$Treatment), mean, na.rm=TRUE)
GD19.5 <- as.data.frame(GD19.5)
GD19.5$Treatment <- ActualGroupOrder2
colnames(GD19.5)[1] <- "Mean" #fix column name
GD19.5.Stdev <- tapply(data_frame$GD19.5, as.character(data_frame$Treatment), sd, na.rm=TRUE)
GD19.5$Stdev <- GD19.5.Stdev
GD19.5$Day <- rep("19.5", 4)

#Food Intake at GD20.5
GD20.5 <- tapply(data_frame$GD20.5, as.character(data_frame$Treatment), mean, na.rm=TRUE)
GD20.5 <- as.data.frame(GD20.5)
GD20.5$Treatment <- ActualGroupOrder2
colnames(GD20.5)[1] <- "Mean" #fix column name
GD20.5.Stdev <- tapply(data_frame$GD20.5, as.character(data_frame$Treatment), sd, na.rm=TRUE)
GD20.5$Stdev <- GD20.5.Stdev
GD20.5$Day <- rep("20.5", 4)
```
```{r Merge tables}
#Merge all tables
FoodIntake_combined <- rbind(GD3.5, GD5.5, GD8.5, GD11.5, GD12.5, GD13.5, GD14.5, GD15.5, GD16.5, GD17.5, GD18.5, GD19.5, GD20.5)
FoodIntake_combined <- FoodIntake_combined[ ,c(2,1,3,4)]
FoodIntake_combined$Day <- as.numeric(as.vector(FoodIntake_combined$Day)) #convert "Age" to a numeric variable so the x-axis adjusts accordingly
names(FoodIntake_combined)[1] <- "Exposure.Group"
FoodIntake_combined$Upper <- FoodIntake_combined$Mean + FoodIntake_combined$Stdev
FoodIntake_combined$Lower <- FoodIntake_combined$Mean - FoodIntake_combined$Stdev
```

## Graph Maternal Food Intake
```{r}
#generate with and without error bars
png("Maternal_PrenatalFoodIntake_wErrorBars_RmData2_PAExFe_LineGraph.png", units="in", width=10, height=7, res=600)

FI <- ggplot(data=FoodIntake_combined, aes(x=Day, y=Mean, group=Exposure.Group, color=Exposure.Group)) +
  geom_point() +
  geom_line() +
  scale_y_continuous(expand = c(0,0), limits = c(0,30))+ 
  scale_color_hue(labels = c("MD", "PAE", "MD+iron", "PAE+iron")) +
  geom_errorbar(aes(ymin=Lower, ymax=Upper), width=.2) + #generate with and without the error bars
  ggtitle("Maternal Prenatal Food Intake") +
  ylab(expression("Food Intake (g)")) + 
  xlab(expression("Gestational Day")) +
  theme(plot.title = element_text(hjust = 0.5, size=18), 
        axis.title.y = element_text(size = 16),
        axis.title.x = element_text(size = 16),
        panel.grid.major = element_blank(), #gets rid of major gridlines
        panel.grid.minor = element_blank(), #gets rid of minor gridlines
        panel.background = element_blank(), #turns background white instead of gray
        axis.line = element_line(colour = "black"), 
        axis.text=element_text(size=18, color = "black"), #sets size of x and y axis labels
        axis.text.x=element_text(vjust = .95, hjust = 0.9),
        axis.title=element_text(size=20,face="bold"))
  
print(FI)
dev.off()
```
```{r Maternal Prenatal Food Intake Graph, echo = FALSE, warning = FALSE, message = FALSE}
print(FI)
```

# Maternal Prenatal Kcal Intake Over Total Pregnancy
```{r Import file #2 and rearrange by treatment to be alphabetical}
File2 <- "MaternalEnergyIntake_RmData2.csv"
dataframe2 <- read.csv(File2, header=TRUE) 
dataframe2 <- dataframe2[order(dataframe2$Treatment), ]
```
```{r echo = FALSE}
print(dataframe2)
```

## Create mean and standard deviation tables for Kcal intake on each day of pregnancy
```{r}
#Kcal Intake at GD3.5
GD3.5 <- tapply(dataframe2$Total.Energy.3.5, as.character(dataframe2$Treatment), mean, na.rm=TRUE)
GD3.5 <- as.data.frame(GD3.5)
GD3.5$Treatment <- ActualGroupOrder2
colnames(GD3.5)[1] <- "Mean" #fix column name
GD3.5.Stdev <- tapply(dataframe2$Total.Energy.3.5, as.character(dataframe2$Treatment), sd, na.rm=TRUE)
GD3.5$Stdev <- GD3.5.Stdev
GD3.5$Day <- rep("03.5", 4)

#Kcal Intake at GD5.5
GD5.5 <- tapply(dataframe2$Total.Energy.5.5, as.character(dataframe2$Treatment), mean, na.rm=TRUE)
GD5.5 <- as.data.frame(GD5.5)
GD5.5$Treatment <- ActualGroupOrder2
colnames(GD5.5)[1] <- "Mean" #fix column name
GD5.5.Stdev <- tapply(dataframe2$Total.Energy.5.5, as.character(dataframe2$Treatment), sd, na.rm=TRUE)
GD5.5$Stdev <- GD5.5.Stdev
GD5.5$Day <- rep("05.5", 4)

#Kcal Intake at GD8.5
GD8.5 <- tapply(dataframe2$Total.Energy.8.5, as.character(dataframe2$Treatment), mean, na.rm=TRUE)
GD8.5 <- as.data.frame(GD8.5)
GD8.5$Treatment <- ActualGroupOrder2
colnames(GD8.5)[1] <- "Mean" #fix column name
GD8.5.Stdev <- tapply(dataframe2$Total.Energy.8.5, as.character(dataframe2$Treatment), sd, na.rm=TRUE)
GD8.5$Stdev <- GD8.5.Stdev
GD8.5$Day <- rep("08.5", 4)

#Kcal Intake at GD11.5
GD11.5 <- tapply(dataframe2$Total.Energy.11.5, as.character(dataframe2$Treatment), mean, na.rm=TRUE)
GD11.5 <- as.data.frame(GD11.5)
GD11.5$Treatment <- ActualGroupOrder2
colnames(GD11.5)[1] <- "Mean" #fix column name
GD11.5.Stdev <- tapply(dataframe2$Total.Energy.11.5, as.character(dataframe2$Treatment), sd, na.rm=TRUE)
GD11.5$Stdev <- GD11.5.Stdev
GD11.5$Day <- rep("11.5", 4)

#Kcal Intake at GD12.5
GD12.5 <- tapply(dataframe2$Total.Energy.12.5, as.character(dataframe2$Treatment), mean, na.rm=TRUE)
GD12.5 <- as.data.frame(GD12.5)
GD12.5$Treatment <- ActualGroupOrder2
colnames(GD12.5)[1] <- "Mean" #fix column name
GD12.5.Stdev <- tapply(dataframe2$Total.Energy.12.5, as.character(dataframe2$Treatment), sd, na.rm=TRUE)
GD12.5$Stdev <- GD12.5.Stdev
GD12.5$Day <- rep("12.5", 4)

#Kcal Intake at GD13.5
GD13.5 <- tapply(dataframe2$Total.Energy.13.5, as.character(dataframe2$Treatment), mean, na.rm=TRUE)
GD13.5 <- as.data.frame(GD13.5)
GD13.5$Treatment <- ActualGroupOrder2
colnames(GD13.5)[1] <- "Mean" #fix column name
GD13.5.Stdev <- tapply(dataframe2$Total.Energy.13.5, as.character(dataframe2$Treatment), sd, na.rm=TRUE)
GD13.5$Stdev <- GD13.5.Stdev
GD13.5$Day <- rep("13.5", 4)

#Kcal Intake at GD14.5
GD14.5 <- tapply(dataframe2$Total.Energy.14.5, as.character(dataframe2$Treatment), mean, na.rm=TRUE)
GD14.5 <- as.data.frame(GD14.5)
GD14.5$Treatment <- ActualGroupOrder2
colnames(GD14.5)[1] <- "Mean" #fix column name
GD14.5.Stdev <- tapply(dataframe2$Total.Energy.14.5, as.character(dataframe2$Treatment), sd, na.rm=TRUE)
GD14.5$Stdev <- GD14.5.Stdev
GD14.5$Day <- rep("14.5", 4)

#Kcal Intake at GD15.5
GD15.5 <- tapply(dataframe2$Total.Energy.15.5, as.character(dataframe2$Treatment), mean, na.rm=TRUE)
GD15.5 <- as.data.frame(GD15.5)
GD15.5$Treatment <- ActualGroupOrder2
colnames(GD15.5)[1] <- "Mean" #fix column name
GD15.5.Stdev <- tapply(dataframe2$Total.Energy.15.5, as.character(dataframe2$Treatment), sd, na.rm=TRUE)
GD15.5$Stdev <- GD15.5.Stdev
GD15.5$Day <- rep("15.5", 4)

#Kcal Intake at GD16.5
GD16.5 <- tapply(dataframe2$Total.Energy.16.5, as.character(dataframe2$Treatment), mean, na.rm=TRUE)
GD16.5 <- as.data.frame(GD16.5)
GD16.5$Treatment <- ActualGroupOrder2
colnames(GD16.5)[1] <- "Mean" #fix column name
GD16.5.Stdev <- tapply(dataframe2$Total.Energy.16.5, as.character(dataframe2$Treatment), sd, na.rm=TRUE)
GD16.5$Stdev <- GD16.5.Stdev
GD16.5$Day <- rep("16.5", 4)

#Kcal Intake at GD17.5
GD17.5 <- tapply(dataframe2$Total.Energy.17.5, as.character(dataframe2$Treatment), mean, na.rm=TRUE)
GD17.5 <- as.data.frame(GD17.5)
GD17.5$Treatment <- ActualGroupOrder2
colnames(GD17.5)[1] <- "Mean" #fix column name
GD17.5.Stdev <- tapply(dataframe2$Total.Energy.17.5, as.character(dataframe2$Treatment), sd, na.rm=TRUE)
GD17.5$Stdev <- GD17.5.Stdev
GD17.5$Day <- rep("17.5", 4)

#Kcal Intake at GD18.5
GD18.5 <- tapply(dataframe2$Total.Energy.18.5, as.character(dataframe2$Treatment), mean, na.rm=TRUE)
GD18.5 <- as.data.frame(GD18.5)
GD18.5$Treatment <- ActualGroupOrder2
colnames(GD18.5)[1] <- "Mean" #fix column name
GD18.5.Stdev <- tapply(dataframe2$Total.Energy.18.5, as.character(dataframe2$Treatment), sd, na.rm=TRUE)
GD18.5$Stdev <- GD18.5.Stdev
GD18.5$Day <- rep("18.5", 4)

#Kcal Intake at GD19.5
GD19.5 <- tapply(dataframe2$Total.Energy.19.5, as.character(dataframe2$Treatment), mean, na.rm=TRUE)
GD19.5 <- as.data.frame(GD19.5)
GD19.5$Treatment <- ActualGroupOrder2
colnames(GD19.5)[1] <- "Mean" #fix column name
GD19.5.Stdev <- tapply(dataframe2$Total.Energy.19.5, as.character(dataframe2$Treatment), sd, na.rm=TRUE)
GD19.5$Stdev <- GD19.5.Stdev
GD19.5$Day <- rep("19.5", 4)

#Kcal Intake at GD20.5
GD20.5 <- tapply(dataframe2$Total.Energy.20.5, as.character(dataframe2$Treatment), mean, na.rm=TRUE)
GD20.5 <- as.data.frame(GD20.5)
GD20.5$Treatment <- ActualGroupOrder2
colnames(GD20.5)[1] <- "Mean" #fix column name
GD20.5.Stdev <- tapply(dataframe2$Total.Energy.20.5, as.character(dataframe2$Treatment), sd, na.rm=TRUE)
GD20.5$Stdev <- GD20.5.Stdev
GD20.5$Day <- rep("20.5", 4)
```
```{r Merge tables 2}
#Merge all tables
KcalIntake_combined <- rbind(GD3.5, GD5.5, GD8.5, GD11.5, GD12.5, GD13.5, GD14.5, GD15.5, GD16.5, GD17.5, GD18.5, GD19.5, GD20.5)
KcalIntake_combined <- KcalIntake_combined[ ,c(2,1,3,4)]
KcalIntake_combined$Day <- as.numeric(as.vector(KcalIntake_combined$Day)) #convert "Day" to a numeric variable so the x-axis adjusts accordingly
names(KcalIntake_combined)[1] <- "Exposure.Group"
KcalIntake_combined$Upper <- KcalIntake_combined$Mean + KcalIntake_combined$Stdev
KcalIntake_combined$Lower <- KcalIntake_combined$Mean - KcalIntake_combined$Stdev
```

## Graph Maternal Food Intake
```{r}
#generate with and without error bars
png("Maternal_PrenatalKcalIntake_wErrorBars_RmData2_PAExFe_LineGraph.png", units="in", width=10, height=7, res=600)

KCalI <- ggplot(data=KcalIntake_combined, aes(x=Day, y=Mean, group=Exposure.Group, color=Exposure.Group)) +
  geom_point() +
  geom_line() +
  scale_y_continuous(expand = c(0,0), limits = c(0,110))+ 
  scale_color_hue(labels = c("MD", "PAE", "MD+iron", "PAE+iron")) +
  geom_errorbar(aes(ymin=Lower, ymax=Upper), width=.2) + #generate with and without the error bars
  ggtitle("Maternal Prenatal Energy Intake") +
  ylab(expression("Energy Intake (Kcal)")) + 
  xlab(expression("Gestational Day")) +
  theme(plot.title = element_text(hjust = 0.5, size=18), 
        axis.title.y = element_text(size = 16),
        axis.title.x = element_text(size = 16),
        panel.grid.major = element_blank(), #gets rid of major gridlines
        panel.grid.minor = element_blank(), #gets rid of minor gridlines
        panel.background = element_blank(), #turns background white instead of gray
        axis.line = element_line(colour = "black"), 
        axis.text=element_text(size=18, color = "black"), #sets size of x and y axis labels
        axis.text.x=element_text(vjust = .95, hjust = 0.9),
        axis.title=element_text(size=20,face="bold"))
  
print(KCalI)
dev.off()
```
```{r Maternal Prenatal Kcal Intake Graph, echo = FALSE, warning = FALSE, message = FALSE}
print(KCalI)
```

# Session Information
```{r, echo = FALSE}
session_info <- devtools::session_info()
print(session_info)
```
