---
title: "Fetal Rat Hematology Data AIN-76A diet with MD or Alcohol and Iron Supplement or Water- GD20.5, 2 Litters Removed"
author: "Kaylee Helfrich"
date: "10/2/2020"
output: 
  pdf_document: default
  html_document: default
data: "FetalRatHematology_DataSheet_Nov-Dec2019_RmData2.csv"
---

Built with R `r getRversion()`

```{r RMarkdown setup, include = FALSE, message = FALSE}
require(knitr)
knitr::opts_chunk$set(echo = TRUE, tidy.opts=list(width.cutoff=60), tidy=TRUE)
knitr::opts_knit$set(root.dir = "~/KayleeStuff/Smith_Lab/Data/Rat_Iron/Fetal_Blood/RmData2-USETHIS")
options(tinytex.verbose = TRUE)
```

# Graphing Fetal Rat CBCs
This document details my graphing of the hematology data from fetal rat CBCs. This analysis uses all data that was collected, except for 2 litters (R029 MD+H2O and R031 MD+Fe) which had only 2 fetuses and were more than 2 standard deviations away from the mean litter size. All samples were collected between 11/2019-12/2019 by Kaylee Helfrich. Long-Evans rats arrived at 7 weeks old and were mated at 9-11 weeks of age. The rats were dosed with 5g/kg ethanol or isocaloric maltodextrin from GD13.5-19.5. The dams also received either an iron supplement (6g/kg, Fer-In-Sol) or the same volume of water as a gavage from GD12.5-GD19.5. All dams consumed AIN-76G diet modified to contain 100ppm of iron from arrival through pregnancy. Tissues were harvested on GD20.5. Blood was collected from the fetuses by decapitation and EDTA collection on the inverted fetal trunk. Blood was pooled across the litter. The blood was run using the standard mode on the pochi analyzer (except for 3 litters which are R014, R029, and R031). All graphs are mean with standard deviation, since there are not multiple measures per sample. This analysis will allow us to compare the 4 groups. Statistical analysis in JMP will use ANOVA to assign significance to the measures. 

```{r include = FALSE}
rm(list=ls())
setwd("~/KayleeStuff/Smith_Lab/Data/Rat_Iron/Fetal_Blood/RmData2-USETHIS")
library(ggplot2)
library(plotrix)
library(extrafont)
loadfonts(device = "win")
```

```{r Import file and rearrange by treatment to be alphabetical}
File <- "FetalRatHematology_DataSheet_Nov-Dec2019_RmData2.csv"
data <- read.csv(File, header=TRUE) 
data_frame <- data.frame(data)
data_frame <- data_frame[order(data_frame$Treatment), ]
```
```{r echo = FALSE}
print(data_frame)
```
```{r Prepare data for graphing}
ActualGroupOrder <- c("ALC+Iron", "ALC","CON+Iron", "CON")
NumPoints <- 9 #Make sure to set the integer to the number of dots/values you have for each treatment
```

#RBCs
## All code is included for this first example, but thereafter, only the heading and graphs are shown. For all graphs, all data is graphed unless mentioned otherwise. Messages and warnings are excluded, since NA's were included to make all groups even, and I didn't want the code to print out these errors when they weren't necessary.
```{r, warning = FALSE, message = FALSE}
#Mean- calculate mean for column, repeat it to number of points, and create dataframe
Mean <- tapply(data_frame$RBC, as.character(data_frame$Treatment), mean, na.rm=TRUE) #make sure to change selected column to change data for graph
Mean <- as.data.frame(rep(Mean, each = NumPoints)) #repeat mean a set number of times
Mean$Treatment <- rep(ActualGroupOrder, each = NumPoints) #repeat treatment a set number of times
colnames(Mean)[1] <- "Mean" #fix column name

#Stdev- calculate standard deviation for column, repeat it to number of points, and create dataframe
Stdev <- tapply(data_frame$RBC, as.character(data_frame$Treatment), sd, na.rm=TRUE) #make sure to change selected column
Stdev <- as.data.frame(rep(Stdev, each = NumPoints)) #repeat stdev a set number of times
Stdev$Treatment <- rep(ActualGroupOrder, each = NumPoints) #repeat treatment a set number of times
colnames(Stdev)[1] <- "Stdev" #fix column name

#Combine mean, standard deviation, and individual data points
dataframe_combine <- cbind(Mean, Stdev, data_frame$RBC) #make sure to change selected column
colnames(dataframe_combine)[5] <- "Value" #Fix name of individual data point column
dataframe_combine <- dataframe_combine[-2] #Remove extra treatment column

#Error bars
dataframe_combine$Upper <- dataframe_combine$Mean + dataframe_combine$Stdev #upper error
dataframe_combine$Lower <- dataframe_combine$Mean - dataframe_combine$Stdev #lower error

#Make Graph#
png("Fetal_RBCs_RmData2_PAExFe_Dotplot_B&W.png", units="in", width=4, height=7, res=600) 

sets <- c("CON", "ALC", "CON+Iron", "ALC+Iron")

p<- ggplot(dataframe_combine, aes(x=Treatment, y=Mean)) + 
  geom_bar(stat="identity", color="black", aes(fill = Treatment),
           position=position_dodge()) +
  scale_fill_manual(values=c("CON" = "grey100",
                             "ALC" = "grey51",
                             "CON+Iron" = "grey75",
                             "ALC+Iron" = "grey30"
                             )) +
  geom_errorbar(aes(ymin=Lower, ymax=Upper), width=.2,
                position=position_dodge(.9)) + 
  geom_point(aes(x=Treatment, y=Value),
             size = 1.25, shape = 19, position = position_jitter(width=.15, height=0)) +
  scale_y_continuous(expand = c(0,0), limits = c(0,3)) +
  ggtitle("Fetal RBCs") +
  ylab(expression("Fetal RBCs (x10^6 cells/uL)")) + 
  theme(plot.title = element_text(hjust = 0.5, size=18, family = "Times New Roman"), 
        axis.title.x = element_blank(), #gets rid of x-axis label
        axis.title.y = element_text(size = 20, family = "Times New Roman"),
        panel.grid.major = element_blank(), #gets rid of major gridlines
        panel.grid.minor = element_blank(), #gets rid of minor gridlines
        panel.background = element_blank(), #turns background white instead of gray
        axis.line = element_line(colour = "black"), 
        legend.position="none", #gets rid of legend
        axis.text=element_text(size=18, color = "black", family = "Times New Roman"), #sets size of x and y axis labels
        axis.text.x=element_text(angle = 45, vjust = .95, hjust = 0.9, family = "Times New Roman"),
        axis.title=element_text(size=22,face="bold", family = "Times New Roman")) + 
  scale_x_discrete (limits = sets)
print(p)
dev.off() 
```
```{r Red Blood Cells, echo = FALSE}
print(p)
```

# Hemoglobin
```{r, echo = FALSE, warning = FALSE, message = FALSE}
#Mean
Mean <- tapply(data_frame$HGB, as.character(data_frame$Treatment), mean, na.rm=TRUE) #make sure to change 
Mean <- as.data.frame(rep(Mean, each = NumPoints))
Mean$Treatment <- rep(ActualGroupOrder, each = NumPoints) 
colnames(Mean)[1] <- "Mean"

#Stdev
Stdev <- tapply(data_frame$HGB, as.character(data_frame$Treatment), sd, na.rm=TRUE) #make sure to change 
Stdev <- as.data.frame(rep(Stdev, each = NumPoints))
Stdev$Treatment <- rep(ActualGroupOrder, each = NumPoints)
colnames(Stdev)[1] <- "Stdev"

#Combine
dataframe_combine <- cbind(Mean, Stdev, data_frame$HGB) #make sure to change
colnames(dataframe_combine)[5] <- "Value"
dataframe_combine <- dataframe_combine[-2]

#Error bars
dataframe_combine$Upper <- dataframe_combine$Mean + dataframe_combine$Stdev
dataframe_combine$Lower <- dataframe_combine$Mean - dataframe_combine$Stdev

#Make Graph#
png("Fetal_Hemoglobin_RmData2_PAExFe_Dotplot_B&W.png", units="in", width=4, height=7, res=600) 

sets <- c("CON", "ALC", "CON+Iron", "ALC+Iron")

p<- ggplot(dataframe_combine, aes(x=Treatment, y=Mean)) + 
  geom_bar(stat="identity", color="black", aes(fill = Treatment),
           position=position_dodge()) +
  scale_fill_manual(values=c("CON" = "grey100",
                             "ALC" = "grey51",
                             "CON+Iron" = "grey75",
                             "ALC+Iron" = "grey30"
                             )) +
  geom_errorbar(aes(ymin=Lower, ymax=Upper), width=.2,
                position=position_dodge(.9)) + 
  geom_point(aes(x=Treatment, y=Value),
             size = 1.25, shape = 19, position = position_jitter(width=.15, height=0)) +
  scale_y_continuous(expand = c(0,0), limits = c(0,15)) +
  ggtitle("Fetal Hemoglobin") +
  ylab(expression("Fetal Hemoglobin (g/dL)")) + 
  theme(plot.title = element_text(hjust = 0.5, size=18, family = "Times New Roman"), 
        axis.title.x = element_blank(), #gets rid of x-axis label
        axis.title.y = element_text(size = 20, family = "Times New Roman"),
        panel.grid.major = element_blank(), #gets rid of major gridlines
        panel.grid.minor = element_blank(), #gets rid of minor gridlines
        panel.background = element_blank(), #turns background white instead of gray
        axis.line = element_line(colour = "black"), 
        legend.position="none", #gets rid of legend
        axis.text=element_text(size=18, color = "black", family = "Times New Roman"), #sets size of x and y axis labels
        axis.text.x=element_text(angle = 45, vjust = .95, hjust = 0.9, family = "Times New Roman"),
        axis.title=element_text(size=22,face="bold", family = "Times New Roman")) + 
  scale_x_discrete (limits = sets)
print(p)
dev.off() 
```
```{r Hemoglobin, echo = FALSE, warning = FALSE, message = FALSE}
print(p)
```

# Hematocrit
```{r, echo = FALSE, warning = FALSE, message = FALSE}
#Mean
Mean <- tapply(data_frame$HCT, as.character(data_frame$Treatment), mean, na.rm=TRUE) #make sure to change 
Mean <- as.data.frame(rep(Mean, each = NumPoints))
Mean$Treatment <- rep(ActualGroupOrder, each = NumPoints) 
colnames(Mean)[1] <- "Mean"

#Stdev
Stdev <- tapply(data_frame$HCT, as.character(data_frame$Treatment), sd, na.rm=TRUE) #make sure to change 
Stdev <- as.data.frame(rep(Stdev, each = NumPoints))
Stdev$Treatment <- rep(ActualGroupOrder, each = NumPoints)
colnames(Stdev)[1] <- "Stdev"

#Combine
dataframe_combine <- cbind(Mean, Stdev, data_frame$HCT) #make sure to change
colnames(dataframe_combine)[5] <- "Value"
dataframe_combine <- dataframe_combine[-2]

#Error bars
dataframe_combine$Upper <- dataframe_combine$Mean + dataframe_combine$Stdev
dataframe_combine$Lower <- dataframe_combine$Mean - dataframe_combine$Stdev

#Make Graph#
png("Fetal_Hematocrit_RmData2_PAExFe_Dotplot_B&W.png", units="in", width=4, height=7, res=600) 

sets <- c("CON", "ALC", "CON+Iron", "ALC+Iron")

p<- ggplot(dataframe_combine, aes(x=Treatment, y=Mean)) + 
  geom_bar(stat="identity", color="black", aes(fill = Treatment),
           position=position_dodge()) +
  scale_fill_manual(values=c("CON" = "grey100",
                             "ALC" = "grey51",
                             "CON+Iron" = "grey75",
                             "ALC+Iron" = "grey30"
                             )) +
  geom_errorbar(aes(ymin=Lower, ymax=Upper), width=.2,
                position=position_dodge(.9)) + 
  geom_point(aes(x=Treatment, y=Value),
             size = 1.25, shape = 19, position = position_jitter(width=.15, height=0)) +
  scale_y_continuous(expand = c(0,0), limits = c(0,50)) +
  ggtitle("Fetal Hematocrit") +
  ylab(expression("Fetal Hematocrit (%)")) + 
  theme(plot.title = element_text(hjust = 0.5, size=18, family = "Times New Roman"), 
        axis.title.x = element_blank(), #gets rid of x-axis label
        axis.title.y = element_text(size = 20, family = "Times New Roman"),
        panel.grid.major = element_blank(), #gets rid of major gridlines
        panel.grid.minor = element_blank(), #gets rid of minor gridlines
        panel.background = element_blank(), #turns background white instead of gray
        axis.line = element_line(colour = "black"), 
        legend.position="none", #gets rid of legend
        axis.text=element_text(size=18, color = "black", family = "Times New Roman"), #sets size of x and y axis labels
        axis.text.x=element_text(angle = 45, vjust = .95, hjust = 0.9, family = "Times New Roman"),
        axis.title=element_text(size=22,face="bold", family = "Times New Roman")) + 
  scale_x_discrete (limits = sets)
print(p)
dev.off() 
```
```{r Hematocrit, echo = FALSE, warning = FALSE, message = FALSE}
print(p)
```

# Session Information
```{r, echo = FALSE}
session_info <- devtools::session_info()
print(session_info)
```