---
title: "Nonheme Iron Analysis- Maternal liver, fetal liver, fetal brain- Rat Alcohol and Iron Study, GD20.5 Collection"
author: "Kaylee Helfrich"
date: "6/1/2021"
output: 
  pdf_document: default
  html_document: default
data: "[Tissue]_NonhemeIron.csv"
---

Built with R `r getRversion()`

```{r RMarkdown setup, include = FALSE, message = FALSE}
require(knitr)
knitr::opts_chunk$set(echo = TRUE, tidy.opts=list(width.cutoff=60), tidy=TRUE)
knitr::opts_knit$set(root.dir = "~/KayleeStuff/Smith_Lab/Data/Rat_Iron/Nonheme_Iron")
options(tinytex.verbose = TRUE)
```

# Overall Study Design
This document details my graphing of nonheme iron data from maternal livers, fetal livers, and fetal brains from rats. This analysis uses all data that were analyzed using the nonheme iron assay (Rebouche et al. 2004). All tissue samples were collected between 11/2019-12/2019 by Kaylee Helfrich, Olivia Rivera, Nipun Saini, and Cecilia Kwan. Long-Evans rats arrived at 7 weeks old and were mated at 9-11 weeks of age. The rats were dosed with 5g/kg ethanol or isocaloric maltodextrin from GD13.5-19.5. The dams also received either an iron supplement (6g/kg, Fer-In-Sol) or the same volume of water as a gavage from GD12.5-GD19.5. All dams consumed AIN-76G diet modified to contain 100ppm of iron from arrival through pregnancy. Tissues were harvested on GD20.5. All graphs are mean with standard deviation, since there are not multiple measures per sample. This analysis will allow us to compare the 4 groups. Statistical analysis in JMP will use ANOVA, following checks for normality and variance, to assign significance to the measures. 

```{r include = FALSE}
rm(list=ls())
setwd("~/KayleeStuff/Smith_Lab/Data/Rat_Iron/Nonheme_Iron")
library(ggplot2)
library(plotrix)
library(dplyr)
library(naniar)
```

# Maternal Liver
```{r Import ML file and rearrange by Group to be alphabetical}
ML_File <- "MaternalLiver_NonhemeIron.csv"
ML_data <- read.csv(ML_File, header=TRUE) 
ML_data_frame <- data.frame(ML_data)
ML_data_frame <- ML_data_frame[order(ML_data_frame$Group), ]
```
```{r echo = FALSE}
head(ML_data_frame)
```
```{r}
ActualGroupOrder <- c("PAE-Iron", "PAE","MD-Iron", "MD")
```

```{r}
#Figure out how many rows of empty NA's are needed to equalize the Group groups
Groupcount <- ML_data_frame %>% count(Group) #Calculate how many individual Females there are per Group group
NumPoints <- max(Groupcount$n) #Create the variable "NumPoints" to count the # of points in the final graphs
DiffFunc <- function(x) NumPoints - x #Create the function "DiffFunc" to calculate the number of NA rows to be added
DiffPoints <- as.data.frame(tapply(Groupcount$n, as.character(Groupcount$Group), DiffFunc)) #Calculate number of NA rows to be added to each Group group
DiffPoints$Group <- ActualGroupOrder #add new column so that the # of points to be added is assigned to the Group
colnames(DiffPoints)[1] <- "NumberN" #rename column
Nrow <- sum(DiffPoints$NumberN) #figure out how many total rows will be added to the DF_extra dataframe
AlcFe <- DiffPoints[1,1] #for each of these, it is creating a variable for the "vector" below
AlcH2O <- DiffPoints[2,1]
MDFe <- DiffPoints[3,1]
MDH2O <- DiffPoints[4,1]

#Add extra rows of NAs to equalize groups
DF_extra <- data.frame(matrix(NA, nrow = Nrow, ncol = 12)) #create an empty dataframe filled with NA's
vector <- rep(c("Alc+Fe", "Alc+H2O", "MD+Fe", "MD+H2O"), times = c(AlcFe, AlcH2O, MDFe, MDH2O)) #create the vector to add the Group groups to the NA matrix
DF_extra$Group <- vector #add in the Group column to the DF_extra dataframe
DF_extra <- DF_extra[,c(1, 13,2:12)] #rearrange the columns so that they are in the same order as the original DF
DF_extra <- setNames(DF_extra, names(ML_data_frame)) #set the names of the new df to match the original df
ML <- rbind(ML_data_frame, DF_extra) #Rbind the 2 dataframes so that we now have equal Group group sizes
print(ML %>% count(Group)) #check that the groups are now equal
#rearrange to be in order of Group, otherwise the dots get accidentally reassigned to the wrong group
ML <- ML[order(ML$Group), ]
```

## Maternal Liver Nonheme Iron

### All code is included for this first example, but thereafter, only the heading and graphs are shown. For all graphs, all data is graphed unless mentioned otherwise. Messages and warnings are excluded, since NA's were included to make all groups even, and I didn't want the code to print out these errors when they weren't necessary.

```{r, warning = FALSE, message = FALSE}
#Mean- calculate mean for column, repeat it to number of points, and create dataframe
Mean <- tapply(ML$Nonheme.Iron, as.character(ML$Group), mean, na.rm=TRUE) #make sure to change selected column to change data for graph
Mean <- as.data.frame(rep(Mean, each = NumPoints)) #repeat mean a set number of times
Mean$Group <- rep(ActualGroupOrder, each = NumPoints) #repeat Group a set number of times
colnames(Mean)[1] <- "Mean" #fix column name

#Stdev- calculate standard deviation for column, repeat it to number of points, and create dataframe
Stdev <- tapply(ML$Nonheme.Iron, as.character(ML$Group), sd, na.rm=TRUE) #make sure to change selected column
Stdev <- as.data.frame(rep(Stdev, each = NumPoints)) #repeat stdev a set number of times
Stdev$Group <- rep(ActualGroupOrder, each = NumPoints) #repeat Group a set number of times
colnames(Stdev)[1] <- "Stdev" #fix column name

#Combine mean, standard deviation, and individual data points
dataframe_combine <- cbind(Mean, Stdev, ML$Nonheme.Iron) #make sure to change selected column
colnames(dataframe_combine)[5] <- "Value" #Fix name of individual data point column
dataframe_combine <- dataframe_combine[-2] #Remove extra Group column

#Error bars
dataframe_combine$Upper <- dataframe_combine$Mean + dataframe_combine$Stdev #upper error
dataframe_combine$Lower <- dataframe_combine$Mean - dataframe_combine$Stdev #lower error

#Make Graph#
png("MaternalLiver_NonhemeIron_AllData_PAExFe_Dotplot.png", units="in", width=7, height=7, res=600) 

sets <- c("MD", "PAE", "MD-Iron", "PAE-Iron")

p<- ggplot(dataframe_combine, aes(x=Group, y=Mean)) + 
  geom_bar(stat="identity", color="black", aes(fill = Group),
           position=position_dodge()) +
  scale_fill_manual(values=c("MD" = "#0000CC",
                             "PAE" = "#6699FF",
                             "MD-Iron" = "#660066",
                             "PAE-Iron" = "#9900CC"
                             )) +
  geom_errorbar(aes(ymin=Lower, ymax=Upper), width=.2,
                position=position_dodge(.9)) + 
  geom_point(aes(x=Group, y=Value),
             size = 1.25, shape = 19, position = position_jitter(width=.15, height=0.1)) +
  scale_y_continuous(expand = c(0,0), limits = c(0,250)) +
  ggtitle("Maternal Liver Nonheme Iron") +
  ylab(expression("Nonheme Iron (µg Fe/g wet weight tissue)")) + 
  theme(plot.title = element_text(hjust = 0.5, size=18), 
        axis.title.x = element_blank(), #gets rid of x-axis label
        axis.title.y = element_text(size = 16),
        panel.grid.major = element_blank(), #gets rid of major gridlines
        panel.grid.minor = element_blank(), #gets rid of minor gridlines
        panel.background = element_blank(), #turns background white instead of gray
        axis.line = element_line(colour = "black"), 
        legend.position="none", #gets rid of legend
        axis.text=element_text(size=18, color = "black"), #sets size of x and y axis labels
        axis.text.x=element_text(angle = 45, vjust = .95, hjust = 0.9),
        axis.title=element_text(size=20,face="bold")) + 
  scale_x_discrete (limits = sets)
print(p)
dev.off() 
```
```{r Maternal Liver Nonheme Iron, echo = FALSE}
print(p)
```

## Maternal Liver Heme Iron
```{r, warning = FALSE, message = FALSE, echo = FALSE}
Mean <- tapply(ML$Heme.Iron, as.character(ML$Group), mean, na.rm=TRUE) #change
Mean <- as.data.frame(rep(Mean, each = NumPoints))
Mean$Group <- rep(ActualGroupOrder, each = NumPoints)
colnames(Mean)[1] <- "Mean" 

Stdev <- tapply(ML$Heme.Iron, as.character(ML$Group), sd, na.rm=TRUE) ##change
Stdev <- as.data.frame(rep(Stdev, each = NumPoints))
Stdev$Group <- rep(ActualGroupOrder, each = NumPoints)
colnames(Stdev)[1] <- "Stdev" 

dataframe_combine <- cbind(Mean, Stdev, ML$Heme.Iron) #change
colnames(dataframe_combine)[5] <- "Value" 
dataframe_combine <- dataframe_combine[-2] 

dataframe_combine$Upper <- dataframe_combine$Mean + dataframe_combine$Stdev 
dataframe_combine$Lower <- dataframe_combine$Mean - dataframe_combine$Stdev

#Make Graph#
png("MaternalLiver_HemeIron_AllData_PAExFe_Dotplot.png", units="in", width=7, height=7, res=600) 

sets <- c("MD", "PAE", "MD-Iron", "PAE-Iron")

p<- ggplot(dataframe_combine, aes(x=Group, y=Mean)) + 
  geom_bar(stat="identity", color="black", aes(fill = Group),
           position=position_dodge()) +
  scale_fill_manual(values=c("MD" = "#0000CC",
                             "PAE" = "#6699FF",
                             "MD-Iron" = "#660066",
                             "PAE-Iron" = "#9900CC"
                             )) +
  geom_errorbar(aes(ymin=Lower, ymax=Upper), width=.2,
                position=position_dodge(.9)) + 
  geom_point(aes(x=Group, y=Value),
             size = 1.25, shape = 19, position = position_jitter(width=.15, height=0.1)) +
  scale_y_continuous(expand = c(0,0), limits = c(-50,50)) +
  ggtitle("Maternal Liver Heme Iron") +
  ylab(expression("Heme Iron (µg Fe/g wet weight tissue)")) + 
  theme(plot.title = element_text(hjust = 0.5, size=18), 
        axis.title.x = element_blank(), #gets rid of x-axis label
        axis.title.y = element_text(size = 16),
        panel.grid.major = element_blank(), #gets rid of major gridlines
        panel.grid.minor = element_blank(), #gets rid of minor gridlines
        panel.background = element_blank(), #turns background white instead of gray
        axis.line = element_line(colour = "black"), 
        legend.position="none", #gets rid of legend
        axis.text=element_text(size=18, color = "black"), #sets size of x and y axis labels
        axis.text.x=element_text(angle = 45, vjust = .95, hjust = 0.9),
        axis.title=element_text(size=20,face="bold")) + 
  scale_x_discrete (limits = sets)
print(p)
dev.off() 
```
```{r Maternal Liver Heme Iron, echo = FALSE}
print(p)
```

# Fetal Liver
```{r Import FL file and rearrange by Group to be alphabetical}
FL_File <- "FetalLiver_NonhemeIron.csv"
FL_data <- read.csv(FL_File, header=TRUE) 
FL_data_frame <- data.frame(FL_data)
FL_data_frame <- FL_data_frame[order(FL_data_frame$Group), ]
```
```{r echo = FALSE}
head(FL_data_frame)
```
```{r}
ActualGroupOrder <- c("PAE-Iron", "PAE","MD-Iron", "MD")
```

```{r echo = FALSE}
#Figure out how many rows of empty NA's are needed to equalize the Group groups
Groupcount <- FL_data_frame %>% count(Group) #Calculate how many individual Females there are per Group group
NumPoints <- max(Groupcount$n) #Create the variable "NumPoints" to count the # of points in the final graphs
DiffFunc <- function(x) NumPoints - x #Create the function "DiffFunc" to calculate the number of NA rows to be added
DiffPoints <- as.data.frame(tapply(Groupcount$n, as.character(Groupcount$Group), DiffFunc)) #Calculate number of NA rows to be added to each Group group
DiffPoints$Group <- ActualGroupOrder #add new column so that the # of points to be added is assigned to the Group
colnames(DiffPoints)[1] <- "NumberN" #rename column
Nrow <- sum(DiffPoints$NumberN) #figure out how many total rows will be added to the DF_extra dataframe
AlcFe <- DiffPoints[1,1] #for each of these, it is creating a variable for the "vector" below
AlcH2O <- DiffPoints[2,1]
MDFe <- DiffPoints[3,1]
MDH2O <- DiffPoints[4,1]

#Add extra rows of NAs to equalize groups
DF_extra <- data.frame(matrix(NA, nrow = Nrow, ncol = 13)) #create an empty dataframe filled with NA's
vector <- rep(c("Alc+Fe", "Alc+H2O", "MD+Fe", "MD+H2O"), times = c(AlcFe, AlcH2O, MDFe, MDH2O)) #create the vector to add the Group groups to the NA matrix
DF_extra$Group <- vector #add in the Group column to the DF_extra dataframe
DF_extra <- DF_extra[,c(1, 14,2:13)] #rearrange the columns so that they are in the same order as the original DF
DF_extra <- setNames(DF_extra, names(FL_data_frame)) #set the names of the new df to match the original df
DF_extra$Sex <- c("F", "M", "F", "M") #Create correct sexes so it doesn't have to be done later
FL <- rbind(FL_data_frame, DF_extra) #Rbind the 2 dataframes so that we now have equal Group group sizes
print(FL %>% count(Group)) #check that the groups are now equal
#rearrange to be in order of Group, otherwise the dots get accidentally reassigned to the wrong group
FL <- FL[order(FL$Group), ]
```

## Fetal Liver Nonheme Iron

```{r, warning = FALSE, message = FALSE, echo = FALSE}
Mean <- tapply(FL$Nonheme.Iron, as.character(FL$Group), mean, na.rm=TRUE) #change
Mean <- as.data.frame(rep(Mean, each = NumPoints)) 
Mean$Group <- rep(ActualGroupOrder, each = NumPoints)
colnames(Mean)[1] <- "Mean"

Stdev <- tapply(FL$Nonheme.Iron, as.character(FL$Group), sd, na.rm=TRUE) #change
Stdev <- as.data.frame(rep(Stdev, each = NumPoints)) 
Stdev$Group <- rep(ActualGroupOrder, each = NumPoints) 
colnames(Stdev)[1] <- "Stdev" 

dataframe_combine <- cbind(Mean, Stdev, FL$Nonheme.Iron) #change
colnames(dataframe_combine)[5] <- "Value"
dataframe_combine <- dataframe_combine[-2] 

dataframe_combine$Upper <- dataframe_combine$Mean + dataframe_combine$Stdev
dataframe_combine$Lower <- dataframe_combine$Mean - dataframe_combine$Stdev

#Make Graph#
png("FetalLiver_NonhemeIron_AllData_PAExFe_Dotplot.png", units="in", width=7, height=7, res=600) 

sets <- c("MD", "PAE", "MD-Iron", "PAE-Iron")

p<- ggplot(dataframe_combine, aes(x=Group, y=Mean)) + 
  geom_bar(stat="identity", color="black", aes(fill = Group),
           position=position_dodge()) +
  scale_fill_manual(values=c("MD" = "#0000CC",
                             "PAE" = "#6699FF",
                             "MD-Iron" = "#660066",
                             "PAE-Iron" = "#9900CC"
                             )) +
  geom_errorbar(aes(ymin=Lower, ymax=Upper), width=.2,
                position=position_dodge(.9)) + 
  geom_point(aes(x=Group, y=Value),
             size = 1.25, shape = 19, position = position_jitter(width=.15, height=0.1)) +
  scale_y_continuous(expand = c(0,0), limits = c(0,250)) +
  ggtitle("Fetal Liver Nonheme Iron") +
  ylab(expression("Nonheme Iron (µg Fe/g wet weight tissue)")) + 
  theme(plot.title = element_text(hjust = 0.5, size=18), 
        axis.title.x = element_blank(), #gets rid of x-axis label
        axis.title.y = element_text(size = 16),
        panel.grid.major = element_blank(), #gets rid of major gridlines
        panel.grid.minor = element_blank(), #gets rid of minor gridlines
        panel.background = element_blank(), #turns background white instead of gray
        axis.line = element_line(colour = "black"), 
        legend.position="none", #gets rid of legend
        axis.text=element_text(size=18, color = "black"), #sets size of x and y axis labels
        axis.text.x=element_text(angle = 45, vjust = .95, hjust = 0.9),
        axis.title=element_text(size=20,face="bold")) + 
  scale_x_discrete (limits = sets)
print(p)
dev.off() 
```
```{r Fetal Liver Nonheme Iron, echo = FALSE}
print(p)
```

## Fetal Liver Heme Iron
```{r, warning = FALSE, message = FALSE, echo = FALSE}
Mean <- tapply(FL$Heme.Iron, as.character(FL$Group), mean, na.rm=TRUE) #change
Mean <- as.data.frame(rep(Mean, each = NumPoints))
Mean$Group <- rep(ActualGroupOrder, each = NumPoints)
colnames(Mean)[1] <- "Mean" 

Stdev <- tapply(FL$Heme.Iron, as.character(FL$Group), sd, na.rm=TRUE) ##change
Stdev <- as.data.frame(rep(Stdev, each = NumPoints))
Stdev$Group <- rep(ActualGroupOrder, each = NumPoints)
colnames(Stdev)[1] <- "Stdev" 

dataframe_combine <- cbind(Mean, Stdev, FL$Heme.Iron) #change
colnames(dataframe_combine)[5] <- "Value" 
dataframe_combine <- dataframe_combine[-2] 

dataframe_combine$Upper <- dataframe_combine$Mean + dataframe_combine$Stdev 
dataframe_combine$Lower <- dataframe_combine$Mean - dataframe_combine$Stdev

#Make Graph#
png("FetalLiver_HemeIron_AllData_PAExFe_Dotplot.png", units="in", width=7, height=7, res=600) 

sets <- c("MD", "PAE", "MD-Iron", "PAE-Iron")

p<- ggplot(dataframe_combine, aes(x=Group, y=Mean)) + 
  geom_bar(stat="identity", color="black", aes(fill = Group),
           position=position_dodge()) +
  scale_fill_manual(values=c("MD" = "#0000CC",
                             "PAE" = "#6699FF",
                             "MD-Iron" = "#660066",
                             "PAE-Iron" = "#9900CC"
                             )) +
  geom_errorbar(aes(ymin=Lower, ymax=Upper), width=.2,
                position=position_dodge(.9)) + 
  geom_point(aes(x=Group, y=Value),
             size = 1.25, shape = 19, position = position_jitter(width=.15, height=0.1)) +
  scale_y_continuous(expand = c(0,0), limits = c(-50,100)) +
  ggtitle("Fetal Liver Heme Iron") +
  ylab(expression("Heme Iron (µg Fe/g wet weight tissue)")) + 
  theme(plot.title = element_text(hjust = 0.5, size=18), 
        axis.title.x = element_blank(), #gets rid of x-axis label
        axis.title.y = element_text(size = 16),
        panel.grid.major = element_blank(), #gets rid of major gridlines
        panel.grid.minor = element_blank(), #gets rid of minor gridlines
        panel.background = element_blank(), #turns background white instead of gray
        axis.line = element_line(colour = "black"), 
        legend.position="none", #gets rid of legend
        axis.text=element_text(size=18, color = "black"), #sets size of x and y axis labels
        axis.text.x=element_text(angle = 45, vjust = .95, hjust = 0.9),
        axis.title=element_text(size=20,face="bold")) + 
  scale_x_discrete (limits = sets)
print(p)
dev.off() 
```
```{r Fetal Liver Heme Iron, echo = FALSE}
print(p)
```

## Create new tables for fetal sex
```{r}
Males <- FL[ which(FL$Sex=='M'), ]
Sex_NumPoints <- 9
Females <- FL[ which(FL$Sex=='F'), ]
```

## Male Fetal Liver
### Male Fetal Liver Nonheme Iron
```{r, warning = FALSE, message = FALSE, echo = FALSE}
#Mean
Mean <- tapply(Males$Nonheme.Iron, as.character(Males$Group), mean, na.rm=TRUE) #change
Mean <- as.data.frame(rep(Mean, each = Sex_NumPoints)) 
Mean$Group <- rep(ActualGroupOrder, each = Sex_NumPoints) 
colnames(Mean)[1] <- "Mean" 

#Stdev
Stdev <- tapply(Males$Nonheme.Iron, as.character(Males$Group), sd, na.rm=TRUE) #change
Stdev <- as.data.frame(rep(Stdev, each = Sex_NumPoints))
Stdev$Group <- rep(ActualGroupOrder, each = Sex_NumPoints)
colnames(Stdev)[1] <- "Stdev"

#Combine mean, standard deviation, and individual data points
dataframe_combine <- cbind(Mean, Stdev, Males$Nonheme.Iron) #change
colnames(dataframe_combine)[5] <- "Value"
dataframe_combine <- dataframe_combine[-2]

#Error bars
dataframe_combine$Upper <- dataframe_combine$Mean + dataframe_combine$Stdev
dataframe_combine$Lower <- dataframe_combine$Mean - dataframe_combine$Stdev 

#Make Graph#
png("FetalLiver_NonhemeIron_AllData_PAExFe_Dotplot_Males.png", units="in", width=7, height=7, res=600) 

sets <- c("MD", "PAE", "MD-Iron", "PAE-Iron")

p<- ggplot(dataframe_combine, aes(x=Group, y=Mean)) + 
  geom_bar(stat="identity", color="black", aes(fill = Group),
           position=position_dodge()) +
  scale_fill_manual(values=c("MD" = "#0000CC",
                             "PAE" = "#6699FF",
                             "MD-Iron" = "#660066",
                             "PAE-Iron" = "#9900CC"
                             )) +
  geom_errorbar(aes(ymin=Lower, ymax=Upper), width=.2,
                position=position_dodge(.9)) + 
  geom_point(aes(x=Group, y=Value),
             size = 1.25, shape = 19, position = position_jitter(width=.15, height=0.1)) +
  scale_y_continuous(expand = c(0,0), limits = c(0,250)) +
  ggtitle("Fetal Liver Nonheme Iron- Males") +
  ylab(expression("Nonheme iron (µg Fe/g wet weight tissue)")) + 
  theme(plot.title = element_text(hjust = 0.5, size=18), 
        axis.title.x = element_blank(), #gets rid of x-axis label
        axis.title.y = element_text(size = 16),
        panel.grid.major = element_blank(), #gets rid of major gridlines
        panel.grid.minor = element_blank(), #gets rid of minor gridlines
        panel.background = element_blank(), #turns background white instead of gray
        axis.line = element_line(colour = "black"), 
        legend.position="none", #gets rid of legend
        axis.text=element_text(size=18, color = "black"), #sets size of x and y axis labels
        axis.text.x=element_text(angle = 45, vjust = .95, hjust = 0.9),
        axis.title=element_text(size=20,face="bold")) + 
  scale_x_discrete (limits = sets)
print(p)
dev.off() 
```
```{r Fetal Liver Nonheme Iron- Male, echo = FALSE}
print(p)
```

### Male Fetal Liver Heme Iron
```{r, warning = FALSE, message = FALSE, echo = FALSE}
#Mean
Mean <- tapply(Males$Heme.Iron, as.character(Males$Group), mean, na.rm=TRUE) #change
Mean <- as.data.frame(rep(Mean, each = Sex_NumPoints)) 
Mean$Group <- rep(ActualGroupOrder, each = Sex_NumPoints) 
colnames(Mean)[1] <- "Mean" 

#Stdev
Stdev <- tapply(Males$Heme.Iron, as.character(Males$Group), sd, na.rm=TRUE) #change
Stdev <- as.data.frame(rep(Stdev, each = Sex_NumPoints))
Stdev$Group <- rep(ActualGroupOrder, each = Sex_NumPoints)
colnames(Stdev)[1] <- "Stdev"

#Combine mean, standard deviation, and individual data points
dataframe_combine <- cbind(Mean, Stdev, Males$Heme.Iron) #change
colnames(dataframe_combine)[5] <- "Value"
dataframe_combine <- dataframe_combine[-2]

#Error bars
dataframe_combine$Upper <- dataframe_combine$Mean + dataframe_combine$Stdev
dataframe_combine$Lower <- dataframe_combine$Mean - dataframe_combine$Stdev 

#Make Graph#
png("FetalLiver_HemeIron_AllData_PAExFe_Dotplot_Males.png", units="in", width=7, height=7, res=600) 

sets <- c("MD", "PAE", "MD-Iron", "PAE-Iron")

p<- ggplot(dataframe_combine, aes(x=Group, y=Mean)) + 
  geom_bar(stat="identity", color="black", aes(fill = Group),
           position=position_dodge()) +
  scale_fill_manual(values=c("MD" = "#0000CC",
                             "PAE" = "#6699FF",
                             "MD-Iron" = "#660066",
                             "PAE-Iron" = "#9900CC"
                             )) +
  geom_errorbar(aes(ymin=Lower, ymax=Upper), width=.2,
                position=position_dodge(.9)) + 
  geom_point(aes(x=Group, y=Value),
             size = 1.25, shape = 19, position = position_jitter(width=.15, height=0.1)) +
  scale_y_continuous(expand = c(0,0), limits = c(-50,100)) +
  ggtitle("Fetal Liver Heme Iron- Males") +
  ylab(expression("Heme iron (µg Fe/g wet weight tissue)")) + 
  theme(plot.title = element_text(hjust = 0.5, size=18), 
        axis.title.x = element_blank(), #gets rid of x-axis label
        axis.title.y = element_text(size = 16),
        panel.grid.major = element_blank(), #gets rid of major gridlines
        panel.grid.minor = element_blank(), #gets rid of minor gridlines
        panel.background = element_blank(), #turns background white instead of gray
        axis.line = element_line(colour = "black"), 
        legend.position="none", #gets rid of legend
        axis.text=element_text(size=18, color = "black"), #sets size of x and y axis labels
        axis.text.x=element_text(angle = 45, vjust = .95, hjust = 0.9),
        axis.title=element_text(size=20,face="bold")) + 
  scale_x_discrete (limits = sets)
print(p)
dev.off() 
```
```{r Fetal Liver Heme Iron- Male, echo = FALSE}
print(p)
```

## Female Fetal Liver
### Female Fetal Liver Nonheme Iron
```{r, warning = FALSE, message = FALSE, echo = FALSE}
#Mean
Mean <- tapply(Females$Nonheme.Iron, as.character(Females$Group), mean, na.rm=TRUE) #change
Mean <- as.data.frame(rep(Mean, each = Sex_NumPoints)) 
Mean$Group <- rep(ActualGroupOrder, each = Sex_NumPoints) 
colnames(Mean)[1] <- "Mean" 

#Stdev
Stdev <- tapply(Females$Nonheme.Iron, as.character(Females$Group), sd, na.rm=TRUE) #change
Stdev <- as.data.frame(rep(Stdev, each = Sex_NumPoints))
Stdev$Group <- rep(ActualGroupOrder, each = Sex_NumPoints)
colnames(Stdev)[1] <- "Stdev"

#Combine mean, standard deviation, and individual data points
dataframe_combine <- cbind(Mean, Stdev, Females$Nonheme.Iron) #change
colnames(dataframe_combine)[5] <- "Value"
dataframe_combine <- dataframe_combine[-2]

#Error bars
dataframe_combine$Upper <- dataframe_combine$Mean + dataframe_combine$Stdev
dataframe_combine$Lower <- dataframe_combine$Mean - dataframe_combine$Stdev 

#Make Graph#
png("FetalLiver_NonhemeIron_AllData_PAExFe_Dotplot_Females.png", units="in", width=7, height=7, res=600) 

sets <- c("MD", "PAE", "MD-Iron", "PAE-Iron")

p<- ggplot(dataframe_combine, aes(x=Group, y=Mean)) + 
  geom_bar(stat="identity", color="black", aes(fill = Group),
           position=position_dodge()) +
  scale_fill_manual(values=c("MD" = "#0000CC",
                             "PAE" = "#6699FF",
                             "MD-Iron" = "#660066",
                             "PAE-Iron" = "#9900CC"
                             )) +
  geom_errorbar(aes(ymin=Lower, ymax=Upper), width=.2,
                position=position_dodge(.9)) + 
  geom_point(aes(x=Group, y=Value),
             size = 1.25, shape = 19, position = position_jitter(width=.15, height=0.1)) +
  scale_y_continuous(expand = c(0,0), limits = c(0,250)) +
  ggtitle("Fetal Liver Nonheme Iron- Females") +
  ylab(expression("Nonheme iron (µg Fe/g wet weight tissue)")) + 
  theme(plot.title = element_text(hjust = 0.5, size=18), 
        axis.title.x = element_blank(), #gets rid of x-axis label
        axis.title.y = element_text(size = 16),
        panel.grid.major = element_blank(), #gets rid of major gridlines
        panel.grid.minor = element_blank(), #gets rid of minor gridlines
        panel.background = element_blank(), #turns background white instead of gray
        axis.line = element_line(colour = "black"), 
        legend.position="none", #gets rid of legend
        axis.text=element_text(size=18, color = "black"), #sets size of x and y axis labels
        axis.text.x=element_text(angle = 45, vjust = .95, hjust = 0.9),
        axis.title=element_text(size=20,face="bold")) + 
  scale_x_discrete (limits = sets)
print(p)
dev.off() 
```
```{r Fetal Liver Nonheme Iron- Female, echo = FALSE}
print(p)
```

### Female Fetal Liver Heme Iron
```{r, warning = FALSE, message = FALSE, echo = FALSE}
#Mean
Mean <- tapply(Females$Heme.Iron, as.character(Females$Group), mean, na.rm=TRUE) #change
Mean <- as.data.frame(rep(Mean, each = Sex_NumPoints)) 
Mean$Group <- rep(ActualGroupOrder, each = Sex_NumPoints) 
colnames(Mean)[1] <- "Mean" 

#Stdev
Stdev <- tapply(Females$Heme.Iron, as.character(Females$Group), sd, na.rm=TRUE) #change
Stdev <- as.data.frame(rep(Stdev, each = Sex_NumPoints))
Stdev$Group <- rep(ActualGroupOrder, each = Sex_NumPoints)
colnames(Stdev)[1] <- "Stdev"

#Combine mean, standard deviation, and individual data points
dataframe_combine <- cbind(Mean, Stdev, Females$Heme.Iron) #change
colnames(dataframe_combine)[5] <- "Value"
dataframe_combine <- dataframe_combine[-2]

#Error bars
dataframe_combine$Upper <- dataframe_combine$Mean + dataframe_combine$Stdev
dataframe_combine$Lower <- dataframe_combine$Mean - dataframe_combine$Stdev 

#Make Graph#
png("FetalLiver_HemeIron_AllData_PAExFe_Dotplot_Females.png", units="in", width=7, height=7, res=600) 

sets <- c("MD", "PAE", "MD-Iron", "PAE-Iron")

p<- ggplot(dataframe_combine, aes(x=Group, y=Mean)) + 
  geom_bar(stat="identity", color="black", aes(fill = Group),
           position=position_dodge()) +
  scale_fill_manual(values=c("MD" = "#0000CC",
                             "PAE" = "#6699FF",
                             "MD-Iron" = "#660066",
                             "PAE-Iron" = "#9900CC"
                             )) +
  geom_errorbar(aes(ymin=Lower, ymax=Upper), width=.2,
                position=position_dodge(.9)) + 
  geom_point(aes(x=Group, y=Value),
             size = 1.25, shape = 19, position = position_jitter(width=.15, height=0.1)) +
  scale_y_continuous(expand = c(0,0), limits = c(-50,100)) +
  ggtitle("Fetal Liver Heme Iron- Females") +
  ylab(expression("Heme iron (µg Fe/g wet weight tissue)")) + 
  theme(plot.title = element_text(hjust = 0.5, size=18), 
        axis.title.x = element_blank(), #gets rid of x-axis label
        axis.title.y = element_text(size = 16),
        panel.grid.major = element_blank(), #gets rid of major gridlines
        panel.grid.minor = element_blank(), #gets rid of minor gridlines
        panel.background = element_blank(), #turns background white instead of gray
        axis.line = element_line(colour = "black"), 
        legend.position="none", #gets rid of legend
        axis.text=element_text(size=18, color = "black"), #sets size of x and y axis labels
        axis.text.x=element_text(angle = 45, vjust = .95, hjust = 0.9),
        axis.title=element_text(size=20,face="bold")) + 
  scale_x_discrete (limits = sets)
print(p)
dev.off() 
```
```{r Fetal Liver Heme Iron- Female, echo = FALSE}
print(p)
```

# Fetal Brain
```{r Import FB file and rearrange by Group to be alphabetical}
FB_File <- "FetalBrain_NonhemeIron.csv"
FB_data <- read.csv(FB_File, header=TRUE) 
FB_data_frame <- data.frame(FB_data)
FB_data_frame <- FB_data_frame[order(FB_data_frame$Group), ]
```
```{r echo = FALSE}
head(FB_data_frame)
```
```{r}
ActualGroupOrder <- c("PAE-Iron", "PAE","MD-Iron", "MD")
```

```{r echo = FALSE}
#Figure out how many rows of empty NA's are needed to equalize the Group groups
Groupcount <- FB_data_frame %>% count(Group) #Calculate how many individual Females there are per Group group
NumPoints <- max(Groupcount$n) #Create the variable "NumPoints" to count the # of points in the final graphs
DiffFunc <- function(x) NumPoints - x #Create the function "DiffFunc" to calculate the number of NA rows to be added
DiffPoints <- as.data.frame(tapply(Groupcount$n, as.character(Groupcount$Group), DiffFunc)) #Calculate number of NA rows to be added to each Group group
DiffPoints$Group <- ActualGroupOrder #add new column so that the # of points to be added is assigned to the Group
colnames(DiffPoints)[1] <- "NumberN" #rename column
Nrow <- sum(DiffPoints$NumberN) #figure out how many total rows will be added to the DF_extra dataframe
AlcFe <- DiffPoints[1,1] #for each of these, it is creating a variable for the "vector" below
AlcH2O <- DiffPoints[2,1]
MDFe <- DiffPoints[3,1]
MDH2O <- DiffPoints[4,1]

#Add extra rows of NAs to equalize groups
DF_extra <- data.frame(matrix(NA, nrow = Nrow, ncol = 13)) #create an empty dataframe filled with NA's
vector <- rep(c("Alc+Fe", "Alc+H2O", "MD+Fe", "MD+H2O"), times = c(AlcFe, AlcH2O, MDFe, MDH2O)) #create the vector to add the Group groups to the NA matrix
DF_extra$Group <- vector #add in the Group column to the DF_extra dataframe
DF_extra <- DF_extra[,c(1, 14,2:13)] #rearrange the columns so that they are in the same order as the original DF
DF_extra <- setNames(DF_extra, names(FB_data_frame)) #set the names of the new df to match the original df
DF_extra$Sex <- c("F", "M", "F", "M") #Create correct sexes so it doesn't have to be done later
FB <- rbind(FB_data_frame, DF_extra) #Rbind the 2 dataframes so that we now have equal Group group sizes
print(FB %>% count(Group)) #check that the groups are now equal
#rearrange to be in order of Group, otherwise the dots get accidentally reassigned to the wrong group
FB <- FB[order(FB$Group), ]
```

## Fetal Brain Nonheme Iron
```{r, warning = FALSE, message = FALSE, echo = FALSE}
Mean <- tapply(FB$Nonheme.Iron, as.character(FB$Group), mean, na.rm=TRUE) #change
Mean <- as.data.frame(rep(Mean, each = NumPoints)) 
Mean$Group <- rep(ActualGroupOrder, each = NumPoints)
colnames(Mean)[1] <- "Mean"

Stdev <- tapply(FB$Nonheme.Iron, as.character(FB$Group), sd, na.rm=TRUE) #change
Stdev <- as.data.frame(rep(Stdev, each = NumPoints)) 
Stdev$Group <- rep(ActualGroupOrder, each = NumPoints) 
colnames(Stdev)[1] <- "Stdev" 

dataframe_combine <- cbind(Mean, Stdev, FB$Nonheme.Iron) #change
colnames(dataframe_combine)[5] <- "Value"
dataframe_combine <- dataframe_combine[-2] 

dataframe_combine$Upper <- dataframe_combine$Mean + dataframe_combine$Stdev
dataframe_combine$Lower <- dataframe_combine$Mean - dataframe_combine$Stdev

#Make Graph#
png("FetalBrain_NonhemeIron_AllData_PAExFe_Dotplot.png", units="in", width=7, height=7, res=600) 

sets <- c("MD", "PAE", "MD-Iron", "PAE-Iron")

p<- ggplot(dataframe_combine, aes(x=Group, y=Mean)) + 
  geom_bar(stat="identity", color="black", aes(fill = Group),
           position=position_dodge()) +
  scale_fill_manual(values=c("MD" = "#0000CC",
                             "PAE" = "#6699FF",
                             "MD-Iron" = "#660066",
                             "PAE-Iron" = "#9900CC"
                             )) +
  geom_errorbar(aes(ymin=Lower, ymax=Upper), width=.2,
                position=position_dodge(.9)) + 
  geom_point(aes(x=Group, y=Value),
             size = 1.25, shape = 19, position = position_jitter(width=.15, height=0.1)) +
  scale_y_continuous(expand = c(0,0), limits = c(0,25)) +
  ggtitle("Fetal Brain Nonheme Iron") +
  ylab(expression("Nonheme Iron (µg Fe/g wet weight tissue)")) + 
  theme(plot.title = element_text(hjust = 0.5, size=18), 
        axis.title.x = element_blank(), #gets rid of x-axis label
        axis.title.y = element_text(size = 16),
        panel.grid.major = element_blank(), #gets rid of major gridlines
        panel.grid.minor = element_blank(), #gets rid of minor gridlines
        panel.background = element_blank(), #turns background white instead of gray
        axis.line = element_line(colour = "black"), 
        legend.position="none", #gets rid of legend
        axis.text=element_text(size=18, color = "black"), #sets size of x and y axis labels
        axis.text.x=element_text(angle = 45, vjust = .95, hjust = 0.9),
        axis.title=element_text(size=20,face="bold")) + 
  scale_x_discrete (limits = sets)
print(p)
dev.off() 
```
```{r Fetal Brain Nonheme Iron, echo = FALSE}
print(p)
```

## Fetal Brain Heme Iron
```{r, warning = FALSE, message = FALSE, echo = FALSE}
Mean <- tapply(FB$Heme.Iron, as.character(FB$Group), mean, na.rm=TRUE) #change
Mean <- as.data.frame(rep(Mean, each = NumPoints))
Mean$Group <- rep(ActualGroupOrder, each = NumPoints)
colnames(Mean)[1] <- "Mean" 

Stdev <- tapply(FB$Heme.Iron, as.character(FB$Group), sd, na.rm=TRUE) ##change
Stdev <- as.data.frame(rep(Stdev, each = NumPoints))
Stdev$Group <- rep(ActualGroupOrder, each = NumPoints)
colnames(Stdev)[1] <- "Stdev" 

dataframe_combine <- cbind(Mean, Stdev, FB$Heme.Iron) #change
colnames(dataframe_combine)[5] <- "Value" 
dataframe_combine <- dataframe_combine[-2] 

dataframe_combine$Upper <- dataframe_combine$Mean + dataframe_combine$Stdev 
dataframe_combine$Lower <- dataframe_combine$Mean - dataframe_combine$Stdev

#Make Graph#
png("FetalBrain_HemeIron_AllData_PAExFe_Dotplot.png", units="in", width=7, height=7, res=600) 

sets <- c("MD", "PAE", "MD-Iron", "PAE-Iron")

p<- ggplot(dataframe_combine, aes(x=Group, y=Mean)) + 
  geom_bar(stat="identity", color="black", aes(fill = Group),
           position=position_dodge()) +
  scale_fill_manual(values=c("MD" = "#0000CC",
                             "PAE" = "#6699FF",
                             "MD-Iron" = "#660066",
                             "PAE-Iron" = "#9900CC"
                             )) +
  geom_errorbar(aes(ymin=Lower, ymax=Upper), width=.2,
                position=position_dodge(.9)) + 
  geom_point(aes(x=Group, y=Value),
             size = 1.25, shape = 19, position = position_jitter(width=.15, height=0.1)) +
  scale_y_continuous(expand = c(0,0), limits = c(-5,11)) +
  ggtitle("Fetal Brain Heme Iron") +
  ylab(expression("Heme Iron (µg Fe/g wet weight tissue)")) + 
  theme(plot.title = element_text(hjust = 0.5, size=18), 
        axis.title.x = element_blank(), #gets rid of x-axis label
        axis.title.y = element_text(size = 16),
        panel.grid.major = element_blank(), #gets rid of major gridlines
        panel.grid.minor = element_blank(), #gets rid of minor gridlines
        panel.background = element_blank(), #turns background white instead of gray
        axis.line = element_line(colour = "black"), 
        legend.position="none", #gets rid of legend
        axis.text=element_text(size=18, color = "black"), #sets size of x and y axis labels
        axis.text.x=element_text(angle = 45, vjust = .95, hjust = 0.9),
        axis.title=element_text(size=20,face="bold")) + 
  scale_x_discrete (limits = sets)
print(p)
dev.off() 
```
```{r Fetal Brain Heme Iron, echo = FALSE}
print(p)
```

## Create new tables for fetal sex
```{r}
Males <- FB[ which(FB$Sex=='M'), ]
Sex_NumPoints <- 9
Females <- FB[ which(FB$Sex=='F'), ]
```

## Male Fetal Brain
### Male Fetal Brain Nonheme Iron
```{r, warning = FALSE, message = FALSE, echo = FALSE}
#Mean
Mean <- tapply(Males$Nonheme.Iron, as.character(Males$Group), mean, na.rm=TRUE) #change
Mean <- as.data.frame(rep(Mean, each = Sex_NumPoints)) 
Mean$Group <- rep(ActualGroupOrder, each = Sex_NumPoints) 
colnames(Mean)[1] <- "Mean" 

#Stdev
Stdev <- tapply(Males$Nonheme.Iron, as.character(Males$Group), sd, na.rm=TRUE) #change
Stdev <- as.data.frame(rep(Stdev, each = Sex_NumPoints))
Stdev$Group <- rep(ActualGroupOrder, each = Sex_NumPoints)
colnames(Stdev)[1] <- "Stdev"

#Combine mean, standard deviation, and individual data points
dataframe_combine <- cbind(Mean, Stdev, Males$Nonheme.Iron) #change
colnames(dataframe_combine)[5] <- "Value"
dataframe_combine <- dataframe_combine[-2]

#Error bars
dataframe_combine$Upper <- dataframe_combine$Mean + dataframe_combine$Stdev
dataframe_combine$Lower <- dataframe_combine$Mean - dataframe_combine$Stdev 

#Make Graph#
png("FetalBrain_NonhemeIron_AllData_PAExFe_Dotplot_Males.png", units="in", width=7, height=7, res=600) 

sets <- c("MD", "PAE", "MD-Iron", "PAE-Iron")

p<- ggplot(dataframe_combine, aes(x=Group, y=Mean)) + 
  geom_bar(stat="identity", color="black", aes(fill = Group),
           position=position_dodge()) +
  scale_fill_manual(values=c("MD" = "#0000CC",
                             "PAE" = "#6699FF",
                             "MD-Iron" = "#660066",
                             "PAE-Iron" = "#9900CC"
                             )) +
  geom_errorbar(aes(ymin=Lower, ymax=Upper), width=.2,
                position=position_dodge(.9)) + 
  geom_point(aes(x=Group, y=Value),
             size = 1.25, shape = 19, position = position_jitter(width=.15, height=0.1)) +
  scale_y_continuous(expand = c(0,0), limits = c(0,25)) +
  ggtitle("Fetal Brain Nonheme Iron- Males") +
  ylab(expression("Nonheme iron (µg Fe/g wet weight tissue)")) + 
  theme(plot.title = element_text(hjust = 0.5, size=18), 
        axis.title.x = element_blank(), #gets rid of x-axis label
        axis.title.y = element_text(size = 16),
        panel.grid.major = element_blank(), #gets rid of major gridlines
        panel.grid.minor = element_blank(), #gets rid of minor gridlines
        panel.background = element_blank(), #turns background white instead of gray
        axis.line = element_line(colour = "black"), 
        legend.position="none", #gets rid of legend
        axis.text=element_text(size=18, color = "black"), #sets size of x and y axis labels
        axis.text.x=element_text(angle = 45, vjust = .95, hjust = 0.9),
        axis.title=element_text(size=20,face="bold")) + 
  scale_x_discrete (limits = sets)
print(p)
dev.off() 
```
```{r Fetal Brain Nonheme Iron- Male, echo = FALSE}
print(p)
```

### Male Fetal Brain Heme Iron
```{r, warning = FALSE, message = FALSE, echo = FALSE}
#Mean
Mean <- tapply(Males$Heme.Iron, as.character(Males$Group), mean, na.rm=TRUE) #change
Mean <- as.data.frame(rep(Mean, each = Sex_NumPoints)) 
Mean$Group <- rep(ActualGroupOrder, each = Sex_NumPoints) 
colnames(Mean)[1] <- "Mean" 

#Stdev
Stdev <- tapply(Males$Heme.Iron, as.character(Males$Group), sd, na.rm=TRUE) #change
Stdev <- as.data.frame(rep(Stdev, each = Sex_NumPoints))
Stdev$Group <- rep(ActualGroupOrder, each = Sex_NumPoints)
colnames(Stdev)[1] <- "Stdev"

#Combine mean, standard deviation, and individual data points
dataframe_combine <- cbind(Mean, Stdev, Males$Heme.Iron) #change
colnames(dataframe_combine)[5] <- "Value"
dataframe_combine <- dataframe_combine[-2]

#Error bars
dataframe_combine$Upper <- dataframe_combine$Mean + dataframe_combine$Stdev
dataframe_combine$Lower <- dataframe_combine$Mean - dataframe_combine$Stdev 

#Make Graph#
png("FetalBrain_HemeIron_AllData_PAExFe_Dotplot_Males.png", units="in", width=7, height=7, res=600) 

sets <- c("MD", "PAE", "MD-Iron", "PAE-Iron")

p<- ggplot(dataframe_combine, aes(x=Group, y=Mean)) + 
  geom_bar(stat="identity", color="black", aes(fill = Group),
           position=position_dodge()) +
  scale_fill_manual(values=c("MD" = "#0000CC",
                             "PAE" = "#6699FF",
                             "MD-Iron" = "#660066",
                             "PAE-Iron" = "#9900CC"
                             )) +
  geom_errorbar(aes(ymin=Lower, ymax=Upper), width=.2,
                position=position_dodge(.9)) + 
  geom_point(aes(x=Group, y=Value),
             size = 1.25, shape = 19, position = position_jitter(width=.15, height=0.1)) +
  scale_y_continuous(expand = c(0,0), limits = c(-5,11)) +
  ggtitle("Fetal Brain Heme Iron- Males") +
  ylab(expression("Heme iron (µg Fe/g wet weight tissue)")) + 
  theme(plot.title = element_text(hjust = 0.5, size=18), 
        axis.title.x = element_blank(), #gets rid of x-axis label
        axis.title.y = element_text(size = 16),
        panel.grid.major = element_blank(), #gets rid of major gridlines
        panel.grid.minor = element_blank(), #gets rid of minor gridlines
        panel.background = element_blank(), #turns background white instead of gray
        axis.line = element_line(colour = "black"), 
        legend.position="none", #gets rid of legend
        axis.text=element_text(size=18, color = "black"), #sets size of x and y axis labels
        axis.text.x=element_text(angle = 45, vjust = .95, hjust = 0.9),
        axis.title=element_text(size=20,face="bold")) + 
  scale_x_discrete (limits = sets)
print(p)
dev.off() 
```
```{r Fetal Brain Heme Iron- Male, echo = FALSE}
print(p)
```

## Female Fetal Brain
### Female Fetal Brain Nonheme Iron
```{r, warning = FALSE, message = FALSE, echo = FALSE}
#Mean
Mean <- tapply(Females$Nonheme.Iron, as.character(Females$Group), mean, na.rm=TRUE) #change
Mean <- as.data.frame(rep(Mean, each = Sex_NumPoints)) 
Mean$Group <- rep(ActualGroupOrder, each = Sex_NumPoints) 
colnames(Mean)[1] <- "Mean" 

#Stdev
Stdev <- tapply(Females$Nonheme.Iron, as.character(Females$Group), sd, na.rm=TRUE) #change
Stdev <- as.data.frame(rep(Stdev, each = Sex_NumPoints))
Stdev$Group <- rep(ActualGroupOrder, each = Sex_NumPoints)
colnames(Stdev)[1] <- "Stdev"

#Combine mean, standard deviation, and individual data points
dataframe_combine <- cbind(Mean, Stdev, Females$Nonheme.Iron) #change
colnames(dataframe_combine)[5] <- "Value"
dataframe_combine <- dataframe_combine[-2]

#Error bars
dataframe_combine$Upper <- dataframe_combine$Mean + dataframe_combine$Stdev
dataframe_combine$Lower <- dataframe_combine$Mean - dataframe_combine$Stdev 

#Make Graph#
png("FetalBrain_NonhemeIron_AllData_PAExFe_Dotplot_Females.png", units="in", width=7, height=7, res=600) 

sets <- c("MD", "PAE", "MD-Iron", "PAE-Iron")

p<- ggplot(dataframe_combine, aes(x=Group, y=Mean)) + 
  geom_bar(stat="identity", color="black", aes(fill = Group),
           position=position_dodge()) +
  scale_fill_manual(values=c("MD" = "#0000CC",
                             "PAE" = "#6699FF",
                             "MD-Iron" = "#660066",
                             "PAE-Iron" = "#9900CC"
                             )) +
  geom_errorbar(aes(ymin=Lower, ymax=Upper), width=.2,
                position=position_dodge(.9)) + 
  geom_point(aes(x=Group, y=Value),
             size = 1.25, shape = 19, position = position_jitter(width=.15, height=0.1)) +
  scale_y_continuous(expand = c(0,0), limits = c(0,25)) +
  ggtitle("Fetal Brain Nonheme Iron- Females") +
  ylab(expression("Nonheme iron (µg Fe/g wet weight tissue)")) + 
  theme(plot.title = element_text(hjust = 0.5, size=18), 
        axis.title.x = element_blank(), #gets rid of x-axis label
        axis.title.y = element_text(size = 16),
        panel.grid.major = element_blank(), #gets rid of major gridlines
        panel.grid.minor = element_blank(), #gets rid of minor gridlines
        panel.background = element_blank(), #turns background white instead of gray
        axis.line = element_line(colour = "black"), 
        legend.position="none", #gets rid of legend
        axis.text=element_text(size=18, color = "black"), #sets size of x and y axis labels
        axis.text.x=element_text(angle = 45, vjust = .95, hjust = 0.9),
        axis.title=element_text(size=20,face="bold")) + 
  scale_x_discrete (limits = sets)
print(p)
dev.off() 
```
```{r Fetal Brain Nonheme Iron- Female, echo = FALSE}
print(p)
```

### Female Fetal Brain Heme Iron
```{r, warning = FALSE, message = FALSE, echo = FALSE}
#Mean
Mean <- tapply(Females$Heme.Iron, as.character(Females$Group), mean, na.rm=TRUE) #change
Mean <- as.data.frame(rep(Mean, each = Sex_NumPoints)) 
Mean$Group <- rep(ActualGroupOrder, each = Sex_NumPoints) 
colnames(Mean)[1] <- "Mean" 

#Stdev
Stdev <- tapply(Females$Heme.Iron, as.character(Females$Group), sd, na.rm=TRUE) #change
Stdev <- as.data.frame(rep(Stdev, each = Sex_NumPoints))
Stdev$Group <- rep(ActualGroupOrder, each = Sex_NumPoints)
colnames(Stdev)[1] <- "Stdev"

#Combine mean, standard deviation, and individual data points
dataframe_combine <- cbind(Mean, Stdev, Females$Heme.Iron) #change
colnames(dataframe_combine)[5] <- "Value"
dataframe_combine <- dataframe_combine[-2]

#Error bars
dataframe_combine$Upper <- dataframe_combine$Mean + dataframe_combine$Stdev
dataframe_combine$Lower <- dataframe_combine$Mean - dataframe_combine$Stdev 

#Make Graph#
png("FetalBrain_HemeIron_AllData_PAExFe_Dotplot_Females.png", units="in", width=7, height=7, res=600) 

sets <- c("MD", "PAE", "MD-Iron", "PAE-Iron")

p<- ggplot(dataframe_combine, aes(x=Group, y=Mean)) + 
  geom_bar(stat="identity", color="black", aes(fill = Group),
           position=position_dodge()) +
  scale_fill_manual(values=c("MD" = "#0000CC",
                             "PAE" = "#6699FF",
                             "MD-Iron" = "#660066",
                             "PAE-Iron" = "#9900CC"
                             )) +
  geom_errorbar(aes(ymin=Lower, ymax=Upper), width=.2,
                position=position_dodge(.9)) + 
  geom_point(aes(x=Group, y=Value),
             size = 1.25, shape = 19, position = position_jitter(width=.15, height=0.1)) +
  scale_y_continuous(expand = c(0,0), limits = c(-5,11)) +
  ggtitle("Fetal Brain Heme Iron- Females") +
  ylab(expression("Heme iron (µg Fe/g wet weight tissue)")) + 
  theme(plot.title = element_text(hjust = 0.5, size=18), 
        axis.title.x = element_blank(), #gets rid of x-axis label
        axis.title.y = element_text(size = 16),
        panel.grid.major = element_blank(), #gets rid of major gridlines
        panel.grid.minor = element_blank(), #gets rid of minor gridlines
        panel.background = element_blank(), #turns background white instead of gray
        axis.line = element_line(colour = "black"), 
        legend.position="none", #gets rid of legend
        axis.text=element_text(size=18, color = "black"), #sets size of x and y axis labels
        axis.text.x=element_text(angle = 45, vjust = .95, hjust = 0.9),
        axis.title=element_text(size=20,face="bold")) + 
  scale_x_discrete (limits = sets)
print(p)
dev.off() 
```
```{r Fetal Brain Heme Iron- Female, echo = FALSE}
print(p)
```

# Session Information
```{r, echo = FALSE}
session_info <- devtools::session_info()
print(session_info)
```