---
title: "Maternal Rat Gestational Weight Gain, AIN-76A diet with MD or Alcohol and Iron Supplement or Water, with Some Data Removed for Litter Size"
author: "Kaylee Helfrich"
date: "8/20/20-10/26/20"
output: 
  pdf_document: default
  html_document: default
data: "GestationalWeightGain_RmData2.csv"
---

Built with R `r getRversion()`

```{r RMarkdown setup, include = FALSE, message = FALSE}
require(knitr)
knitr::opts_chunk$set(echo = TRUE, tidy.opts=list(width.cutoff=60), tidy=TRUE)
knitr::opts_knit$set(root.dir = "~/KayleeStuff/Smith_Lab/Data/Rat_Iron/Maternal_Anthro/WeightGain")
options(tinytex.verbose = TRUE)
```

# Graphing Maternal Rat Prenatal Weight Gain
This document details my graphing of the weight gain from maternal rats. This includes bar and line graphs for various measures of weight gain. This analysis uses data that was collected, excluding samples from dams with litters that were 10 fetuses +/- 2SDs from the mean (including R029, R031 and nonpregnant dams). Long-Evans rats arrived at 7 weeks old and were mated at 9-11 weeks of age. The rats were dosed with 5g/kg ethanol or isocaloric maltodextrin from GD17.5-19.5. The dams also received either an iron supplement (6g/kg, Fer-In-Sol) or the same volume of water as a gavage from GD12.5-GD19.5. All dams consumed AIN-76G diet modified to contain 100ppm of iron from arrival through pregnancy. Tissues were harvested on GD20.5. All graphs are mean with standard deviation, since there are not multiple measures per sample. This analysis will allow us to compare the 4 groups. Statistical analysis in JMP will use ANOVA, following checks for normality and variance, to assign significance to the measures. 

```{r include = FALSE}
rm(list=ls())
setwd("~/KayleeStuff/Smith_Lab/Data/Rat_Iron/Maternal_Anthro/WeightGain")
library(ggplot2)
library(plotrix)
library(dplyr)
library(nlme)
```

```{r Import file and rearrange by treatment to be alphabetical}
File <- "GestationalWeightGain_RmData2.csv"
data <- read.csv(File, header=TRUE) 
data_frame <- data.frame(data)
data_frame <- data_frame[order(data_frame$Treatment), ]
```
```{r echo = FALSE}
print(data_frame)
```
```{r Prepare data for graphing}
ActualGroupOrder <- c("PAE-Iron", "PAE","MD-Iron", "MD")
data_frame<-subset(data_frame, Pregnant.!="No") #remove all nonpregnant dams from dataset
```

```{r Standard Error Function}
standard_error <- function(x) sd(x) / sqrt(length(x))
```

# Pregnant growth from GD0.5-GD20.5 by treatment group (with standard deviation)
Data is graphed by treatment, with shaded error bars
```{r}
#Weight at GD0.5
GD0.5 <- as.data.frame(tapply(data_frame$GD0.5, as.character(data_frame$Treatment), mean, na.rm=TRUE))
GD0.5$Treatment <- ActualGroupOrder
colnames(GD0.5)[1] <- "Mean" #fix column name
GD0.5$Stdev <- tapply(data_frame$GD0.5, as.character(data_frame$Treatment), sd, na.rm=TRUE)
GD0.5$Day <- rep("0.5", 4)

#Weight at GD3.5
GD3.5 <- as.data.frame(tapply(data_frame$GD3.5, as.character(data_frame$Treatment), mean, na.rm=TRUE))
GD3.5$Treatment <- ActualGroupOrder
colnames(GD3.5)[1] <- "Mean" #fix column name
GD3.5$Stdev <- tapply(data_frame$GD3.5, as.character(data_frame$Treatment), sd, na.rm=TRUE)
GD3.5$Day <- rep("03.5", 4)

#Weight at GD5.5
GD5.5 <- as.data.frame(tapply(data_frame$GD5.5, as.character(data_frame$Treatment), mean, na.rm=TRUE))
GD5.5$Treatment <- ActualGroupOrder
colnames(GD5.5)[1] <- "Mean" #fix column name
GD5.5$Stdev <- tapply(data_frame$GD5.5, as.character(data_frame$Treatment), sd, na.rm=TRUE)
GD5.5$Day <- rep("05.5", 4)

#Weight at GD8.5
GD8.5 <- as.data.frame(tapply(data_frame$GD8.5, as.character(data_frame$Treatment), mean, na.rm=TRUE))
GD8.5$Treatment <- ActualGroupOrder
colnames(GD8.5)[1] <- "Mean" #fix column name
GD8.5$Stdev <- tapply(data_frame$GD8.5, as.character(data_frame$Treatment), sd, na.rm=TRUE)
GD8.5$Day <- rep("08.5", 4)

#Weight at GD11.5
GD11.5 <- as.data.frame(tapply(data_frame$GD11.5, as.character(data_frame$Treatment), mean, na.rm=TRUE))
GD11.5$Treatment <- ActualGroupOrder
colnames(GD11.5)[1] <- "Mean" #fix column name
GD11.5$Stdev <- tapply(data_frame$GD11.5, as.character(data_frame$Treatment), sd, na.rm=TRUE)
GD11.5$Day <- rep("11.5", 4)

#Weight at GD12.5
GD12.5 <- as.data.frame(tapply(data_frame$GD12.5, as.character(data_frame$Treatment), mean, na.rm=TRUE))
GD12.5$Treatment <- ActualGroupOrder
colnames(GD12.5)[1] <- "Mean" #fix column name
GD12.5$Stdev <- tapply(data_frame$GD12.5, as.character(data_frame$Treatment), sd, na.rm=TRUE)
GD12.5$Day <- rep("12.5", 4)

#Weight at GD13.5
GD13.5 <- as.data.frame(tapply(data_frame$GD13.5, as.character(data_frame$Treatment), mean, na.rm=TRUE))
GD13.5$Treatment <- ActualGroupOrder
colnames(GD13.5)[1] <- "Mean" #fix column name
GD13.5$Stdev <- tapply(data_frame$GD13.5, as.character(data_frame$Treatment), sd, na.rm=TRUE)
GD13.5$Day <- rep("13.5", 4)

#Weight at GD14.5
GD14.5 <- as.data.frame(tapply(data_frame$GD14.5, as.character(data_frame$Treatment), mean, na.rm=TRUE))
GD14.5$Treatment <- ActualGroupOrder
colnames(GD14.5)[1] <- "Mean" #fix column name
GD14.5$Stdev <- tapply(data_frame$GD14.5, as.character(data_frame$Treatment), sd, na.rm=TRUE)
GD14.5$Day <- rep("14.5", 4)

#Weight at GD15.5
GD15.5 <- as.data.frame(tapply(data_frame$GD15.5, as.character(data_frame$Treatment), mean, na.rm=TRUE))
GD15.5$Treatment <- ActualGroupOrder
colnames(GD15.5)[1] <- "Mean" #fix column name
GD15.5$Stdev <- tapply(data_frame$GD15.5, as.character(data_frame$Treatment), sd, na.rm=TRUE)
GD15.5$Day <- rep("15.5", 4)

#Weight at GD16.5
GD16.5 <- as.data.frame(tapply(data_frame$GD16.5, as.character(data_frame$Treatment), mean, na.rm=TRUE))
GD16.5$Treatment <- ActualGroupOrder
colnames(GD16.5)[1] <- "Mean" #fix column name
GD16.5$Stdev <- tapply(data_frame$GD16.5, as.character(data_frame$Treatment), sd, na.rm=TRUE)
GD16.5$Day <- rep("16.5", 4)

#Weight at GD17.5
GD17.5 <- as.data.frame(tapply(data_frame$GD17.5, as.character(data_frame$Treatment), mean, na.rm=TRUE))
GD17.5$Treatment <- ActualGroupOrder
colnames(GD17.5)[1] <- "Mean" #fix column name
GD17.5$Stdev <- tapply(data_frame$GD17.5, as.character(data_frame$Treatment), sd, na.rm=TRUE)
GD17.5$Day <- rep("17.5", 4)

#Weight at GD18.5
GD18.5 <- as.data.frame(tapply(data_frame$GD18.5, as.character(data_frame$Treatment), mean, na.rm=TRUE))
GD18.5$Treatment <- ActualGroupOrder
colnames(GD18.5)[1] <- "Mean" #fix column name
GD18.5$Stdev <- tapply(data_frame$GD18.5, as.character(data_frame$Treatment), sd, na.rm=TRUE)
GD18.5$Day <- rep("18.5", 4)

#Weight at GD19.5
GD19.5 <- as.data.frame(tapply(data_frame$GD19.5, as.character(data_frame$Treatment), mean, na.rm=TRUE))
GD19.5$Treatment <- ActualGroupOrder
colnames(GD19.5)[1] <- "Mean" #fix column name
GD19.5$Stdev <- tapply(data_frame$GD19.5, as.character(data_frame$Treatment), sd, na.rm=TRUE)
GD19.5$Day <- rep("19.5", 4)

#Weight at GD20.5
GD20.5 <- as.data.frame(tapply(data_frame$GD20.5, as.character(data_frame$Treatment), mean, na.rm=TRUE))
GD20.5$Treatment <- ActualGroupOrder
colnames(GD20.5)[1] <- "Mean" #fix column name
GD20.5$Stdev <- tapply(data_frame$GD20.5, as.character(data_frame$Treatment), sd, na.rm=TRUE)
GD20.5$Day <- rep("20.5", 4)
```
```{r Merge all weight tables}
#Merge all tables
Weight_Combined <- rbind(GD0.5, GD3.5, GD5.5, GD8.5, GD11.5, GD12.5, GD13.5, GD14.5, GD15.5, GD16.5, 
                                  GD17.5, GD18.5, GD19.5, GD20.5)
Weight_Combined <- Weight_Combined[ ,c(2,1,3,4)]
Weight_Combined$Day <- as.numeric(as.vector(Weight_Combined$Day)) #convert "Age" to a numeric variable so the x-axis adjusts accordingly
Weight_Combined$Upper <- Weight_Combined$Mean + Weight_Combined$Stdev
Weight_Combined$Lower <- Weight_Combined$Mean - Weight_Combined$Stdev
```

## Graph Weight Gain of Pregnant Dams, Separated by Exposure Group
```{r}
png("MaternalWeightGain_SDErrorShading_RmData2_PAExFe_LineGraph.png", units="in", width=10, height=7, res=600)

WG_bygroup <- ggplot(Weight_Combined, aes(x = Day, y = Mean, group = Treatment, color = Treatment) ) +
     geom_point() +
     geom_ribbon(aes(ymin=Lower, ymax=Upper, fill = Treatment), alpha = 0.15) +
     geom_line(aes(y = Mean)) +
  scale_y_continuous(limits = c(200,370)) + 
  ggtitle("Maternal Prenatal Weight Gain by Exposure Group") +
  ylab(expression("Weight (g)")) + 
  xlab(expression("Gestational Day")) +
  theme(plot.title = element_text(hjust = 0.5, size=18), 
        axis.title.y = element_text(size = 16),
        axis.title.x = element_text(size = 16),
        panel.grid.major = element_blank(), #gets rid of major gridlines
        panel.grid.minor = element_blank(), #gets rid of minor gridlines
        panel.background = element_blank(), #turns background white instead of gray
        axis.line = element_line(colour = "black"), 
        axis.text=element_text(size=18, color = "black"), #sets size of x and y axis labels
        axis.text.x=element_text(vjust = .95, hjust = 0.9),
        axis.title=element_text(size=20,face="bold"))
print(WG_bygroup)
dev.off()
```
```{r Maternal Prenatal Weight Gain with Standard Deviation Error Shading, echo = FALSE, warning = FALSE, message = FALSE}
print(WG_bygroup)
```

# Pregnant growth from GD0.5-GD20.5 by treatment group (with standard error)
Data is graphed by treatment, with shaded error bars
```{r}
#Weight at GD0.5
GD0.5 <- as.data.frame(tapply(data_frame$GD0.5, as.character(data_frame$Treatment), mean, na.rm=TRUE))
GD0.5$Treatment <- ActualGroupOrder
colnames(GD0.5)[1] <- "Mean" #fix column name
GD0.5$SE <- tapply(data_frame$GD0.5, as.character(data_frame$Treatment), standard_error)
GD0.5$Day <- rep("0.5", 4)

#Weight at GD3.5
GD3.5 <- as.data.frame(tapply(data_frame$GD3.5, as.character(data_frame$Treatment), mean, na.rm=TRUE))
GD3.5$Treatment <- ActualGroupOrder
colnames(GD3.5)[1] <- "Mean" #fix column name
GD3.5$SE <- tapply(data_frame$GD3.5, as.character(data_frame$Treatment), standard_error)
GD3.5$Day <- rep("03.5", 4)

#Weight at GD5.5
GD5.5 <- as.data.frame(tapply(data_frame$GD5.5, as.character(data_frame$Treatment), mean, na.rm=TRUE))
GD5.5$Treatment <- ActualGroupOrder
colnames(GD5.5)[1] <- "Mean" #fix column name
GD5.5$SE <- tapply(data_frame$GD5.5, as.character(data_frame$Treatment), standard_error)
GD5.5$Day <- rep("05.5", 4)

#Weight at GD8.5
GD8.5 <- as.data.frame(tapply(data_frame$GD8.5, as.character(data_frame$Treatment), mean, na.rm=TRUE))
GD8.5$Treatment <- ActualGroupOrder
colnames(GD8.5)[1] <- "Mean" #fix column name
GD8.5$SE <- tapply(data_frame$GD8.5, as.character(data_frame$Treatment), standard_error)
GD8.5$Day <- rep("08.5", 4)

#Weight at GD11.5
GD11.5 <- as.data.frame(tapply(data_frame$GD11.5, as.character(data_frame$Treatment), mean, na.rm=TRUE))
GD11.5$Treatment <- ActualGroupOrder
colnames(GD11.5)[1] <- "Mean" #fix column name
GD11.5$SE <- tapply(data_frame$GD11.5, as.character(data_frame$Treatment), standard_error)
GD11.5$Day <- rep("11.5", 4)

#Weight at GD12.5
GD12.5 <- as.data.frame(tapply(data_frame$GD12.5, as.character(data_frame$Treatment), mean, na.rm=TRUE))
GD12.5$Treatment <- ActualGroupOrder
colnames(GD12.5)[1] <- "Mean" #fix column name
GD12.5$SE <- tapply(data_frame$GD12.5, as.character(data_frame$Treatment), standard_error)
GD12.5$Day <- rep("12.5", 4)

#Weight at GD13.5
GD13.5 <- as.data.frame(tapply(data_frame$GD13.5, as.character(data_frame$Treatment), mean, na.rm=TRUE))
GD13.5$Treatment <- ActualGroupOrder
colnames(GD13.5)[1] <- "Mean" #fix column name
GD13.5$SE <- tapply(data_frame$GD13.5, as.character(data_frame$Treatment), standard_error)
GD13.5$Day <- rep("13.5", 4)

#Weight at GD14.5
GD14.5 <- as.data.frame(tapply(data_frame$GD14.5, as.character(data_frame$Treatment), mean, na.rm=TRUE))
GD14.5$Treatment <- ActualGroupOrder
colnames(GD14.5)[1] <- "Mean" #fix column name
GD14.5$SE <- tapply(data_frame$GD14.5, as.character(data_frame$Treatment), standard_error)
GD14.5$Day <- rep("14.5", 4)

#Weight at GD15.5
GD15.5 <- as.data.frame(tapply(data_frame$GD15.5, as.character(data_frame$Treatment), mean, na.rm=TRUE))
GD15.5$Treatment <- ActualGroupOrder
colnames(GD15.5)[1] <- "Mean" #fix column name
GD15.5$SE <- tapply(data_frame$GD15.5, as.character(data_frame$Treatment), standard_error)
GD15.5$Day <- rep("15.5", 4)

#Weight at GD16.5
GD16.5 <- as.data.frame(tapply(data_frame$GD16.5, as.character(data_frame$Treatment), mean, na.rm=TRUE))
GD16.5$Treatment <- ActualGroupOrder
colnames(GD16.5)[1] <- "Mean" #fix column name
GD16.5$SE <- tapply(data_frame$GD16.5, as.character(data_frame$Treatment), standard_error)
GD16.5$Day <- rep("16.5", 4)

#Weight at GD17.5
GD17.5 <- as.data.frame(tapply(data_frame$GD17.5, as.character(data_frame$Treatment), mean, na.rm=TRUE))
GD17.5$Treatment <- ActualGroupOrder
colnames(GD17.5)[1] <- "Mean" #fix column name
GD17.5$SE <- tapply(data_frame$GD17.5, as.character(data_frame$Treatment), standard_error)
GD17.5$Day <- rep("17.5", 4)

#Weight at GD18.5
GD18.5 <- as.data.frame(tapply(data_frame$GD18.5, as.character(data_frame$Treatment), mean, na.rm=TRUE))
GD18.5$Treatment <- ActualGroupOrder
colnames(GD18.5)[1] <- "Mean" #fix column name
GD18.5$SE <- tapply(data_frame$GD18.5, as.character(data_frame$Treatment), standard_error)
GD18.5$Day <- rep("18.5", 4)

#Weight at GD19.5
GD19.5 <- as.data.frame(tapply(data_frame$GD19.5, as.character(data_frame$Treatment), mean, na.rm=TRUE))
GD19.5$Treatment <- ActualGroupOrder
colnames(GD19.5)[1] <- "Mean" #fix column name
GD19.5$SE <- tapply(data_frame$GD19.5, as.character(data_frame$Treatment), standard_error)
GD19.5$Day <- rep("19.5", 4)

#Weight at GD20.5
GD20.5 <- as.data.frame(tapply(data_frame$GD20.5, as.character(data_frame$Treatment), mean, na.rm=TRUE))
GD20.5$Treatment <- ActualGroupOrder
colnames(GD20.5)[1] <- "Mean" #fix column name
GD20.5$SE <- tapply(data_frame$GD20.5, as.character(data_frame$Treatment), standard_error)
GD20.5$Day <- rep("20.5", 4)
```
```{r Merge all weight tables with SE}
#Merge all tables
Weight_Combined_se <- rbind(GD0.5, GD3.5, GD5.5, GD8.5, GD11.5, GD12.5, GD13.5, GD14.5, GD15.5, GD16.5, 
                                  GD17.5, GD18.5, GD19.5, GD20.5)
Weight_Combined_se <- Weight_Combined_se[ ,c(2,1,3,4)]
Weight_Combined_se$Day <- as.numeric(as.vector(Weight_Combined_se$Day)) #convert "Age" to a numeric variable so the x-axis adjusts accordingly
Weight_Combined_se$Upper <- Weight_Combined_se$Mean + Weight_Combined_se$SE
Weight_Combined_se$Lower <- Weight_Combined_se$Mean - Weight_Combined_se$SE
```

## Graph Weight Gain to Distinguish Groups, using standard error
```{r}
png("MaternalWeightGain_SEErrorShading_RmData2_PAExFe_LineGraph.png", units="in", width=10, height=7, res=600)

WG_bygroup_se <- ggplot(Weight_Combined_se, aes(x = Day, y = Mean, group = Treatment, color = Treatment) ) +
     geom_point() +
     geom_ribbon(aes(ymin=Lower, ymax=Upper, fill = Treatment), alpha = 0.15) +
     geom_line(aes(y = Mean))+
  scale_y_continuous(limits = c(220,360))+ 
  ggtitle("Maternal Prenatal Weight Gain by Exposure Group") +
  ylab(expression("Weight (g)")) + 
  xlab(expression("Gestational Day")) +
  theme(plot.title = element_text(hjust = 0.5, size=18), 
        axis.title.y = element_text(size = 16),
        axis.title.x = element_text(size = 16),
        panel.grid.major = element_blank(), #gets rid of major gridlines
        panel.grid.minor = element_blank(), #gets rid of minor gridlines
        panel.background = element_blank(), #turns background white instead of gray
        axis.line = element_line(colour = "black"), 
        axis.text=element_text(size=18, color = "black"), #sets size of x and y axis labels
        axis.text.x=element_text(vjust = .95, hjust = 0.9),
        axis.title=element_text(size=20,face="bold"))
print(WG_bygroup_se)
dev.off()
```
```{r Maternal Prenatal Weight Gain with Standard Error Error Shading, echo = FALSE, warning = FALSE, message = FALSE}
print(WG_bygroup_se)
```

# Weight Gain- percent weight gain from arrival weight
```{r}
PercentIncreaseF <- function(x1, x2) { ((x2 - x1) / x1) * 100 }

#Calculate percent increase from GD0.5 for all dams
PercentIncrease <- data_frame%>% mutate(PI_3.5 = PercentIncreaseF(GD0.5, GD3.5))
PercentIncrease <- PercentIncrease%>% mutate(PI_5.5 = PercentIncreaseF(GD0.5, GD5.5))
PercentIncrease <- PercentIncrease%>% mutate(PI_8.5 = PercentIncreaseF(GD0.5, GD8.5))
PercentIncrease <- PercentIncrease%>% mutate(PI_11.5 = PercentIncreaseF(GD0.5, GD11.5))
PercentIncrease <- PercentIncrease%>% mutate(PI_12.5 = PercentIncreaseF(GD0.5, GD12.5))
PercentIncrease <- PercentIncrease%>% mutate(PI_13.5 = PercentIncreaseF(GD0.5, GD13.5))
PercentIncrease <- PercentIncrease%>% mutate(PI_14.5 = PercentIncreaseF(GD0.5, GD14.5))
PercentIncrease <- PercentIncrease%>% mutate(PI_15.5 = PercentIncreaseF(GD0.5, GD15.5))
PercentIncrease <- PercentIncrease%>% mutate(PI_16.5 = PercentIncreaseF(GD0.5, GD16.5))
PercentIncrease <- PercentIncrease%>% mutate(PI_17.5 = PercentIncreaseF(GD0.5, GD17.5))
PercentIncrease <- PercentIncrease%>% mutate(PI_18.5 = PercentIncreaseF(GD0.5, GD18.5))
PercentIncrease <- PercentIncrease%>% mutate(PI_19.5 = PercentIncreaseF(GD0.5, GD19.5))
PercentIncrease <- PercentIncrease%>% mutate(PI_20.5 = PercentIncreaseF(GD0.5, GD20.5))
PercentIncrease <- select (PercentIncrease,-c(4:26))
```
```{r}
#Percent Increase at GD3.5
PI_GD3.5 <- as.data.frame(tapply(PercentIncrease$PI_3.5, as.character(data_frame$Treatment), mean, na.rm=TRUE))
PI_GD3.5$Treatment <- ActualGroupOrder
colnames(PI_GD3.5)[1] <- "Mean" #fix column name
PI_GD3.5$SE <- tapply(PercentIncrease$PI_3.5, as.character(data_frame$Treatment), standard_error)
PI_GD3.5$Day <- rep("03.5", 4)

#Percent Increase at GD5.5
PI_GD5.5 <- as.data.frame(tapply(PercentIncrease$PI_5.5, as.character(data_frame$Treatment), mean, na.rm=TRUE))
PI_GD5.5$Treatment <- ActualGroupOrder
colnames(PI_GD5.5)[1] <- "Mean" #fix column name
PI_GD5.5$SE <- tapply(PercentIncrease$PI_5.5, as.character(data_frame$Treatment), standard_error)
PI_GD5.5$Day <- rep("05.5", 4)

#Percent Increase at GD8.5
PI_GD8.5 <- as.data.frame(tapply(PercentIncrease$PI_8.5, as.character(data_frame$Treatment), mean, na.rm=TRUE))
PI_GD8.5$Treatment <- ActualGroupOrder
colnames(PI_GD8.5)[1] <- "Mean" #fix column name
PI_GD8.5$SE <- tapply(PercentIncrease$PI_8.5, as.character(data_frame$Treatment), standard_error)
PI_GD8.5$Day <- rep("08.5", 4)

#Percent Increase at GD11.5
PI_GD11.5 <- as.data.frame(tapply(PercentIncrease$PI_11.5, as.character(data_frame$Treatment), mean, na.rm=TRUE))
PI_GD11.5$Treatment <- ActualGroupOrder
colnames(PI_GD11.5)[1] <- "Mean" #fix column name
PI_GD11.5$SE <- tapply(PercentIncrease$PI_11.5, as.character(data_frame$Treatment), standard_error)
PI_GD11.5$Day <- rep("11.5", 4)

#Percent Increase at GD12.5
PI_GD12.5 <- as.data.frame(tapply(PercentIncrease$PI_12.5, as.character(data_frame$Treatment), mean, na.rm=TRUE))
PI_GD12.5$Treatment <- ActualGroupOrder
colnames(PI_GD12.5)[1] <- "Mean" #fix column name
PI_GD12.5$SE <- tapply(PercentIncrease$PI_12.5, as.character(data_frame$Treatment), standard_error)
PI_GD12.5$Day <- rep("12.5", 4)

#Percent Increase at GD13.5
PI_GD13.5 <- as.data.frame(tapply(PercentIncrease$PI_13.5, as.character(data_frame$Treatment), mean, na.rm=TRUE))
PI_GD13.5$Treatment <- ActualGroupOrder
colnames(PI_GD13.5)[1] <- "Mean" #fix column name
PI_GD13.5$SE <- tapply(PercentIncrease$PI_13.5, as.character(data_frame$Treatment), standard_error)
PI_GD13.5$Day <- rep("13.5", 4)

#Percent Increase at GD14.5
PI_GD14.5 <- as.data.frame(tapply(PercentIncrease$PI_14.5, as.character(data_frame$Treatment), mean, na.rm=TRUE))
PI_GD14.5$Treatment <- ActualGroupOrder
colnames(PI_GD14.5)[1] <- "Mean" #fix column name
PI_GD14.5$SE <- tapply(PercentIncrease$PI_14.5, as.character(data_frame$Treatment), standard_error)
PI_GD14.5$Day <- rep("14.5", 4)

#Percent Increase at GD15.5
PI_GD15.5 <- as.data.frame(tapply(PercentIncrease$PI_15.5, as.character(data_frame$Treatment), mean, na.rm=TRUE))
PI_GD15.5$Treatment <- ActualGroupOrder
colnames(PI_GD15.5)[1] <- "Mean" #fix column name
PI_GD15.5$SE <- tapply(PercentIncrease$PI_15.5, as.character(data_frame$Treatment), standard_error)
PI_GD15.5$Day <- rep("15.5", 4)

#Percent Increase at GD16.5
PI_GD16.5 <- as.data.frame(tapply(PercentIncrease$PI_16.5, as.character(data_frame$Treatment), mean, na.rm=TRUE))
PI_GD16.5$Treatment <- ActualGroupOrder
colnames(PI_GD16.5)[1] <- "Mean" #fix column name
PI_GD16.5$SE <- tapply(PercentIncrease$PI_16.5, as.character(data_frame$Treatment), standard_error)
PI_GD16.5$Day <- rep("16.5", 4)

#Percent Increase at GD17.5
PI_GD17.5 <- as.data.frame(tapply(PercentIncrease$PI_17.5, as.character(data_frame$Treatment), mean, na.rm=TRUE))
PI_GD17.5$Treatment <- ActualGroupOrder
colnames(PI_GD17.5)[1] <- "Mean" #fix column name
PI_GD17.5$SE <- tapply(PercentIncrease$PI_17.5, as.character(data_frame$Treatment), standard_error)
PI_GD17.5$Day <- rep("17.5", 4)

#Percent Increase at GD18.5
PI_GD18.5 <- as.data.frame(tapply(PercentIncrease$PI_18.5, as.character(data_frame$Treatment), mean, na.rm=TRUE))
PI_GD18.5$Treatment <- ActualGroupOrder
colnames(PI_GD18.5)[1] <- "Mean" #fix column name
PI_GD18.5$SE <- tapply(PercentIncrease$PI_18.5, as.character(data_frame$Treatment), standard_error)
PI_GD18.5$Day <- rep("18.5", 4)

#Percent Increase at GD19.5
PI_GD19.5 <- as.data.frame(tapply(PercentIncrease$PI_19.5, as.character(data_frame$Treatment), mean, na.rm=TRUE))
PI_GD19.5$Treatment <- ActualGroupOrder
colnames(PI_GD19.5)[1] <- "Mean" #fix column name
PI_GD19.5$SE <- tapply(PercentIncrease$PI_19.5, as.character(data_frame$Treatment), standard_error)
PI_GD19.5$Day <- rep("19.5", 4)

#Percent Increase at GD20.5
PI_GD20.5 <- as.data.frame(tapply(PercentIncrease$PI_20.5, as.character(data_frame$Treatment), mean, na.rm=TRUE))
PI_GD20.5$Treatment <- ActualGroupOrder
colnames(PI_GD20.5)[1] <- "Mean" #fix column name
PI_GD20.5$SE <- tapply(PercentIncrease$PI_20.5, as.character(data_frame$Treatment), standard_error)
PI_GD20.5$Day <- rep("20.5", 4)
```
```{r Merge percent increase tables}
#Merge tables
PercentIncrease_Combined <- rbind(PI_GD3.5, PI_GD5.5, PI_GD8.5, PI_GD11.5, PI_GD12.5, PI_GD13.5, PI_GD14.5, PI_GD15.5, PI_GD16.5, PI_GD17.5, PI_GD18.5, PI_GD19.5, PI_GD20.5)
PercentIncrease_Combined <- PercentIncrease_Combined[ ,c(2,1,3,4)]
PercentIncrease_Combined$Day <- as.numeric(as.vector(PercentIncrease_Combined$Day)) #convert "Day" to a numeric variable so the x-axis adjusts accordingly
names(PercentIncrease_Combined)[1] <- "Treatment"
PercentIncrease_Combined$Upper <- PercentIncrease_Combined$Mean + PercentIncrease_Combined$SE
PercentIncrease_Combined$Lower <- PercentIncrease_Combined$Mean - PercentIncrease_Combined$SE
```

## Graph of Percentage Weight Change to Distinguish Groups, using standard error
```{r}
png("MaternalWeightGainPercentIncrease_SEErrorShading_RmData2_PAExFe_LineGraph.png", units="in", width=10, height=7, res=600)

WG_PI_se <- ggplot(PercentIncrease_Combined, aes(x = Day, y = Mean, group = Treatment, color = Treatment) ) +
     geom_point() +
     geom_ribbon(aes(ymin=Lower, ymax=Upper, fill = Treatment), alpha = 0.15) +
     geom_line(aes(y = Mean))+
  scale_y_continuous(limits = c(0,50))+ 
  ggtitle("Maternal Prenatal Percent Weight Increase by Exposure Group") +
  ylab(expression("Weight Increase from GD0.5 (%)")) + 
  xlab(expression("Gestational Day")) +
  theme(plot.title = element_text(hjust = 0.5, size=18), 
        axis.title.y = element_text(size = 16),
        axis.title.x = element_text(size = 16),
        panel.grid.major = element_blank(), #gets rid of major gridlines
        panel.grid.minor = element_blank(), #gets rid of minor gridlines
        panel.background = element_blank(), #turns background white instead of gray
        axis.line = element_line(colour = "black"), 
        axis.text=element_text(size=18, color = "black"), #sets size of x and y axis labels
        axis.text.x=element_text(vjust = .95, hjust = 0.9),
        axis.title=element_text(size=20,face="bold"))
print(WG_PI_se)
dev.off()
```
```{r Maternal Prenatal Percent Weight Increase with Standard Error Error Shading, echo = FALSE, warning = FALSE, message = FALSE}
print(WG_PI_se)
```

# Session Information
```{r, echo = FALSE}
session_info <- devtools::session_info()
print(session_info)
```
