---
title: "Maternal Rat Gestational Weight Gain, AIN-76A diet with MD or Alcohol and Iron Supplement or Water"
author: "Kaylee Helfrich"
date: "7/10/20-8/20/20"
output: 
  pdf_document: default
  html_document: default
data: "GestationalWeightGain.csv"
---

Built with R `r getRversion()`

```{r RMarkdown setup, include = FALSE, message = FALSE}
require(knitr)
knitr::opts_chunk$set(echo = TRUE, tidy.opts=list(width.cutoff=60), tidy=TRUE)
knitr::opts_knit$set(root.dir = "~/KayleeStuff/Smith_Lab/Data/Rat_Iron/Maternal_Anthro/WeightGain")
options(tinytex.verbose = TRUE)
```

# Graphing Maternal Rat Prenatal Weight Gain
This document details my graphing of the weight gain from maternal rats. This includes bar and line graphs for various measures of weight gain. This analysis uses all data that was collected (including nonpregnant dams for some measures), while another set of analyses will exclude samples from dams with litters that were too small or too large (including R014, R017, R048, R029, R031 and nonpregnant dams). Long-Evans rats arrived at 7 weeks old and were mated at 9-11 weeks of age. The rats were dosed with 5g/kg ethanol or isocaloric maltodextrin from GD17.5-19.5. The dams also received either an iron supplement (6g/kg, Fer-In-Sol) or the same volume of water as a gavage from GD12.5-GD19.5. All dams consumed AIN-76G diet modified to contain 100ppm of iron from arrival through pregnancy. Tissues were harvested on GD20.5. All graphs are mean with standard deviation, since there are not multiple measures per sample. This analysis will allow us to compare the 4 groups. Statistical analysis in JMP will use ANOVA, following checks for normality and variance, to assign significance to the measures. 

```{r include = FALSE}
rm(list=ls())
setwd("~/KayleeStuff/Smith_Lab/Data/Rat_Iron/Maternal_Anthro/WeightGain")
library(ggplot2)
library(plotrix)
library(dplyr)
```

```{r Import file and rearrange by treatment to be alphabetical}
File <- "GestationalWeightGain.csv"
data <- read.csv(File, header=TRUE) 
data_frame <- data.frame(data)
data_frame <- data_frame[order(data_frame$Treatment), ]
```
```{r echo = FALSE}
print(data_frame)
```
```{r Prepare data for graphing}
ActualGroupOrder <- c("PAE-Iron", "PAE","MD-Iron", "MD")
##NumPoints <- 11 #Make sure to set the integer to the number of dots/values you have for each treatment
```

# Pregnant vs. Nonpregnant from arrival until GD12.5- actual weight
The purpose of these graphs is to see if there is a way to distinguish nonpregnant from pregnant rats early in pregnancy before dosing begins to enable optimized dosing.
```{r}
Pregnant <- c("Nonpregnant", "Pregnant")

#Weight at arrival
Arrival <- as.data.frame(tapply(data_frame$Arrival..g., as.character(data_frame$Pregnant.), mean, na.rm=TRUE))
Arrival$Pregnant <- Pregnant
colnames(Arrival)[1] <- "Mean" #fix column name
Arrival$Stdev <- tapply(data_frame$Arrival..g., as.character(data_frame$Pregnant), sd, na.rm=TRUE)
Arrival$Day <- rep("-14", 2)

#Weight at 1 week
OneWeek <- as.data.frame(tapply(data_frame$Arrival..1w..g., as.character(data_frame$Pregnant.), mean, na.rm=TRUE))
OneWeek$Pregnant <- Pregnant
colnames(OneWeek)[1] <- "Mean" #fix column name
OneWeek$Stdev <- tapply(data_frame$Arrival..g., as.character(data_frame$Pregnant), sd, na.rm=TRUE)
OneWeek$Day <- rep("-7", 2)

#Weight at 2 weeks
TwoWeek <- as.data.frame(tapply(data_frame$Arrival...2w..g., as.character(data_frame$Pregnant.), mean, na.rm=TRUE))
TwoWeek$Pregnant <- Pregnant
colnames(TwoWeek)[1] <- "Mean" #fix column name
TwoWeek$Stdev <- tapply(data_frame$Arrival...2w..g., as.character(data_frame$Pregnant), sd, na.rm=TRUE)
TwoWeek$Day <- rep("0", 2)

#Weight at Plug
GD0.5 <- as.data.frame(tapply(data_frame$GD0.5, as.character(data_frame$Pregnant.), mean, na.rm=TRUE))
GD0.5$Pregnant <- Pregnant
colnames(GD0.5)[1] <- "Mean" #fix column name
GD0.5$Stdev <- tapply(data_frame$GD0.5, as.character(data_frame$Pregnant), sd, na.rm=TRUE)
GD0.5$Day <- rep("0.5", 2)

#Weight at GD3.5
GD3.5 <- as.data.frame(tapply(data_frame$GD3.5, as.character(data_frame$Pregnant.), mean, na.rm=TRUE))
GD3.5$Pregnant <- Pregnant
colnames(GD3.5)[1] <- "Mean" #fix column name
GD3.5$Stdev <- tapply(data_frame$GD3.5, as.character(data_frame$Pregnant), sd, na.rm=TRUE)
GD3.5$Day <- rep("03.5", 2)

#Weight at GD5.5
GD5.5 <- as.data.frame(tapply(data_frame$GD5.5, as.character(data_frame$Pregnant.), mean, na.rm=TRUE))
GD5.5$Pregnant <- Pregnant
colnames(GD5.5)[1] <- "Mean" #fix column name
GD5.5$Stdev <- tapply(data_frame$GD5.5, as.character(data_frame$Pregnant), sd, na.rm=TRUE)
GD5.5$Day <- rep("05.5", 2)

#Weight at GD8.5
GD8.5 <- as.data.frame(tapply(data_frame$GD8.5, as.character(data_frame$Pregnant.), mean, na.rm=TRUE))
GD8.5$Pregnant <- Pregnant
colnames(GD8.5)[1] <- "Mean" #fix column name
GD8.5$Stdev <- tapply(data_frame$GD8.5, as.character(data_frame$Pregnant), sd, na.rm=TRUE)
GD8.5$Day <- rep("08.5", 2)

#Weight at GD11.5
GD11.5 <- as.data.frame(tapply(data_frame$GD11.5, as.character(data_frame$Pregnant.), mean, na.rm=TRUE))
GD11.5$Pregnant <- Pregnant
colnames(GD11.5)[1] <- "Mean" #fix column name
GD11.5$Stdev <- tapply(data_frame$GD11.5, as.character(data_frame$Pregnant), sd, na.rm=TRUE)
GD11.5$Day <- rep("11.5", 2)

#Weight at GD12.5
GD12.5 <- as.data.frame(tapply(data_frame$GD12.5, as.character(data_frame$Pregnant.), mean, na.rm=TRUE))
GD12.5$Pregnant <- Pregnant
colnames(GD12.5)[1] <- "Mean" #fix column name
GD12.5$Stdev <- tapply(data_frame$GD12.5, as.character(data_frame$Pregnant), sd, na.rm=TRUE)
GD12.5$Day <- rep("12.5", 2)
```
```{r Merge early gestation tables}
#Merge all tables
EarlyWeightGain_Combined <- rbind(Arrival, OneWeek, TwoWeek, GD0.5, GD3.5, GD5.5, GD8.5, GD11.5, GD12.5)
EarlyWeightGain_Combined <- EarlyWeightGain_Combined[ ,c(2,1,3,4)]
EarlyWeightGain_Combined$Day <- as.numeric(as.vector(EarlyWeightGain_Combined$Day)) #convert "Age" to a numeric variable so the x-axis adjusts accordingly
names(EarlyWeightGain_Combined)[1] <- "Pregnant"
EarlyWeightGain_Combined$Upper <- EarlyWeightGain_Combined$Mean + EarlyWeightGain_Combined$Stdev
EarlyWeightGain_Combined$Lower <- EarlyWeightGain_Combined$Mean - EarlyWeightGain_Combined$Stdev
```

## Graph Early Prenatal Weight Gain to Distinguish Pregnant vs. Nonpregnant dams
```{r}
#generate with and without error bars
png("Maternal_EarlyPrenatalWeightGain_PregnantvsNonpregnant_AllData_PAExFe_LineGraph.png", units="in", width=10, height=7, res=600)

WG_PvNP <- ggplot(data=EarlyWeightGain_Combined, aes(x=Day, y=Mean, group=Pregnant, color=Pregnant)) +
  geom_point() +
  geom_line() +
  scale_y_continuous(expand = c(0,0), limits = c(0,325))+ 
  scale_color_hue(labels = c("Nonpregnant", "Pregnant")) +
  geom_errorbar(aes(ymin=Lower, ymax=Upper), width=.2) +
  ggtitle("Maternal Early Prenatal Weight Gain, Pregnant Vs. Nonpregnant") +
  ylab(expression("Weight (g)")) + 
  xlab(expression("Gestational Day")) +
  theme(plot.title = element_text(hjust = 0.5, size=18), 
        axis.title.y = element_text(size = 16),
        axis.title.x = element_text(size = 16),
        panel.grid.major = element_blank(), #gets rid of major gridlines
        panel.grid.minor = element_blank(), #gets rid of minor gridlines
        panel.background = element_blank(), #turns background white instead of gray
        axis.line = element_line(colour = "black"), 
        axis.text=element_text(size=18, color = "black"), #sets size of x and y axis labels
        axis.text.x=element_text(vjust = .95, hjust = 0.9),
        axis.title=element_text(size=20,face="bold"))
  
print(WG_PvNP)
dev.off()
```
```{r Maternal Early Prenatal Weight Gain, Pregnant vs. Nonpregnant, echo = FALSE, warning = FALSE, message = FALSE}
print(WG_PvNP)
```

```{r}
#Total Weight Gain, pregnant vs. nonpregnant
#Weight at GD13.5
GD13.5 <- as.data.frame(tapply(data_frame$GD13.5, as.character(data_frame$Pregnant.), mean, na.rm=TRUE))
GD13.5$Pregnant <- Pregnant
colnames(GD13.5)[1] <- "Mean" #fix column name
GD13.5$Stdev <- tapply(data_frame$GD13.5, as.character(data_frame$Pregnant), sd, na.rm=TRUE)
GD13.5$Day <- rep("13.5", 2)

#Weight at GD14.5
GD14.5 <- as.data.frame(tapply(data_frame$GD14.5, as.character(data_frame$Pregnant.), mean, na.rm=TRUE))
GD14.5$Pregnant <- Pregnant
colnames(GD14.5)[1] <- "Mean" #fix column name
GD14.5$Stdev <- tapply(data_frame$GD14.5, as.character(data_frame$Pregnant), sd, na.rm=TRUE)
GD14.5$Day <- rep("14.5", 2)

#Weight at GD15.5
GD15.5 <- as.data.frame(tapply(data_frame$GD15.5, as.character(data_frame$Pregnant.), mean, na.rm=TRUE))
GD15.5$Pregnant <- Pregnant
colnames(GD15.5)[1] <- "Mean" #fix column name
GD15.5$Stdev <- tapply(data_frame$GD15.5, as.character(data_frame$Pregnant), sd, na.rm=TRUE)
GD15.5$Day <- rep("15.5", 2)

#Weight at GD16.5
GD16.5 <- as.data.frame(tapply(data_frame$GD16.5, as.character(data_frame$Pregnant.), mean, na.rm=TRUE))
GD16.5$Pregnant <- Pregnant
colnames(GD16.5)[1] <- "Mean" #fix column name
GD16.5$Stdev <- tapply(data_frame$GD16.5, as.character(data_frame$Pregnant), sd, na.rm=TRUE)
GD16.5$Day <- rep("16.5", 2)

#Weight at GD17.5
GD17.5 <- as.data.frame(tapply(data_frame$GD17.5, as.character(data_frame$Pregnant.), mean, na.rm=TRUE))
GD17.5$Pregnant <- Pregnant
colnames(GD17.5)[1] <- "Mean" #fix column name
GD17.5$Stdev <- tapply(data_frame$GD17.5, as.character(data_frame$Pregnant), sd, na.rm=TRUE)
GD17.5$Day <- rep("17.5", 2)

#Weight at GD18.5
GD18.5 <- as.data.frame(tapply(data_frame$GD18.5, as.character(data_frame$Pregnant.), mean, na.rm=TRUE))
GD18.5$Pregnant <- Pregnant
colnames(GD18.5)[1] <- "Mean" #fix column name
GD18.5$Stdev <- tapply(data_frame$GD18.5, as.character(data_frame$Pregnant), sd, na.rm=TRUE)
GD18.5$Day <- rep("18.5", 2)

#Weight at GD19.5
GD19.5 <- as.data.frame(tapply(data_frame$GD19.5, as.character(data_frame$Pregnant.), mean, na.rm=TRUE))
GD19.5$Pregnant <- Pregnant
colnames(GD19.5)[1] <- "Mean" #fix column name
GD19.5$Stdev <- tapply(data_frame$GD19.5, as.character(data_frame$Pregnant), sd, na.rm=TRUE)
GD19.5$Day <- rep("19.5", 2)

#Weight at GD20.5
GD20.5 <- as.data.frame(tapply(data_frame$GD20.5, as.character(data_frame$Pregnant.), mean, na.rm=TRUE))
GD20.5$Pregnant <- Pregnant
colnames(GD20.5)[1] <- "Mean" #fix column name
GD20.5$Stdev <- tapply(data_frame$GD20.5, as.character(data_frame$Pregnant), sd, na.rm=TRUE)
GD20.5$Day <- rep("20.5", 2)
```
```{r Merge total gestation tables}
#Merge all tables
TotalWeightGain_Combined <- rbind(Arrival, OneWeek, TwoWeek, GD0.5, GD3.5, GD5.5, GD8.5, GD11.5, GD12.5, GD13.5, GD14.5, GD15.5, GD16.5, GD17.5, GD18.5, GD19.5, GD20.5)
TotalWeightGain_Combined <- TotalWeightGain_Combined[ ,c(2,1,3,4)]
TotalWeightGain_Combined$Day <- as.numeric(as.vector(TotalWeightGain_Combined$Day)) #convert "Day" to a numeric variable so the x-axis adjusts accordingly
names(TotalWeightGain_Combined)[1] <- "Pregnant"
TotalWeightGain_Combined$Upper <- TotalWeightGain_Combined$Mean + TotalWeightGain_Combined$Stdev
TotalWeightGain_Combined$Lower <- TotalWeightGain_Combined$Mean - TotalWeightGain_Combined$Stdev
```

## Graph Total Prenatal Weight Gain to Distinguish Pregnant vs. Nonpregnant dams
```{r}
#generate with and without error bars
png("Maternal_TotalPrenatalWeightGain_PregnantvsNonpregnant_AllData_PAExFe_LineGraph.png", units="in", width=10, height=7, res=600)

WG_PvNP <- ggplot(data=TotalWeightGain_Combined, aes(x=Day, y=Mean, group=Pregnant, color=Pregnant)) +
  geom_point() +
  geom_line() +
  scale_y_continuous(expand = c(0,0), limits = c(0,375))+ 
  scale_color_hue(labels = c("Nonpregnant", "Pregnant")) +
  geom_errorbar(aes(ymin=Lower, ymax=Upper), width=.2) +
  ggtitle("Maternal Total Prenatal Weight Gain, Pregnant Vs. Nonpregnant") +
  ylab(expression("Weight (g)")) + 
  xlab(expression("Gestational Day")) +
  theme(plot.title = element_text(hjust = 0.5, size=18), 
        axis.title.y = element_text(size = 16),
        axis.title.x = element_text(size = 16),
        panel.grid.major = element_blank(), #gets rid of major gridlines
        panel.grid.minor = element_blank(), #gets rid of minor gridlines
        panel.background = element_blank(), #turns background white instead of gray
        axis.line = element_line(colour = "black"), 
        axis.text=element_text(size=18, color = "black"), #sets size of x and y axis labels
        axis.text.x=element_text(vjust = .95, hjust = 0.9),
        axis.title=element_text(size=20,face="bold"))
  
print(WG_PvNP)
dev.off()
```
```{r Maternal Total Prenatal Weight Gain, Pregnant vs. Nonpregnant, echo = FALSE, warning = FALSE, message = FALSE}
print(WG_PvNP)
```

# Pregnant vs. Nonpregnant from arrival until GD12.5- percent weight gain from arrival weight
```{r}
Function1 <- function(x1, x2) { ((x2 - x1) / x1) * 100 }

#Calculate percent increase from GD0.5 for all dams
PercentIncrease <- data_frame%>% mutate(PI_3.5 = Function1(GD0.5, GD3.5))
PercentIncrease <- PercentIncrease%>% mutate(PI_5.5 = Function1(GD0.5, GD5.5))
PercentIncrease <- PercentIncrease%>% mutate(PI_8.5 = Function1(GD0.5, GD8.5))
PercentIncrease <- PercentIncrease%>% mutate(PI_11.5 = Function1(GD0.5, GD11.5))
PercentIncrease <- PercentIncrease%>% mutate(PI_12.5 = Function1(GD0.5, GD12.5))
PercentIncrease <- PercentIncrease%>% mutate(PI_13.5 = Function1(GD0.5, GD13.5))
PercentIncrease <- PercentIncrease%>% mutate(PI_14.5 = Function1(GD0.5, GD14.5))
PercentIncrease <- PercentIncrease%>% mutate(PI_15.5 = Function1(GD0.5, GD15.5))
PercentIncrease <- PercentIncrease%>% mutate(PI_16.5 = Function1(GD0.5, GD16.5))
PercentIncrease <- PercentIncrease%>% mutate(PI_17.5 = Function1(GD0.5, GD17.5))
PercentIncrease <- PercentIncrease%>% mutate(PI_18.5 = Function1(GD0.5, GD18.5))
PercentIncrease <- PercentIncrease%>% mutate(PI_19.5 = Function1(GD0.5, GD19.5))
PercentIncrease <- PercentIncrease%>% mutate(PI_20.5 = Function1(GD0.5, GD20.5))
PercentIncrease <- select (PercentIncrease,-c(4:26))
```
```{r}
#Percent Increase at GD3.5
PI_GD3.5 <- as.data.frame(tapply(PercentIncrease$PI_3.5, as.character(data_frame$Pregnant.), mean, na.rm=TRUE))
PI_GD3.5$Pregnant <- Pregnant
colnames(PI_GD3.5)[1] <- "Mean" #fix column name
PI_GD3.5$Stdev <- tapply(PercentIncrease$PI_3.5, as.character(data_frame$Pregnant), sd, na.rm=TRUE)
PI_GD3.5$Day <- rep("03.5", 2)

#Percent Increase at GD5.5
PI_GD5.5 <- as.data.frame(tapply(PercentIncrease$PI_5.5, as.character(data_frame$Pregnant.), mean, na.rm=TRUE))
PI_GD5.5$Pregnant <- Pregnant
colnames(PI_GD5.5)[1] <- "Mean" #fix column name
PI_GD5.5$Stdev <- tapply(PercentIncrease$PI_5.5, as.character(data_frame$Pregnant), sd, na.rm=TRUE)
PI_GD5.5$Day <- rep("05.5", 2)

#Percent Increase at GD8.5
PI_GD8.5 <- as.data.frame(tapply(PercentIncrease$PI_8.5, as.character(data_frame$Pregnant.), mean, na.rm=TRUE))
PI_GD8.5$Pregnant <- Pregnant
colnames(PI_GD8.5)[1] <- "Mean" #fix column name
PI_GD8.5$Stdev <- tapply(PercentIncrease$PI_8.5, as.character(data_frame$Pregnant), sd, na.rm=TRUE)
PI_GD8.5$Day <- rep("08.5", 2)

#Percent Increase at GD11.5
PI_GD11.5 <- as.data.frame(tapply(PercentIncrease$PI_11.5, as.character(data_frame$Pregnant.), mean, na.rm=TRUE))
PI_GD11.5$Pregnant <- Pregnant
colnames(PI_GD11.5)[1] <- "Mean" #fix column name
PI_GD11.5$Stdev <- tapply(PercentIncrease$PI_11.5, as.character(data_frame$Pregnant), sd, na.rm=TRUE)
PI_GD11.5$Day <- rep("11.5", 2)

#Percent Increase at GD12.5
PI_GD12.5 <- as.data.frame(tapply(PercentIncrease$PI_12.5, as.character(data_frame$Pregnant.), mean, na.rm=TRUE))
PI_GD12.5$Pregnant <- Pregnant
colnames(PI_GD12.5)[1] <- "Mean" #fix column name
PI_GD12.5$Stdev <- tapply(PercentIncrease$PI_12.5, as.character(data_frame$Pregnant), sd, na.rm=TRUE)
PI_GD12.5$Day <- rep("12.5", 2)

#Percent Increase at GD13.5
PI_GD13.5 <- as.data.frame(tapply(PercentIncrease$PI_13.5, as.character(data_frame$Pregnant.), mean, na.rm=TRUE))
PI_GD13.5$Pregnant <- Pregnant
colnames(PI_GD13.5)[1] <- "Mean" #fix column name
PI_GD13.5$Stdev <- tapply(PercentIncrease$PI_13.5, as.character(data_frame$Pregnant), sd, na.rm=TRUE)
PI_GD13.5$Day <- rep("13.5", 2)

#Percent Increase at GD14.5
PI_GD14.5 <- as.data.frame(tapply(PercentIncrease$PI_14.5, as.character(data_frame$Pregnant.), mean, na.rm=TRUE))
PI_GD14.5$Pregnant <- Pregnant
colnames(PI_GD14.5)[1] <- "Mean" #fix column name
PI_GD14.5$Stdev <- tapply(PercentIncrease$PI_14.5, as.character(data_frame$Pregnant), sd, na.rm=TRUE)
PI_GD14.5$Day <- rep("14.5", 2)

#Percent Increase at GD15.5
PI_GD15.5 <- as.data.frame(tapply(PercentIncrease$PI_15.5, as.character(data_frame$Pregnant.), mean, na.rm=TRUE))
PI_GD15.5$Pregnant <- Pregnant
colnames(PI_GD15.5)[1] <- "Mean" #fix column name
PI_GD15.5$Stdev <- tapply(PercentIncrease$PI_15.5, as.character(data_frame$Pregnant), sd, na.rm=TRUE)
PI_GD15.5$Day <- rep("15.5", 2)

#Percent Increase at GD16.5
PI_GD16.5 <- as.data.frame(tapply(PercentIncrease$PI_16.5, as.character(data_frame$Pregnant.), mean, na.rm=TRUE))
PI_GD16.5$Pregnant <- Pregnant
colnames(PI_GD16.5)[1] <- "Mean" #fix column name
PI_GD16.5$Stdev <- tapply(PercentIncrease$PI_16.5, as.character(data_frame$Pregnant), sd, na.rm=TRUE)
PI_GD16.5$Day <- rep("16.5", 2)

#Percent Increase at GD17.5
PI_GD17.5 <- as.data.frame(tapply(PercentIncrease$PI_17.5, as.character(data_frame$Pregnant.), mean, na.rm=TRUE))
PI_GD17.5$Pregnant <- Pregnant
colnames(PI_GD17.5)[1] <- "Mean" #fix column name
PI_GD17.5$Stdev <- tapply(PercentIncrease$PI_17.5, as.character(data_frame$Pregnant), sd, na.rm=TRUE)
PI_GD17.5$Day <- rep("17.5", 2)

#Percent Increase at GD18.5
PI_GD18.5 <- as.data.frame(tapply(PercentIncrease$PI_18.5, as.character(data_frame$Pregnant.), mean, na.rm=TRUE))
PI_GD18.5$Pregnant <- Pregnant
colnames(PI_GD18.5)[1] <- "Mean" #fix column name
PI_GD18.5$Stdev <- tapply(PercentIncrease$PI_18.5, as.character(data_frame$Pregnant), sd, na.rm=TRUE)
PI_GD18.5$Day <- rep("18.5", 2)

#Percent Increase at GD19.5
PI_GD19.5 <- as.data.frame(tapply(PercentIncrease$PI_19.5, as.character(data_frame$Pregnant.), mean, na.rm=TRUE))
PI_GD19.5$Pregnant <- Pregnant
colnames(PI_GD19.5)[1] <- "Mean" #fix column name
PI_GD19.5$Stdev <- tapply(PercentIncrease$PI_19.5, as.character(data_frame$Pregnant), sd, na.rm=TRUE)
PI_GD19.5$Day <- rep("19.5", 2)

#Percent Increase at GD20.5
PI_GD20.5 <- as.data.frame(tapply(PercentIncrease$PI_20.5, as.character(data_frame$Pregnant.), mean, na.rm=TRUE))
PI_GD20.5$Pregnant <- Pregnant
colnames(PI_GD20.5)[1] <- "Mean" #fix column name
PI_GD20.5$Stdev <- tapply(PercentIncrease$PI_20.5, as.character(data_frame$Pregnant), sd, na.rm=TRUE)
PI_GD20.5$Day <- rep("20.5", 2)
```
```{r Merge percent increase tables}
#Merge tables
PercentIncrease_Combined <- rbind(PI_GD3.5, PI_GD5.5, PI_GD8.5, PI_GD11.5, PI_GD12.5, PI_GD13.5, PI_GD14.5, PI_GD15.5, PI_GD16.5, PI_GD17.5, PI_GD18.5, PI_GD19.5, PI_GD20.5)
PercentIncrease_Combined <- PercentIncrease_Combined[ ,c(2,1,3,4)]
PercentIncrease_Combined$Day <- as.numeric(as.vector(PercentIncrease_Combined$Day)) #convert "Day" to a numeric variable so the x-axis adjusts accordingly
names(PercentIncrease_Combined)[1] <- "Pregnant"
PercentIncrease_Combined$Upper <- PercentIncrease_Combined$Mean + PercentIncrease_Combined$Stdev
PercentIncrease_Combined$Lower <- PercentIncrease_Combined$Mean - PercentIncrease_Combined$Stdev
```

## Graph Total Prenatal Weight Gain to Distinguish Pregnant vs. Nonpregnant dams
```{r}
#generate with and without error bars
png("Maternal_PercentIncreaseWeightGain_PregnantvsNonpregnant_AllData_PAExFe_LineGraph.png", units="in", width=10, height=7, res=600)

WG_PI_PvNP <- ggplot(data=PercentIncrease_Combined, aes(x=Day, y=Mean, group=Pregnant, color=Pregnant)) +
  geom_point() +
  geom_line() +
  scale_y_continuous(expand = c(0,0), limits = c(0,55))+ 
  scale_color_hue(labels = c("Nonpregnant", "Pregnant")) +
  geom_errorbar(aes(ymin=Lower, ymax=Upper), width=.2) +
  ggtitle("Maternal % Increase in Weight from GD0.5, Pregnant Vs. Nonpregnant") +
  ylab(expression("Weight Increase from GD0.5 (%)")) + 
  xlab(expression("Gestational Day")) +
  theme(plot.title = element_text(hjust = 0.5, size=18), 
        axis.title.y = element_text(size = 16),
        axis.title.x = element_text(size = 16),
        panel.grid.major = element_blank(), #gets rid of major gridlines
        panel.grid.minor = element_blank(), #gets rid of minor gridlines
        panel.background = element_blank(), #turns background white instead of gray
        axis.line = element_line(colour = "black"), 
        axis.text=element_text(size=18, color = "black"), #sets size of x and y axis labels
        axis.text.x=element_text(vjust = .95, hjust = 0.9),
        axis.title=element_text(size=20,face="bold"))
  
print(WG_PI_PvNP)
dev.off()
```
```{r Maternal Percent Increase in Weight, Pregnant vs. Nonpregnant, echo = FALSE, warning = FALSE, message = FALSE}
print(WG_PI_PvNP)
```

# Session Information
```{r, echo = FALSE}
session_info <- devtools::session_info()
print(session_info)
```
